---
title: "CC Custom Scorecard Quarterly Report"
author: "Bryan Thomas"
date: "2026-04-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Desktop/Professional/Projects/CC_Model_Monitoring")
here::i_am("orchestration_2.Rmd")
```

## Overview

TBD

## Running the Workflow

### 1) Renv Initialization

If this is the first time pulling the project, you will need to initialize the renv.lock file. This will set the environment dependencies in sync with what was used during project development. Run the init function below.

You should see this prompt:

``` r
renv::init()
this project already has a lockfile. What would you like to do?

1: Restore the project from the lockfile.
2: Discard the lockfile and re-initialize the project.
3: Activate the project without snapshotting or installing any packages.
4: Abort project initialization.
```

Select option 1 and the environment will be set up appropriately.

```{r}
# renv::init()
```

### 2) Credential Setup

Database credentials are supplied via environment variables from `.Renviron`;
see `.Renviron.example`. In the production environment this section configured
a credential store for the internal warehouses.

### 3) Setting the Project Paths

All pointers in this project use soft paths via the {here} package. To ensure that the pointers are correct. Be sure that the `CC_Model_Monitoring` project is opened before proceeding. This ensures the working directory is set appropriately.

Code and reference files are sourced within the `CC_Model_Monitoring` repo. Data is written in this directory as well as a local `data/` folder.

### 4) Loading Functions & Globals

Source all required R scripts and load necessary libraries. Set global variables for cohort dates and file paths.

```{r}
library(lubridate)
library(ggplot2)
library(data.table)

set.seed(42)
options(scipen = 999)
# cohort_date: override by setting before knitting; defaults to current quarter
# cohort_date <- as.Date('2026-04-01')
if (!exists("cohort_date")) {
  cohort_date <- lubridate::floor_date(Sys.Date(), "quarter")
}
backfilling_date <- cohort_date %m-% months(6)

# Gates which R methodologies can/cannot, wired into logic starting [checkpoint 5
ks_methods <- c('live', 'fixed', 'true')
stopifnot(all(unlist(ks_methods %in% c('live', 'fixed', 'true'))))

source('R/pull_apps.R')
source('R/function_cc_scorecard_data.R')
source('R/pull_features.R')
source('R/pull_performance.R')
# PENDING TRANSCRIPTION — not yet OCR'd, not needed before the QC marker
```

### 5) Folder Init

This section checks for required directories and creates them if missing. Run once per new project setup.

**Note** — after folder creation, copy any required data files into the local `data/` directory to preserve file pointers.

```{r, echo=FALSE}
#------------------------------- Folder Structure ---------------------------------
fs::dir_create(c('data', 'data/apps', 'data/scorecard', 'data/features', 'data/dq_12_mos'))
fs::dir_create(c('output_files', 'output_files/quarterly_stats'))
```
# Quarterly Report

This section processes scorecard and application data, calculates PSI, CSI, KS, bad rate, and approval rate metrics, and prepares summary tables.

PSI and CSI evaluate the most recent window of through the door (TTD) applications. This window is considered the model input.

## PSI

The chunk below pulls the most recent Starters application and scorecard data from PATH if it is not already held within the local repository and writes the data as a .txt.gz file. This allows us to avoid repetitious pulls when looking over windows or different report iterations.

```{r}

paths <- fs::dir_ls('data/scorecard')[which(basename(fs::dir_ls('data/scorecard')) %in% c(
  glue::glue('scorecard_{format(as.Date(cohort_date), "%Y%m")}.txt.gz'),
  glue::glue('scorecard_{format(as.Date(cohort_date) %m+% months(1), "%Y%m")}.txt.gz'),
  glue::glue('scorecard_{format(as.Date(cohort_date) %m+% months(2), "%Y%m")}.txt.gz')))]

if(length(paths) != 3){
  scorecard <- purrr::map_dfr(seq(cohort_date, cohort_date %m+% months(2), 'month'),
                              .progress = TRUE,
                              function(model_input_window){

                              df <- get_cc_scorecard_data(performance_window = model_input_window,
                                                          write = T)
                              return(df)
                              })
}


paths <- fs::dir_ls('data/apps/')[which(basename(fs::dir_ls('data/apps/')) %in% c(
  glue::glue('apps_{format(as.Date(cohort_date), "%Y%m")}.txt.gz'),
  glue::glue('apps_{format(as.Date(cohort_date) %m+% months(1), "%Y%m")}.txt.gz'),
  glue::glue('apps_{format(as.Date(cohort_date) %m+% months(2), "%Y%m")}.txt.gz')
))]

if(length(paths) != 3){
  apps <- purrr::map_dfr(seq(cohort_date, cohort_date %m+% months(2), 'month'),
                              .progress = TRUE,
                              function(model_input_window){

                              df <- get_apps_data(performance_window = model_input_window,
                                                          write = T)
                              return(df)
                              })
}

gc()
```

This section pulls in the most recent quarter of application and scorecard data and uses predefined custom score ranges to set PSI bins in accordance with the model development population.

```{r}
number_of_month_window <- 3

scorecard <- purrr::map_df(c(1:number_of_month_window),
                function(i) {
                  
                  df <- data.table::fread(glue::glue('data/scorecard/scorecard_{format(cohort_date %m+% months(i - 1), "%Y%m")}.txt.gz'))
                  
                  })

apps <- purrr::map_df(seq(number_of_month_window),
                function(i) {
                  
                  df <- data.table::fread(glue::glue('data/apps/apps_{format(cohort_date %m+% months(i - 1), "%Y%m")}.txt.gz'))
                  
                  })

names(apps) <- names(apps) |> tolower()
names(scorecard) <- names(scorecard) |> tolower()
```

```{r}
 psi_df <- apps |> 
  mutate(app_num = as.numeric(app_num),
         user_ref_num = as.numeric(user_ref_num)) |>
    left_join(scorecard |>
                mutate(user_ref_num = as.numeric(user_ref_num))) |>
  mutate(has_score = case_when(is.na(prim_score) ~ 0,
                                 prim_score < 100 ~ -1,
                                 prim_score > 450 ~ 9999,
                              T ~ 1),
           has_segment = case_when(is.na(segment) ~ 0,
                                   T ~ 1)) |>
  filter(!client_product_cd %in% c('SEC', 'MSC'),
         !is.na(prim_score),
         has_segment == 1,
         prim_score >= 100)

  # Define vigintile breaks per segment (20 buckets each)
  # Breaks represent score thresholds; labels are auto-generated as "lower to upper"
  segment_breaks <- list(
    "All Segments" = c(100, 117, 134, 151, 168, 185, 202, 219, 236, 253,
                       270, 287, 304, 321, 338, 355, 372, 389, 406, 423, 450),
    "0" = c(100, 112, 124, 136, 148, 160, 172, 184, 196, 208,
            220, 232, 244, 256, 268, 280, 292, 304, 316, 328, 450),
    "1" = c(100, 118, 136, 154, 172, 190, 208, 226, 244, 262,
            280, 298, 316, 334, 352, 362, 372, 382, 392, 410, 450),
    "2" = c(100, 120, 140, 160, 180, 200, 220, 240, 260, 280,
            300, 315, 330, 345, 360, 375, 390, 405, 420, 435, 450),
    "3" = c(100, 125, 150, 170, 190, 210, 230, 250, 270, 290,
            310, 325, 340, 355, 370, 385, 395, 405, 420, 435, 450),
    "4" = c(100, 130, 155, 180, 200, 220, 240, 260, 280, 300,
            320, 335, 350, 365, 380, 390, 400, 410, 425, 440, 450)
  )

  # Helper: cut scores into labeled bins using segment-specific breaks
  bucket_scores <- function(scores, breaks) {
    labels <- paste(head(breaks, -1), tail(breaks, -1), sep = " to ")
    cut(scores, breaks = breaks, labels = labels, include.lowest = TRUE, right = TRUE)
  }

  # "All Segments" row
  psi_all <- psi_df |>
    dplyr::mutate(all_bucket_aligned = bucket_scores(prim_score, segment_breaks[["All Segments"]])) |>
    dplyr::group_by(all_bucket_aligned) |>
    dplyr::summarise(counts = dplyr::n_distinct(user_ref_num)) |>
    dplyr::mutate(segment = 'All Segments')

  # Per-segment rows
  psi_by_seg <- psi_df |>
    dplyr::mutate(segment = as.character(as.numeric(segment))) |>
    dplyr::group_by(segment) |>
    dplyr::group_modify(~ {
      brks <- segment_breaks[[.y$segment]]
      .x |>
        dplyr::mutate(all_bucket_aligned = bucket_scores(prim_score, brks)) |>
        dplyr::group_by(all_bucket_aligned) |>
        dplyr::summarise(counts = dplyr::n_distinct(user_ref_num), .groups = 'drop')
    }) |>
    dplyr::ungroup()

  psi <- dplyr::bind_rows(psi_all, psi_by_seg) |>
    dplyr::select(segment, counts, all_bucket_aligned) |>
    dplyr::arrange(segment, desc(all_bucket_aligned))
        
  
psi_raw_data <- psi |>
  tidyr::separate(all_bucket_aligned, c('Lower_Range', 'Upper_Range'), sep = ' to ') |>
  dplyr::mutate(Lower_Range = as.numeric(Lower_Range),
                Upper_Range = as.numeric(Upper_Range)) |>
  dplyr::rename(Scorecard = segment)

psi_raw_data
```


Join the development population reference (generated by R/build_dev_population.R)
with psi_raw_data on Scorecard + Lower_Range + Upper_Range (numeric). Compute
PSI per segment: percent_dev, percent_current, difference, proportion, log of
proportion, and population divergence. Split into 6 tibbles (All Segments + 0-4)
and write to a cached xlsx with one tab per segment.

```{r}
# --- PENDING REBUILD: refit range tables ---
# Originally :240-399 loaded development population from external xlsx files
# (loan_and_cd_event_DEFAULT.xlsx, refit_Development_est_bin.xlsx) and
# constructed: ranges_refit, ranges_refit_plt, ranges_refit3, pol_data, ranges.
#
# Downstream status:
#   ranges_refit_pol  — read at :2031 (dt_ks_bins_pol = ranges_refit_pol |>).
#                       Genuine orphan: ranges_refit_pol is never assigned
#                       anywhere in the file (OCR loss). KS task must rebuild.
#   ranges            — reassigned at :518, :542, :554 before any post-:453 read.
#                       Commenting :385 (ranges <- ranges_refit) costs nothing.
#   ranges_refit_plt  — zero reads after :453. Dead object.
#   ranges_refit3     — zero reads after :453. Dead object.
#   pol_data          — zero reads after :445. Dead object.
#
# Not required for PSI; will be rebuilt in the KS task.
# ---------------------------------------------------------------------------

# --- PSI Calculation ---
# Load shared stability index helper and development population reference
source(here::here("R/compute_si.R"))
source(here::here("R/build_dev_population.R"))
dev_pop <- build_dev_population(here::here("data/dev_population/dev_population.txt.gz"))

# Full join: dev side drives the 120-row frame; coalesce empty current bins to 0
psi_joined <- dplyr::full_join(
  dev_pop, psi_raw_data,
  by = c("Scorecard", "Lower_Range", "Upper_Range")
) |>
  dplyr::mutate(counts = dplyr::coalesce(counts, 0L))

# --- Assertions ---
stopifnot("Dev bins have NAs - join key mismatch" =
            sum(is.na(psi_joined$counts_dev)) == 0)
stopifnot("Expected 120 rows (6 segments x 20 bins)" =
            nrow(psi_joined) == 120)

# Zero-bin policy (D14): floor at epsilon to avoid ln(0) = -Inf.
psi_epsilon <- 0.0001

# PSI-specific: assert uniform 5% dev (guaranteed by construction for vigintiles)
dev_pcts <- psi_joined |>
  dplyr::group_by(Scorecard) |>
  dplyr::mutate(p = counts_dev / sum(counts_dev)) |>
  dplyr::pull(p)
stopifnot("Dev percentages are not all 5%" = all(dev_pcts == 0.05))

# Compute stability index (shared helper — also used by CSI)
psi_result <- compute_stability_index(psi_joined, epsilon = psi_epsilon)

# Restore PSI column selection and order for downstream compatibility.
# Downstream formatters at :737 read psi_data back FROM the xlsx cache.
# openxlsx::read.xlsx applies make.names(): Lower_Range -> Lower.Range.
# This is a known transformation; the formatter must account for it.
psi_col_order <- c("Scorecard", "Lower_Range", "Upper_Range", "counts_dev",
                   "counts", "percent_dev", "percent_current",
                   "Difference (B-A)", "Proportion (B/A)",
                   "Log of Proportion (B/A)", "Population Divergence (K-L)",
                   "epsilon_floored", "epsilon_only")
psi_data_list <- purrr::map(psi_result$detail, function(tbl) {
  tbl |> dplyr::select(dplyr::all_of(psi_col_order))
})

psi_summary <- psi_result$summary |>
  dplyr::rename(Population_Stability_Index = SI_value)

psi_summary

# --- Write xlsx ---
wb <- openxlsx::createWorkbook()
purrr::walk(names(psi_data_list), function(nm) {
  openxlsx::addWorksheet(wb, nm)
  openxlsx::writeDataTable(wb, nm, psi_data_list[[nm]])
})
fs::dir_create(here::here("output_files"))
openxlsx::saveWorkbook(wb,
  here::here("output_files/psi_quarterly.xlsx"),
  overwrite = TRUE)
```

## CSI

CSI evaluates drift in the model's input features. Each feature is binned using
frozen development-population breaks (D18) and compared to the dev distribution.
The CSI population is derived from psi_df to guarantee identity with the PSI
population.

```{r}
# --- CSI: Feature Stability ---
source(here::here("R/feature_breaks.R"))
fs::dir_create(here::here("data/features"))

# Pull + cache (mirrors apps/scorecard pattern at :103-137)
feat_paths <- fs::dir_ls("data/features")[which(
  basename(fs::dir_ls("data/features")) %in% c(
    glue::glue("features_{format(as.Date(cohort_date), '%Y%m')}.txt.gz"),
    glue::glue("features_{format(as.Date(cohort_date) %m+% months(1), '%Y%m')}.txt.gz"),
    glue::glue("features_{format(as.Date(cohort_date) %m+% months(2), '%Y%m')}.txt.gz")
  )
)]

if (length(feat_paths) != 3) {
  purrr::walk(seq(cohort_date, cohort_date %m+% months(2), "month"),
              function(m) get_features_data(performance_window = m, write = TRUE))
}

# Read from cache
features <- purrr::map_dfr(seq_len(number_of_month_window), function(i) {
  data.table::fread(glue::glue(
    "data/features/features_{format(cohort_date %m+% months(i - 1), '%Y%m')}.txt.gz"
  ))
})
names(features) <- tolower(names(features))
features <- features |> dplyr::mutate(user_ref_num = as.numeric(user_ref_num))

# Join to PSI population (guarantees identical population — same filters applied)
csi_df <- dplyr::inner_join(
  psi_df |> dplyr::select(user_ref_num, segment),
  features,
  by = "user_ref_num"
)

# --- Per-feature CSI ---
csi_results <- list()
csi_summary_rows <- list()

for (fname in names(feature_breaks)) {
  fb <- feature_breaks[[fname]]
  vals <- csi_df[[fname]]

  # Bin: integer index (1:n_bins). Join key is structural, not label-based.
  if (fb$type == "continuous") {
    bin_idx <- as.integer(cut(vals, breaks = fb$breaks,
                              right = TRUE, include.lowest = TRUE))
    n_bins <- length(fb$dev_counts)
    bin_labels <- paste(head(fb$breaks, -1), tail(fb$breaks, -1), sep = " to ")
  } else {
    bin_idx <- as.integer(factor(vals, levels = fb$levels))
    n_bins <- length(fb$levels)
    bin_labels <- fb$levels
  }

  # Assert no NA bin index (value outside declared bins/levels)
  stopifnot("Feature value outside declared bins/levels" = !anyNA(bin_idx))

  # Aggregation: per segment + All Segments
  binned <- dplyr::tibble(
    user_ref_num = csi_df$user_ref_num,
    Scorecard    = as.character(as.numeric(csi_df$segment)),
    bin_index    = bin_idx
  )

  agg_by_seg <- binned |>
    dplyr::group_by(Scorecard, bin_index) |>
    dplyr::summarise(counts = dplyr::n(), .groups = "drop")

  agg_all <- binned |>
    dplyr::mutate(Scorecard = "All Segments") |>
    dplyr::group_by(Scorecard, bin_index) |>
    dplyr::summarise(counts = dplyr::n(), .groups = "drop")

  agg <- dplyr::bind_rows(agg_all, agg_by_seg)

  # Dev reference: 6 segments x n_bins rows (global breaks — same for all)
  dev_ref <- dplyr::bind_rows(lapply(
    c("All Segments", as.character(0:4)),
    function(seg) {
      dplyr::tibble(
        Scorecard  = seg,
        bin_index  = seq_len(n_bins),
        counts_dev = fb$dev_counts,
        bin_label  = bin_labels
      )
    }
  ))

  # Full join from dev side; coalesce empty current bins to 0
  csi_joined <- dplyr::full_join(dev_ref, agg,
                                  by = c("Scorecard", "bin_index")) |>
    dplyr::mutate(counts = dplyr::coalesce(counts, 0L))

  # Assert full grid
  expected_rows <- n_bins * 6L
  if (nrow(csi_joined) != expected_rows) {
    stop(fname, ": expected ", expected_rows, " rows, got ", nrow(csi_joined))
  }

  # Compute stability index (same helper as PSI)
  result <- compute_stability_index(csi_joined, epsilon = psi_epsilon)

  csi_results[[fname]] <- result
  csi_summary_rows[[fname]] <- result$summary |>
    dplyr::mutate(feature = fname)
}

# --- CSI summary table: 6 segments x 5 features ---
csi_summary_long <- dplyr::bind_rows(csi_summary_rows)
csi_summary <- csi_summary_long |>
  dplyr::select(Scorecard, feature, CSI = SI_value) |>
  tidyr::pivot_wider(names_from = feature, values_from = CSI)

csi_summary

# Epsilon share
csi_eps_share <- csi_summary_long |>
  dplyr::select(Scorecard, feature, epsilon_share) |>
  tidyr::pivot_wider(names_from = feature, values_from = epsilon_share)

csi_eps_share

# --- Assert full bin grid: 10+8+5+4+3 = 30 bins per segment, 180 total ---
total_data_rows <- sum(purrr::map_int(names(csi_results), function(fname) {
  fb <- feature_breaks[[fname]]
  n_bins <- if (fb$type == "continuous") length(fb$dev_counts) else length(fb$levels)
  data_rows <- sum(purrr::map_int(
    csi_results[[fname]]$detail,
    ~ sum(!is.na(.x$bin_index))
  ))
  if (data_rows != n_bins * 6) {
    stop(fname, ": expected ", n_bins * 6, " data rows, got ", data_rows)
  }
  data_rows
}))
stopifnot("Total data rows should be 180 (30 bins x 6 segments)" =
            total_data_rows == 180)

# --- Write xlsx: one tab per feature, segment as column ---
wb_csi <- openxlsx::createWorkbook()
purrr::walk(names(csi_results), function(fname) {
  tab_data <- dplyr::bind_rows(csi_results[[fname]]$detail)
  openxlsx::addWorksheet(wb_csi, fname)
  openxlsx::writeDataTable(wb_csi, fname, tab_data)
})
openxlsx::saveWorkbook(wb_csi,
  here::here("output_files/csi_quarterly.xlsx"),
  overwrite = TRUE)
```

## KS and DQ90 Rank Ordering

Performance-based metrics use a DIFFERENT cohort than PSI/CSI. PSI/CSI
evaluate Q3 2026 through-the-door applications (current quarter input
distribution). KS and DQ90 rank ordering evaluate Q3 2025 BOOKED
applications whose 12-month outcome window has now closed. The lag is
inherent to outcome monitoring: performance evidence is always 12 months
behind the input distribution that PSI measures.

```{r}
# --- KS and DQ90 Rank Ordering ---
source(here::here("R/compute_ks.R"))
source(here::here("R/ks_baseline.R"))

# Performance cohort: 12 months prior to current quarter
perf_date <- cohort_date %m-% months(12)

# Pull + cache performance data (3 months, mirrors apps pattern at :104)
perf_paths <- fs::dir_ls("data/dq_12_mos")[which(
  basename(fs::dir_ls("data/dq_12_mos")) %in% c(
    glue::glue("dq_12_mos_{format(perf_date, '%Y%m')}.txt.gz"),
    glue::glue("dq_12_mos_{format(perf_date %m+% months(1), '%Y%m')}.txt.gz"),
    glue::glue("dq_12_mos_{format(perf_date %m+% months(2), '%Y%m')}.txt.gz")
  )
)]

if (length(perf_paths) != 3) {
  purrr::walk(seq(perf_date, perf_date %m+% months(2), "month"),
              function(m) get_performance_data(performance_window = m, write = TRUE))
}

perf <- purrr::map_dfr(seq_len(number_of_month_window), function(i) {
  data.table::fread(glue::glue(
    "data/dq_12_mos/dq_12_mos_{format(perf_date %m+% months(i - 1), '%Y%m')}.txt.gz"
  ))
})
names(perf) <- tolower(names(perf))

# Pull Q3 2025 apps + scorecard for score and segment
perf_apps_paths <- fs::dir_ls("data/apps")[which(
  basename(fs::dir_ls("data/apps")) %in% c(
    glue::glue("apps_{format(perf_date, '%Y%m')}.txt.gz"),
    glue::glue("apps_{format(perf_date %m+% months(1), '%Y%m')}.txt.gz"),
    glue::glue("apps_{format(perf_date %m+% months(2), '%Y%m')}.txt.gz")
  )
)]

if (length(perf_apps_paths) != 3) {
  purrr::walk(seq(perf_date, perf_date %m+% months(2), "month"),
              function(m) get_apps_data(performance_window = m, write = TRUE))
}

perf_apps <- purrr::map_dfr(seq_len(number_of_month_window), function(i) {
  data.table::fread(glue::glue(
    "data/apps/apps_{format(perf_date %m+% months(i - 1), '%Y%m')}.txt.gz"
  ))
})
names(perf_apps) <- tolower(names(perf_apps))

perf_sc_paths <- fs::dir_ls("data/scorecard")[which(
  basename(fs::dir_ls("data/scorecard")) %in% c(
    glue::glue("scorecard_{format(perf_date, '%Y%m')}.txt.gz"),
    glue::glue("scorecard_{format(perf_date %m+% months(1), '%Y%m')}.txt.gz"),
    glue::glue("scorecard_{format(perf_date %m+% months(2), '%Y%m')}.txt.gz")
  )
)]

if (length(perf_sc_paths) != 3) {
  purrr::walk(seq(perf_date, perf_date %m+% months(2), "month"),
              function(m) get_cc_scorecard_data(performance_window = m, write = TRUE))
}

perf_sc <- purrr::map_dfr(seq_len(number_of_month_window), function(i) {
  data.table::fread(glue::glue(
    "data/scorecard/scorecard_{format(perf_date %m+% months(i - 1), '%Y%m')}.txt.gz"
  ))
})
names(perf_sc) <- tolower(names(perf_sc))

# Join: performance -> apps -> scorecard
ks_df <- perf |>
  dplyr::mutate(user_ref_num = as.numeric(user_ref_num)) |>
  dplyr::inner_join(
    perf_apps |> dplyr::mutate(user_ref_num = as.numeric(user_ref_num)) |>
      dplyr::select(user_ref_num, prim_score, decision),
    by = "user_ref_num"
  ) |>
  dplyr::inner_join(
    perf_sc |> dplyr::mutate(user_ref_num = as.numeric(user_ref_num)) |>
      dplyr::select(user_ref_num, segment),
    by = "user_ref_num"
  )

# Assert: all performance rows are approved (table-level constraint)
stopifnot("Performance rows with non-Approve decision" =
            all(ks_df$decision == "Approve"))

# KS deciles are RE-DERIVED from the booked cohort, NOT frozen.
# This is the OPPOSITE of PSI/CSI and correctly so: PSI asks whether the
# population moved relative to development, KS asks whether the score
# still separates within THIS population.
ks_result <- compute_ks_stats(ks_df)

# --- Monitoring flags (observations, not hard stops) ---
# Monotonicity: segments 1-4 should have non-decreasing decile bad rates
for (seg in c("0", "1", "2", "3", "4")) {
  seg_rates <- ks_result$decile_rates |>
    dplyr::filter(segment == seg) |>
    dplyr::arrange(decile)
  diffs <- diff(seg_rates$bad_rate)
  if (!all(diffs >= 0)) {
    breaks <- which(diffs < 0)
    warning("Seg ", seg, ": monotonicity break at decile(s) ",
            paste(breaks, collapse = ", "))
  }
}

# Average bads per decile per segment >= 28 (3x volume)
for (seg in as.character(0:4)) {
  seg_bads <- ks_result$ks_by_segment |>
    dplyr::filter(segment == seg) |>
    dplyr::pull(n_bads)
  if (seg_bads / 10 < 28) warning("Seg ", seg, ": avg bads/decile < 28")
}

# --- Compare to development baseline ---
ks_comparison <- dplyr::inner_join(
  ks_result$ks_by_segment,
  ks_baseline$ks,
  by = "segment"
) |>
  dplyr::mutate(ks_delta = ks_value - dev_ks)

ks_comparison

# Decile bad rates
ks_result$decile_rates

# --- Cache ---
openxlsx::write.xlsx(
  list(ks_comparison = ks_comparison,
       decile_rates = ks_result$decile_rates),
  here::here("output_files/ks_quarterly.xlsx"),
  overwrite = TRUE
)
```

# QC: Completed

# QC: Validated
