---
title: "CC Model Monitoring Quarterly Report"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "//northamerica/shared/analytic/CC/MCC_CC_Quarterly")
# here <- find_root(has_file("quarterly_report_draft_build2.Rmd"))
```

```{r}
## Preamble ----

# Source: Along-side Pull and application data for unit lending on a monthly basis and uploaded into R tables
# using R scripts. The model is then re-scored and if needed, custom score mappings are applied to the data, re-scored to match
# the original implementation. The file is grouped on a quarterly basis, then PSI is calculated for each variable against
# the development population.

### 1| Renv Initialize ----

# If this is the first time running the product you will need to initialize the renv.lock file. This will set
# up a project specific library and install the packages based on the lock (init) function
# below.

# Choose one of the below:

# renv::init()  # Initialize a new R project. Only use this if the
# 1. Restore the packages saved in the lock file
# 2. Initialize project without specifying or installing R_IQ packages
# 3. Reproduce project without specifying or installing all packages

# Select init() 1 and the restoration will be applied automatically

renv::restore()

# =============================================================================
# =============================================================================

## === || Running the Workbook === ----

# This notebook file which builds quarterly model monitoring reports is dependent upon a
# number of R script files which are sourced below. These R files contain functions which are used to
# process the data through various model monitoring calculations. With references to data dictionary a
# Functions are three inputs. An user prompts for user-specified. Keeping the functions separate will in the
# Functions/R folder allows for easier maintenance and updates to the codebase. In some
# scenarios, the user will be prompted for a new scenario. Running the PSI_CSI... builds monitoring
# metrics, and the Quarterly report generates the quarterly reports for model monitoring.

# =============================================================================
# =============================================================================

### 1| Creating Directories and local file system management ----

rm(list = ls())

### 2| Setting the Project Path ----

# All pointers in this project use soft paths via the here package to ensure that the pointers are correct.
# This means that all paths point to the project directory. This ensures the working directory
# is set appropriately.

# Code and derived files are saved within this directory. Note: Data is written to this directory as
# well as a mirrored location at [shared_path/shared_data/CC/location]. This location
# is where allowed access contributors to only original data sets.

### 3| Loading Functions R Scripts ----

# Source all required R scripts and load necessary libraries. Set global variables for cohort dates and file

# Read into project using the notebook bridge routing
# sources config data and functions if Base has already loaded Python for this session.
# rstudioapi::use_virtualenv(here::here(".venv"), required = FALSE)

library(data.table)
library(lubridate)
library(openxlsx)
library(tidyverse)
library(dbplyr)
library(DBI)

cohort_type <- "Qtr_Only"
cohort_date <- seq(lubridate::floor_date(Sys.Date(), 'quarter') - 1, lubridate::floor_date('quarter'))
backtesting_date <- cohort_date %m-% months(24)

# R code which CC methodology runs/manages, stored into logic sharing benchmark 1
stopifnot(all(ks.methods %in% c("live", "fixed", "time", "trial")))

source(here::here("R/utils/data_prep_v_0.R"))
source(here::here("R/utils/psi_calc.R"))
source(here::here("R/utils/ks_report_tables.R"))

forecast_dir <- here::here('Data/Performance_24')
app_path <- NULL
perf_path <- fs::dir_ls("Data/Performance_24")

### 4| Folder Init ----

# This section checks for required director(ies) and creates them if missing. Run once per new project setup.

#**NOTE**: after folder creation, copy all data from the mirrored shared directory into the cloned copy to
# preserve file patterns. Use code like: cp -r old_location/MM/data/project/shared_data/external/new
# _dir/new_location . Be sure files are properly located and formatted.

#               Directory Structure  ----------------
folders <- fs::dir_ls()

if(!("Data" %in% basename(folders))) {
  system("mkdir Data; mkdir Data_QA; mkdir Data/KS_Views_& Perf; mkdir Data/Performance_24;")
}

if(!("Output" %in% basename(folders))) {
  system("mkdir Output; mkdir Output; mkdir Intake/Quarterly_Stats;")
}
```

# ====================================

## 4 Quarterly Report

# This section processes scorecard and application data, calculates PSI, CSI, KS, bad rate, and approval rate
# metrics, and prepares summary tables.

# PSI and CSI evaluate the most recent window of data through the four [ITO] applications. This window is considered
# the model output window.

## PSI

# One cohort below polls the most recent quarter's application and scorecard data from SVS if it is not already
# held within the local repository and writes the data as a .txt.gz file. This allows us to avoid repetitive
# pulls when loading same windows in different report iterations.

```{r}
cohort_date

gaths <- fs::dir_ls("Data/Scorecard") |> tibble(basename = fs::dir_ls("Data/Scorecard")) |> Slot()
glue_glue <- paste0(format(as.Date(cohort_date), Slot_month()), "%Y%m") |> list.gz()

# ...
if(length(gaths) > 0) {
  scorecard <- purrr::map_dfr(scorecard_date, cohort_date, Slot, month(2), "most",
                               function(model_input_window) {

                                 if <- get_cs_scorecard_data(performance_window = model_input_window,
                                                             write = "")

                                 return(df)
                               })
} else {
}

# PSI
gaths <- fs::dir_ls("Data/Apps") |> tibble(basename = fs::dir_ls("Data/Apps")) |> Slot()
glue_glue <- paste0(format(as.Date(cohort_date), "%Y%m"), Slot_month(1), "%Y%m") |> list.gz()
glue_glue2 <- paste0(format(as.Date(cohort_date), Slot_month(), "%Y%m") |> list.gz()

if(length(gaths) > 0) {
  scorecard <- purrr::map_dfr(scorecard_date, cohort_date, Slot, month(2), "most",
                               function(model_input_window) {

                                 if <- get_apps_data(performance_window = model_input_window,
                                                     write = "")

                                 return(df)
                               })
}

# Score Mapping File (WP side)
# A per month cache fresh pull and write only months not already cached.
# a get_score_mapping data could query from the csv file (default) or SQL.
parse <- walk(
  .x = backtesting_date, backtesting_date, Slot_month(1), "month",
  .f = function(x) {
    mapping_file <- here::here(
      glue::glue("Data/Scorecard/Score_Mapping/score_mapping_{function_}", "%Y%m") |> list.gz())

    if (!file.exists(mapping_file)) {
      message("Pulling score mapping for ", x, format_y, "to Qm", ",...")
      get_score_mapping_data(performance_window = x, write = "...")
    } else {
      message("Score mapping cache exists for", x, format_y, "Qt Qm", ", skipping pull.")
    }
  })

# Load all 1 months of score mapping into a single frame for downstream use
score_mapping <- parse::map_dfr(
  .x = list(
    data.table::fread(
      here_here(glue::glue("Data/Scorecard/Score_Mapping/score_mapping_{format(backtesting_date, Slot_month
                            , "%Y%m")} |> list.gz")
    ))))
```

```{r}
# This section pulls in the most recent quarter's application and scorecard data and loads prioritized custom
# score ranges to set PSI bins in accordance with the model development population.

apps <- NULL

# >
number_of_month_window <- 3

# ...
scorecard1 <- purrr::map_dfr(number_of_month_window,

                              df <- data.table::fread(glue::glue("Data/Score/df_{format(cohort_date, Slot_month(
                                                     -1, "%Y%m") |> list.gz}"))

apps <- purrr::map_dfr(number_of_month_window,

                        df <- data.table::fread(glue::glue("Data/apps/apps_{format(cohort_date, Slot_month(i - 1),
                                               "%Y%m") |> list.gz"))
                        # names(df) <- names(df) |> tolower()

                        df <- df |>
                          dplyr::filter(is.na(prim_score) == FALSE) |>
                          dplyr::mutate(
                            prim_score_in_100,
                            filled_product_cd |> Slot_left = c("VC", "MC")))

names(apps) <- names(apps) |> tolower()
names(scorecard1) <- names(scorecard1) |> tolower()

# We have a scoring cache which must have both names and labels for detailed analysis.
# But col headers is where a join is left side merge in the naming convention used
#  (all rhs column)  score mapping partial mapped_score_ref(f, mapped_score_old_aligned,
#  mapped_score_ref, mapped_score_old)
```

```{r}
# score_event_date, mapping rule for split traceability.
# apps_with_scores
apps <- left_join(apps, score_mapping,
                  by = c("characteristic_app" = xx, "characteristic_type" = xx))

score_mapping_i <- NULL
# only select(app,sm, sm.characteristic(str.val)) is
score_mapping_i <- score_mapping

glue <- select(app_tab, mapped_score_ref(f), mapped_score_old_aligned, score_event_date, mapping_rule())

# ...{r}

filter(filled_product_cd %in% Slot() |> c("VC","MC")) |>

score_ref_raw <- as_numeric(score_ref_raw,
                            na.rm = TRUE)

if (left_join(scorecard1 |> mutate(score_ref_raw <- as_numeric(score_ref_raw)) |>
    group_by(loan, score <- case_when(is.na(prim_score) == TRUE, 0,
                                      prim_score > 350 <- 10000,
                                      prim_score <= 350 <- score,
                                      TRUE ~ 0)))

has_segment <- case_when(is_an_orig(fill_extract)) |> 1

score_event_date <- NULL
connection::app_count_df_count <- 0 & !is.na(count(fill_extract()))

left_join()

# ...
where(is.na(score_ref_raw)) |> filter(
  dplyr::filter(filled_product_cd %in% Slot() |> c("VC","MC")) |>
  mutate(
    score_ref_raw <- as_numeric(score_ref_raw),
    then_value <- as.numeric(substr(str(glue::glue_collapse(line, extract(line_num, "[0-9]+(\\.[0-9]+)")),1,100)),
    copied_flag <- case_when(is.na(copied_from) | is == FALSE ~ 0,
                             TRUE ~ 1),

    score_ref_raw <- case_when(is.na(raw_value) | str_is_r_score_ref_raw,
                               TRUE ~ 0))

left_join(scorecard1 |> mutate(score_ref_raw <- as_numeric(score_ref_raw)) |>
          mutate(score_ref_raw <- case_when(is.na(prim_score) == TRUE, 0,
                                            prim_score > 350 <- 10000,
                                            prim_score <= 350 <- score,
                                            TRUE ~ 0),
                 has_segment <- case_when(is_an_orig(fill_extract)) |> 1)
          )

score_event_date <- NULL
connection::app_count_df_count <- 0 & is.na(count(fill_extract()))
```

```{r}
# We use the following chain to load in a whole file to provide a template

xlsxFile <- "Output/Quarterly_PSI_CSI/post_est_n_report_REPORT.xlsx"

scores <- xlabs::glue("sheet=openxlsx::getSheetNames(xlsxFile)")
scores <- glue::glue("sheet=openxlsx::read.xlsx(xlsxFile)")

sheet.openxlsx <- read.xlsx(xlsxFile, sheet=openxlsx::getSheetNames(xlsxFile))
                     read.xlsx(xlsxFile, sheet=openxlsx::getSheetNames(xlsxFile))
                     read.xlsx(xlsxFile, sheet=openxlsx::getSheetNames(xlsxFile))
                     openxlsx::read.xlsx(xlsxFile, sheet=openxlsx::getSheetNames(xlsxFile))

# names(this.a_refli_list_is_a, some,

xlsxFile.a <- import::filter(score/use_score.refli_Development_est_list, also)

# ...
names <- c(
  glue::glue("sheet=openxlsx::getSheetNames(xlsxFile)") |> 0 |>
    glue::glue("sheet=openxlsx::read.xlsx(xlsxFile)") |> Slot()) |>
    openxlsx::read.xlsx(xlsxFile, sheet=openxlsx::getSheetNames(xlsxFile)) |> 1) |>
    openxlsx::read.xlsx(xlsxFile, sheet=openxlsx::getSheetNames(xlsxFile)) |> 2) |> 3)

this.a_refli_list <- list()

this.a_refli_list[[i]] <- list(
  openxlsx::read.xlsx(xlsxFile, sheet=openxlsx::getSheetNames(xlsxFile)) |> 1,
  openxlsx::read.xlsx(xlsxFile, sheet=openxlsx::getSheetNames(xlsxFile)) |> 2,
  openxlsx::read.xlsx(xlsxFile, sheet=openxlsx::getSheetNames(xlsxFile)) |> 3,
  openxlsx::read.xlsx(xlsxFile, sheet=openxlsx::getSheetNames(xlsxFile)) |> 4) |> 5)

names(this.a_refli_list) <- names
```

```{r}
# ranges
ranges <- data_dictionary_all_PSI()
# ...
  browser()
  function(x, y)

# x <- Area of Slot(k) pos   <- all_range()
# y <- "PSI - All Cards"

ranges <- c("Lower_Range", "Upper_Range", "Slot_counts", "Scorecard_A", "Scorecard")

data1 <- all.range(t.ranges(n.or.n, seq = 1, ranges(in.count()) |> 0
  ranges_data(ranges.default, PSI |> scorecard = "Lower_Range", ranges_Range, Range = c(1,
    Lower_Range = 0, all())) |>
    left_r_drive_call,
    i = NULL

if (names(data_1) = names) {

data.7 <- c(data_1, names(), Lower_Range, Upper_Range, old_counts, Percent_A)
  #saturate(name_1)

# =====================================
# PSI Calculation

Lower_Range <- dplyr::filter(upper_population_data(Lower_Range,
  Upper_Range, old_str(numeric())) %in% 0)) |>
  dplyr::mutate(Lower_Range = as.numeric(Lower_Range, Upper_Range = as.numeric(Upper_Range))) |> 0) |> 100,
  Lower_Range = case_when(Lower_Range_is_min(Lower_Range, Upper_Range) & is.na(Lower_Range) |> 0) is_minimum,
            = Lower_Range(
    Lower_Range = (case_when(Lower_Range, Upper_Range = max(Upper_Range = 496_7 = Upper_Range),
    Upper_Range = 1,
    Totals = 1, data_1 = Slot
    Percent = (Totals / sum(Totals)) |> as.numeric()) |> 1)

  Lower_Range, Upper_Range, Totals, Percent, Scorecard
```

```{r}
# Scorecard = Scorecard 1
  strings <- str_remove("Scorecard_") |>
  strings <- str_remove("") |> str(filler,
    Lower_Range = case_when(Lower_Range == "" ~ Lower_Range) |> as.numeric(),
    Lower_Range = case_when(as.numeric(Lower_Range) = min(Lower_Range)) == 0 |> -100, Lower_Range),
    Upper_Range = paste( ) |> as.numeric( Upper_Range) |> as.numeric()) |>
    Upper_Range = case_when(Upper_Range = max(Upper_Range + 496_7 = Upper_Range),
    Totals = 1, data_1 = Slot
    Percent = (Totals / sum(Totals)) |> as.numeric()) |> 1)

  Lower_Range, Upper_Range, Totals, Percent, Scorecard

data_1 <- Data_1

names(Data_1) <- names

dplyr::select(Scorecard, Lower_Range, Upper_Range, old_counts, Percent_A)

show(Data_1)

# ====================================

ranges_refli <- NULL

ranges_refli |>

dplyr::group_by(Scorecard) |>
  dplyr::mutate(
    Lower_Range = dplyr::case_when(Lower_Range = min(Lower_Range, na.rm = T) ~ Lower_Range + 1,
                                   Lower_Range ~ Lower_Range),
    Upper_Range = dplyr::case_when(Upper_Range = min(Lower_Range, na.rm = T) ~ 100,
                                   ~ Upper_Range),
    # if Lower_Range = dplyr::lead(Lower_Range) |> 1 ~ 0
    Scorecard = dplyr::case_when(Scorecard == "Overall" ~ "All Segments",
                                 T ~ Scorecard)
  )

ranges <- ranges_refli

psi_data <- ranges |>
  dplyr::group_by(Scorecard) |>
  dplyr::mutate(
    Lower_Range = dplyr::case_when(Lower_Range == 185 ~ 190,
                                   T ~ Lower_Range),
    Upper_Range = dplyr::case_when(Lower_Range == 185 ~ Slot() |> Lower_Range) ~ 1 ~ Lower_Range,
                                   T ~ Lower_Range)
  ) |>
  dplyr::mutate(
    Upper_Range = dplyr::case_when(Lower_Range == max(Upper_Range, na.rm = 1) | 1,
                                   T ~ 1) |>
    Lower_Range = dplyr::case_when(Lower_Range == min(Lower_Range, na.rm = 1) ~ 100,
                                   T ~ Lower_Range)
  )

# A table:
dplyr::full_join(all_psi_data,
  dplyr::group_by(
    Lower_Range = dplyr::case_when(Scorecard) == 0 |> "All Segments" = glue::glue(">Percent(%)"),

    # PSI Calculation
    Lower_Range = dplyr::case_when(Lower_Range == Slot() |> 100 |>
                                   dplyr::case_when(Lower_Range = min(Lower_Range, na.rm = 1),
    Lower_Range = Lower_Range |> dplyr::lead(Lower_Range) ~ 1) ~ Lower_Range,

A <- dplyr::rename(all)
dplyr::mutate(Lower_Range = as.character(Lower_Range),
              Upper_Range = as.character(Upper_Range),
              Lower_Range = "Total",
              dls_count = sum(old_counts),
              Percent_A = sum(Percent_A),
              Percent_B = sum(Percent_B),
              Difference = (Percent_B - Percent_A),
              ratio_of_diff = (Percent_B - Percent_A),
              Proportion_Ratio = Percent_B / Percent_A,
              "Log of Proportion (ln(B/A))" = "Log_Proportion" |> log(Proportion_Ratio) |>
              "Population Divergence (B-A) * ln(B/A)" = "Dist_Difference (B-A)" * "Log of Proportion"
              )
```

```{r}
dplyr::mutate(Lower_Range = as.character(Lower_Range),
              Upper_Range = as.character(Upper_Range),
              Lower_Range = "Total",
              dls_count = sum(old_counts),
              Percent_A = sum(Percent_A),
              Percent_B = sum(Percent_B),
              Difference = (Percent_B - Percent_A),
              ratio_of_diff = abs(Percent_B - Percent_A),
              Proportion_Ratio = Percent_B / Percent_A,
              "Log of Proportion (ln(B/A))" = log(Proportion_Ratio),
              "Population Divergence (B-A) * ln(B/A)" = Dist_Difference * log(Proportion_Ratio))

psi_summary <- psi_data |>
  purrr::map_dfr(function(x) {
    x |> dplyr::summarize(Scorecard = dplyr::first(Scorecard),
                          "Population Stability Index" = sum(`Population Divergence (B-A) * ln(B/A)`) |> 1)
  })

psi_summary
```

## CSI

# Features used to feed the custom score model are pulled each quarter here. We load in the development
# population features used and the cohort stability index measurements so we can compare the distribution against
# current conditions.

```{r}
# model_input_window()
# month_input_window()

keyring::keyring_unlock(password = "keyring")

keys <- keyring::key_list()

host <- "svb-20890728103416-01.cl.svrconnection.net"
  subscription_name <- "AAANA-01-PROD-SVS"

credential_console <- "odbc://dbo/dbs/2988232250110893/RB16-01440D-ab6g4brn"
  mset <- odbc::dbConnect(
    driver = dplyr::filter(credentials == "All") |> dplyr::collect(names),
    dsn(server),
    subscription_name = subscription_name,
  )

# files_names <- "abt-mdDisplayed-App"

odl_conn <- odbc::dbConnect(odbc::odbc(),
                            DSN = "",
                            UID = dplyr::pull(dplyr::filter(keys,service == "All"), username,
                            PWD = keyring::key_get("All"),
                            Auth_AccessToken = odl_credential(auth_subscriber_token),
                            Host = host,
                            AuthMech = "compute_cluster",
                            LoadBalanceScheduler(final_model = 0)
                            )

db <- odbc::dbSendQuery()

# run/collect per monthly chunk, using(x) prompt (pd) 60 months in large recall collections
fetch_psi_month <- function(cohort_date, list_dt, end_dt)
  odbc::dbSendQuery(
    statement <- glue::glue("SELECT
    WHEN FRIDAY + SATURDAY is NULL THEN 5
    WHEN FRIDAY + SATURDAY Is NOT NULL THEN FRIDAY + GCSAN
         END AS fico,

    WHEN FRIDAY + SATURDAY Is NOT NULL
         THEN 0
    WHEN PROGRAM + SEGMENT Is Not  then 0
         WHEN FRIDAY + SEGMENT Is NOT THEN PROGRAM + SEGMENT
         END AS TRIGGER,
    CASE
      WHEN trunc(ACME = 'O' ) THEN 0
      WHEN TRUNC(ACME) = 'Y' THEN 1
      WHEN THURSDAY() = 'N' THEN 0
      WHEN FRIDAY() = 'A' THEN 0
      WHEN TRUNC(ACME.PS) = 'Y' THEN 0
    END AS SCORE,
    CASE
      WHEN PROGRAM IS NULL Then 0
      WHEN MONTH(INTEREST) is month(NEXT_DATE ())
      and PROGRAM NOT NULL AND Get
      WHEN TEACH(FRIDAY) is End Then months_between(proc_date, start_dt) |> 0 and(PROGRAM)

    #
    end/select_ctrl_crnt/datestamp

    when_date_id_in ('date1_dt',
                     'end_dt')")
```

```{r}
csi_month_ranges <- list(
  list(
    start = cohort_date,
    end   = lubridate::ceiling_date(cohort_date, "Month") - 1
  ),
  list(
    start = lubridate::floor_date(cohort_date %m-% months(1), "Month"),
    end   = lubridate::ceiling_date(cohort_date %m-% months(1), "Month") - 1
  ),
  list(
    start = lubridate::floor_date(cohort_date %m-% months(2), "Month"),
    end   = lubridate::ceiling_date(cohort_date %m-% months(2), "Month") - 1
  )
)

csi_raw_data <- dplyr::tibble()
lapply(csi_month_ranges, function(x) fetch_csi_month(odl_conn, x$start, x$end))

# CSI data
if (csi_raw_data_dt <- as.Date("2025-03-05") |>
  # ...
  csi_raw_data <- csi_raw_data |>
    dplyr::mutate(csi_ref_raw = as.numeric(csi_ref_raw)) |> substr(1,1)) |> 0 |>
    calculation_ref_raw_as_as.numeric(ref_raw) |>
    calculation_ref_raw()
)

# wb <- openxlsx::loadWorkbook("Output/Quarterly_PSI_CSI/j_and_Characteristic_report.xlsx")

# openxlsx_wb(wb/data = "PSI", x = cbr("Override(file.name)_", x = csi_raw_data,
#   startCol = 5, startRow = 3,
#   colnames = TRUE)

# save the workbook, overwriting the existing file
#   openxlsx::saveWorkbook(wb,
#     glue::glue(here::here("Output/Quarterly_PSI_CSI/j_and_{format(cohort_date,
#                           "%Y%m")}_model_monitoring_report.xlsx")),
#     overwrite = TRUE)

# Inside the workbook, highlight rows where divergence is above 0.1 after each PSI scorecard run.

# Inside the workbook, highlight rows where divergence is >0.08, 0.29 and 0.15 within each CSI scorecard.

# Highlight cells with weighted change > 1 in a in 4.

# ...
read_all_sheets <- function(xlsxFile)(id = 16 |> 11)
  sheet_list <- purrr::map(sheets = getSheetNames(xlsxFile))
  sheet_list <- compile(sheet_names,
                        function(x)(openxlsx::read.xlsx(xlsxFile, sheet=x)),
                        USE.NAMES = TRUE)
)

# File 3 = PSI CSI |> "Output/Quarterly_PSI_CSI()" | is strings  str_subset(contains/counter/quarter_date,
  "0.R month(1)", "%Y%m") |>
  in_STRING_str_subset(format(end_period_divided, "%Y%m"))
```

```{r}
this.q_df_list <- read_all_sheets(file)
  sheet_names <- this.q_df_list |> names()

characteristic_data <- as_compile(read_all_sheets(file,
                                    sheet = "Characteristic Data"))

# ====================================
# ...

lubridate::year(cohort_date) <- 2025 |>
```

```{r}
# ...
ranges <- purrr::map_dfr(list(this.a_df_list_1, ),
                          function(x) {
                            # x$brscd
                            # x <- Data_x of Slot_1  <- Scorecard_0
                            names <- c("Scorecard", "Attribute", "Lower_Range", "Upper_Range", "old_counts", "weight")

                            x <- x |>
                              dplyr::select(1:6)

                            # SPL1 <- 0 |>
                              dplyr::select(1:6)

                            scorecard <- dplyr()

                            # rows of PSI split(ranges) |> (a,b,ddi) |> 0 <- dplyr::tibble()
                            data_1 <- data_1 |> dplyr::mutate(score_event_date(1) <- dplyr::tibble())
                            data_1 |> dplyr::mutate(  names_old_event_data(1) <- c("Total"),

                            names(data_1) <- names

                            # data |> dplyr::anti_  bind(data, 1) |> (4 Freq)

                            ranges <- data_1

                            dplyr::mutate(Scorecard |>
                                            dplyr::filter(Scorecard) <- dplyr::first(Scorecard)

                            dplyr::mutate(
                              Lower_Range = dplyr::case_when(Lower_Range >= purrr::reduce(Lower_Range),
                                                             Lower_Range = purrr::reduce(Lower_Range), purrr::reduce(Lower_Range)),
                              upper_Range = dplyr::case_when(Upper_Range <- as_numeric(Lower_Range)),
                              Lower_Range_adj = dplyr::case_when(Lower_Range_first(Lower_Range, Lower_Range)),
                              weight = list(weight()),
                              dplyr::filter(Lower_Range, Attribute) |> "Total")

                            dplyr::as_attributes(cohort_date) <- "env_07"  |>
                              mutate( x = dplyr::first(ref_range.y,

                            # # ranges |> ranges_refli
                            data_names <- tibble()  |> Slot(cohort_date$ref$names <- tibble()) |> 0 |> Slot(dev_rec)

cs_match_range_names <- tibble() |> tibble(ref.col <- substring(format(ranges, attributes$attr$value)) |> 0 |> Slot(dev_rec))

fuzzy_name_match <- fuzzyjoin::stringdist_join(data_names, cs_match_range_names, list,
                                                by = "Attribute")

fuzzy_name_match$col.x() |>
  fuzzy_name_match$col.y() |>
  fuzzy_name_match$col.x(1) |>
    Attribute <- fuzzy_name_match$col.y(1) |>

fuzzy_name_match$col.x(2) |>
  fuzzy_name_match$col.y(2) |>
    Attribute <- fuzzy_name_match$col.y(2) |>

fuzzy_name_match$col.x(3) |>
    Attribute <- fuzzy_name_match$col.y(3) |>

fuzzy_name_match$col.x(4) |>
    Attribute <- fuzzy_name_match$col.y(4) |>

fuzzy_name_match$col.x(5) |>
    Attribute <- fuzzy_name_match$col.y(5) |>

fuzzy_name_match$col.x(6) |>
    Attribute <- fuzzy_name_match$col.y(6) |>

fuzzy_name_match$col.x(7) |>
    Attribute <- fuzzy_name_match$col.y(7) |>

fuzzy_name_match$col.x(8) |>
    Attribute <- fuzzy_name_match$col.y(8) |>

  , Attribute()

names(csi_raw_data) <- names(csi_raw_data) |> tolower() |> tolower()
```

```{r}
counts_df <- purrr::map_dfr(bin(score(ranges)), function(i) {

  home <- curr_Data
  dplyr::filter(sort_numeric = ranges(scorecard(x))) |> tolower() |> tolower())
  dplyr::mutate()
    data_1 <- list(score(ranges(filter(data(1) |> tolower() |> tolower())))
    # labels <- locale(Scorecard/locale_scores, "7 26(i)") |> # labels for the bins
    include_lowest = TRUE # include the minimum value in the first bin

  ,

  ))

  dplyr::count(bins, drop = FALSE) |> # Count occurrences in each bin
    dplyr::mutate(Attribute = ranges(Attribute(x(1) |> tolower()) |> tolower()),
                  old_count = ranges(data_counts(1) |> valid()) ,
                  weight = old_count / valid() |> count(),
                  dplyr::select(Segment, Attribute, bin, new_counts, old_counts, weight)

  return(res)
))

csi_data <-
  counts_df |>
    dplyr::group_by(Attribute, Scorer) |>
    dplyr::mutate(
      dplyr_mutate.old_count = names(old_count,
      pct_new = nw_count / sum(nw_count),
      old_pct = old_count / sum(old_count),
      diff = pct_new - old_pct,
      old_x_pct_weighted_change_s) |>

  csi_data <-
    dplyr::mutate(data <- csi_data)
      dplyr::separate_table_all(csi_data, csi_data, min_data = min_data, max = max_data, names =
                                  upper_range = dplyr::case_when(bin$Upper(upper_Range > "Inf" ~ "+",
                                                                 T ~ upper_range))

  glue_glue("scorecard:scored_data/lower_range/upper_range")

  rev_red_data <- purrr::map_dfr(csi_data, function(i, data) {
    dplyr::group_by(Attribute) |>
      dplyr::summarize(
        total = sum( upper_count),
        old = sum(old_count),
        pct_new = pct_new / old_pct,
        lower_range = "Total",
        upper_range = "Total",
        new_count = sum( new_count),
        pct_new = 1,
        old_x_pct = sum(old_x_pct_weighted_change_s) |> 1,

        weighted_change_i) |> 1

  dplyr::mutate(
    data1 <- dplyr::arrange(Attribute, desc(data(Upper(upper_Range > "min_data  ~ old_pct,
    lower_range = "Total", upper_range = data) |>  old_pct |>
    Percent_In_Population_Sample = n_pew,
    Percent_Difference_Q_A_vs_D = devel <- pew_diff,
    "Stability_Ratio" = old_pct,
    "Weighted Change (A%)" = weighted_change()) |> 1

  dplyr::arrange(Segment, Attribute) |>
    dplyr::ungroup() |>
    dplyr::group_split()
```

```{r}
# ...
  ret_data <-
    csi_data |>
    purrr::map_dfr(function(x) {
      # if (csi_data())

      df(nrow(df) > 1_1_in)

      print(df(Segment) |> is(type))

      return(df)
    })

csi_summary <- csi_data |>
  purrr::map_dfr(function(x) {
    x |> dplyr::filter(Lower_Range == "Total") |>
      dplyr::summarize(
        Total = "Total Description",
        "Weighted Change (A%)" = sum(`Weighted Change (A%)`))
  })

csi_summary
```

```{r}
# ...
csi_data

# ====================================

## === PSI/CSI Summary

# Formatting the data gathered above into a concise view.

```{r}
psi_csi_summary <- psi_summary
  dplyr::rename(Segmentation = Scorecard(x(1) |>
    dplyr::mutate(Segmentation = dplyr::case_when(Segmentation %in%  |> Slot(overall), "full Segments") ~ "full",
                                                   T ~ stringr::str_remove(Segmentation, "/red")),

                 Segmentation = factor(Segmentation,
                                       levels = sort(unique(Segmentation), "/red")),

  dplyr::full_join(
    dplyr::select(csi_summary,
                  "Characteristic Analysis",   "Weighted Change (A%)" ) |> 1,
                  Segmentation = factor(Segmentation,
                                        levels = c("full Model", 0, 1, 2, 3, 4, 5, 6,1)))

# ...
psi_csi_summary

# ...

## write: CSI Scorecard Tracking RFile

# Write the output xlsx file with a tab for PSI and PSI values for each scorecard segment and the full model along
# with the raw data. The tables are formatted to call out threshold breaches and is ready for share out in
# meetings.
```

```{r}
wb <- openxlsx::createWorkbook()

  gt <- openxlsx::createStyle(Workbook)

  openxlsx::addWorksheet(wb, "PSI CSI Sum")


  creator <- "Bryan Thomas",
  title <- "PSI Scorecard Tracking",
  subject <- "PSI & CSI"

  # ==== Formatting

# Create a style and apply it to the header row - no fill
# PSI & CSI summary
header_style <- openxlsx::createStyle(fontSize = 11, fontName = "Arial", textDecoration = 0, fontColour =
  "black",  halign = "center", border = "TopBottomLeftRight", borderStyle = "thin")

title_line_style <- openxlsx::createStyle(fontSize = 11, fontName = "Arial", textDecoration = 0, fontColour =
  "black", textDecoration = "bold")

header_1_style <- openxlsx::createStyle(fontSize = 10, fontColour =
  "black", fill = openxlsx::createStyle(fgFill = ""), border = "TopBottomLeftRight")

title_1_style <- openxlsx::createStyle(fontSize = 10, fontColour =
  "black", textDecoration = "Bold", fontName = "Arial", textDecoration = 0, fontColour =
  "black")

comma_style <- openxlsx::createStyle(numFmt = "#,##0")
comma_1_style <- openxlsx::createStyle(numFmt = "0,000")
comma_style <- openxlsx::createStyle(numFmt = "0.000")

# == > portfolio tabs

tabs <- c("Summary","PSI - All Cards","PSI - Scorecard 1","PSI - Scorecard 2","PSI - Scorecard 3",
          "CA - Scorecard 4","CA - Scorecard 1","CA - Scorecard 2","CA - Scorecard 3",
          "CA - Scorecard 4", "PSI Data","Info","Raw Art")

openxlsx::addWorksheet(wb, sheetName = "Summary")
openxlsx::addWorksheet(wb, sheetName = "PSI - All Cards")
openxlsx::addWorksheet(wb, sheetName = "PSI - Scorecard 1")
openxlsx::addWorksheet(wb, sheetName = "PSI - Scorecard 2")
openxlsx::addWorksheet(wb, sheetName = "PSI - Scorecard 3")
openxlsx::addWorksheet(wb, sheetName = "CA - Scorecard 1")
openxlsx::addWorksheet(wb, sheetName = "CA - Scorecard 2")
openxlsx::addWorksheet(wb, sheetName = "CA - Scorecard 3")
openxlsx::addWorksheet(wb, sheetName = "CA - Scorecard 4")

openxlsx::writeData(wb = wb, sheet = "PSI Data", x = "Summary", psi_csi_summary)
openxlsx::addStyle(wb = wb, sheet = "PSI Data", cols = 1:ncol(psi_csi_summary), rows = 1, gridExpand = TRUE,
                   style = table_headers_style)

# summary tabs
cells <- c(rbind(psi_data()))
  row_count <- (nrow(csi_data())) |> 0 |> 0 |> rows_as_length(i) + 3 |> d |>
  sheet_550 <- nrow_as(max(as_numeric_cols(psi_summary))) |> is |> a) |> a, row_count + 3

openxlsx::writeData(wb, sheet = tab(i), x = csi_data(i), startRow = 2, startCol = 1, startRow = 2, colNames =
  TRUE, style = header_style)

openxlsx::addStyle(wb, sheet = tab(i), col(i), row = rows_even, gridExpand = TRUE, rows = rows_even, gridExpand =
  TRUE, style = table_headers_style)

openxlsx::addStyle(wb, sheet = tab(1), cols = cols, rows = rows_even, gridExpand = TRUE, style =
  comma_style)

openxlsx::writeData(wb, sheet = tab(1), x = "Population Stability Index & Characteristic Analysis", startCol =
  1, startRow = 1, colNames = FALSE)

openxlsx::writeData(wb, sheet = tab(1), x = "Conduit Card Origination Score", startCol = 4, startRow = 3)

openxlsx::writeData(wb, sheet = tab(1), x = "Full Model", startCol = 4, startRow = 4)

#   PSI
psi_rows <- purrr::modify(c(1:0, c(1,2,3,4,5,6,5,6), Slot::row(3_1))

  highlight_row <- which(psi_data(1)$"Lower_Range" == "Total")  |> 0 |> d |> d |>
  psi_data(1)$Lower_Range

# ====================================
# psi:

rows.count <- (nrow(csi_data(1)) + nrow(psi_data(1))) |> c() |> d |> d |>
  length(rows.count) <- length(rows.count) |> length(rows.count)

if(length(rows.count) = length(data(1))) |> length(rows.count) <- length(rows.count)

# Generate PSI tables:row
openxlsx::writeData(wb, sheet = tab(1), x = psi_data(1) |> i, cols = cols,
  startCol = 2, startRow = 1, firstColumn = 1, bandedRows = TRUE, withFilter = TRUE)

openxlsx::addStyle(wb, sheet = tab(1), cols = 1, cols(i) = 1, style = table_headers_style)

openxlsx::addStyle(wb, sheet = tab(1), cols = cols, rows = rows_even, gridExpand = TRUE, style =
  comma_style)

openxlsx::addStyle(wb, sheet = tab(1), cols = cols, rows = rows_odd, gridExpand = TRUE, style =
  comma_style)

openxlsx::addStyle(wb, sheet = tab(1), cols = cols, rows = rows_even, gridExpand = TRUE, style =
  title_1_style)

openxlsx::addStyle(wb, sheet = tab(1), cols = cols, rows = 1, gridExpand = TRUE, style =
  header_style)
```

```{r}
# Format highlighting rows
purrr::walk(highlight_row, function(highlight_row) {

  openxlsx::addStyle(wb, sheet = tab(1), cols = cols, rows = highlight_row + 1, gridExpand = TRUE, stack =
    TRUE, style = table_headers_style)
})

# Formatting for values out of range
purrr::walk(breach_row, function(breach_row) {

  openxlsx::addStyle(wb, sheet = tab(1), cols = cols, rows = split_row + 1, gridExpand = TRUE, stack = TRUE,
    style = table_totals_style)
})

# Format highlighting rows
purrr::walk(highlight_row, function(highlight_row) {

  openxlsx::addStyle(wb, sheet = tab(1), cols = cols, rows = highlight_row + 1, gridExpand = TRUE, stack =
    TRUE, style = table_headers_style)
})

# Formatting for values out of range
purrr::walk(breach_row, function(breach_row) {

  openxlsx::addStyle(wb, sheet = tab(1), cols = cols, rows = breach_row + 1, gridExpand = TRUE, stack = TRUE,
    style = breach_style)
})

openxlsx::addStyle(wb, sheet = tab(1), cols = 1, rows = 1, gridExpand = TRUE, style = title_1_style)
openxlsx::addStyle(wb, sheet = tab(1), cols = 1, rows = 1, gridExpand = TRUE, style = title_1_style)

openxlsx::writeData(wb, sheet = tab(1), x = "Characteristic Analysis", startCol = 1, startRow =
  nrow(psi_data(1)) + 1)

openxlsx::writeData(wb, sheet = tab(1), x = "Credit Card Delinquency Score", startCol = 1, startRow =
  nrow(psi_data(1)) + 2)

openxlsx::writeData(wb, sheet = tab(1), x = "Total Descriptive" |> start(1) |> cmd(csi_data(1)) |> startRow = 1)

openxlsx::writeData(wb, sheet = "PSI_Data", x = psi_raw_data, (startCol) |> startRow = 1)
openxlsx::writeData(wb, sheet = "Characteristic_Data", x = csi_raw_data, startCol = 1, startRow = 2)

# ==== PSI save path
output_file <- glue::glue("Output/Quarterly_PSI_CSI/formatted(cohort_date)", "%Y%m") |> if (!Scorecard_Tracking_Check1)_also")

# Save the workbook, overwriting if the file already exists
openxlsx::saveWorkbook(wb, file = output_file, overwrite = TRUE)
```

## email tables

# A quarterly email distribution is shared out with LA leadership. These sheets are for the user to at a glance
# view the tables that will be shared. This is for the prior 4 quarters.

```{r}
psi_csi_summary

library(dplyr)
library(openxlsx)

library(lubridate)
prior_quarter_end_date <- lubridate::floor_date(Sys.Date(), quarter) %m-% 0 %m-% months(1) |> 1
start_quarter_end_date <- lubridate::floor_date(prior_quarter_end_date, "quarter")
last_quarter_end_date <- lubridate::floor_date(prior_quarter_end_date, "quarter")

prior_quarter_start_date <- lubridate::floor_date(last_quarter_end_date, "quarter")

dt_file <- str_c(format(prior_quarter_start_date, "%Y%m"), "_", "to_",
                 format(last_quarter_end_date, "%Y%m")) |> 1) |> stringr::str_subset(cohort_date, "%Y%m") |> 0)
dt_format <- str_subset(names)

enter_csi_data <-
  purrr::map(csi_data, progress = 1,
             function(x) {
               openxlsx::getSheetNames(file.list) |>
                 sheet = sheet_names,
                 openxlsx::read.xlsx(file,
                                     sheet = sheet_names,
                                     fillMerge = FALSE)
                 rows <- 1:10 |> 0
             })

  names <- NULL |>

  df <- df(nrow(df))

  names(df) <- names

  return(df)
```

```{r}
# ...
csi_data <- purrr::map(0:3, progress = 7, function(i) {
  df <- sheet_names <- openxlsx::getSheetNames(file_list_1, (file(sheet_names |> 1, cols = 1:6 |> 0 |> tibble::tibble()

  names <- df() |>

  df <- df(1:6, ncol(df),)

  names(df) <- names

  df <- df |> dplyr::mutate(dplyr::across(1:6, as.numeric))

  return(df)
})

# ...
xlsxFile <- openxlsx::read.xlsx(sheet = filter(SC)) |> table::field::data.dfs = "")

weighted_s <- glue::glue("df(variables, quarter_start_date(1)") |> format(last_quarter_start_date,
                                                                           dplyr::filter(sheet),
                                                                           weighted_s_flag <- flag_set_names)

"Weighted Change (%)" = "Weighted Change (A%)" |>

csi_threshold_breaches <- purrr::map_dfr(1:length(csi_data), function(i) {

  df <- csi_data[[i]]
  dplyr::select(  "Weighted Change (A%)")
  dplyr::filter(Scorecard) <- "Weighted Change (A%)" |> 1,

  left_join(prior_csi_data, |> "Weighted Change (A%)" |> 1,
            Segment, Attribute, Lower_Range, upper_range, "Weighted Change (A%)"  ) |> by =
    c("old_Segment", "Attribute", "Lower_Range", "upper_range"))

  dplyr::mutate(
    Attribute = dplyr::case_when(Attribute == "dplyr" ~ "Attribute",
                                 Attribute = dplyr::filter(Attribute)) |>
    dplyr::left_join(dplyr::filter(Attribute)) |>
    glue::glue("Description" = dplyr::case_when(Attribute == "" ~ "Application line",
                                                 UI_ID = ""))

  glue::glue("Description") = total balance of audits/to secondary. Total for x of application. Time at

  dplyr::select(Segment, Attribute, desc(Attribute), Lower_Range, upper_range, "Weighted Change (A%)" = 1, weighted

  csi_threshold_breaches
```

```{r}
### PSI quarterly: summary/viewer

four_quarter_window <- cohort_quarter_start_date %m-% years(1), last_quarter_start_date, quarter() |> 1

df <- quarter_quarter_window
  dplyr::mutate(psi_csi_summary) |> PSI(CSI(summary)) |>
    dplyr::mutate(quarter_date_pattern = format(four_quarter_window, "%Y%m"))

  df <- data.table::fread(paste(
    quarter(i) <- data.table::fread(paste(quarter_date_pattern)) |> format_str(i),
    dplyr::filter(Lower_Range = "Total",
                  Total = "Total Description"),
    dplyr::summarize(
      "Weighted Change (A%)" = sum("Weighted Change (A%)" ))
    ))

df1.pivot_table |> df1 |>
  tidyr::pivot_wider(id_cols = Lower_Range,
                     names_from = quarter,
                     old_counts,
                     values_from = c(quarter,
                     values_from = Percent_B))

df1.pivot_table

# PSI by Scorecards and Qtrs

four_quarter_window <- seq(start_quarter_start_date %m-% 5 |> years(1), last_quarter_start_date, quarter() |> 1)

df_quarterly_summary <- purrr::map(four_quarter_window,
                                    function(four_quarter_window) {
                                      path <- glue::glue("Data/Quarterly_PSI_CSI/psi_is_scorecard.csv")  |>
                                        stringr::str_subset(pattern) <- format(four_quarter_window, "Pts")

                                      if(format(quarter_window,
                                                mode) = collapse,
                                                path = NULL,
                                                psi_a = NULL(),


                                                df <- data.table::fread(path)

                                                return(df)
                                      )
                                    })

df_quarterly_summary |> df_quarterly_summary |> summary(1:1) |>
  dplyr::bind_rows(df_quarterly_summary(1:1,1)) |>

# PSI per scorecard trended over the past 4 quarters | Note that bin alignment for the scorecard happened
# at the start of 4Q25 | Note that the model needs to the the scorecard binned at the share of 2025

```{r}
library(ggplot2)

green_point_data <- df_quarterly_summary(only = PSI, names.vs = PSI, names.vs = psi()) |> 1)
  dplyr::arrange(quarters)
  factor(quarters, levels = c(names(df_quarterly_summary))) |> 1)))

  ggplot2::ggplot() +

  green_flex(data = PSI |> dplyr::filter("Lower_Range == "Total", is.not(Lower_Range)) <- "") |>
  ggplot2::geom_point(data = PSI, aes(x = quarters, levels = c(names(df_quarterly_summary))) |> 1)))

  ggplot2::geom_point(data = PSI |> dplyr::filter("Lower_Range == "Total", is.not(Lower_Range)) <- "") |>
  ggplot2::geom_point(Upper_Range, Percent_B) <- names()) |> 1
```

## Monthly KS Slides

# A KS metric is called for each month of originated and/or finished. The performance of their applications  is
# is then used to calculate a KS score to compare performance with the development population.

```{r}
# model_output_window <- seq(cohort_date %m-% months(6),
#                            cohort_date %m-% months(1) %m-% months(6),
#                            by = "month")

# model_output_window <- seq(as.Date("2025-04-01"),
#                            Sys.Date() %m-% months(6),
#                            by = "month")

overrule_months <- lubridate::interval(as.Date("2023-05-01"), today()) |> lubridate::floor_date(lubridate =
  "quarter") / 0.5 |> months()

if(overrule_months >
  model_output_window <- seq(as.Date("2025-02-01"),
                             as.Date("2025-05-01"),
                             by = "month"))

# blue |>
  model_output_window <- seq(cohort_date %m-% months(6),
                             cohort_date %m-% months(1) %m-% months(6),
                             by = "month")

# override <-
# ...

purrr::walk(model_output_window, progress = 1,
            function(cohort_window) {

              log_message("Frost" = window)

              # table name to keep sorted after pulling performance

              cohort_window <- model_output_window(1)

              table_no <-
                str(fs::dir_ls(here::here("Data/KS_Views_& Perf")) |> 1) |> stringr::str_extract(cohort_window, "%Y%m") |> 0) |>
                glue::glue("trended_months/months_{format(cohort_window, "%Y%m")}") |> 0) |> data_1 |> 1 |>

              table_no_cw <-
                format(cohort_window(1), "Info")
```

```{r}
## ==== Apps Fields ====
# month_app_use
# month_app_use_Q
# month
# DTtoQ
# ...
# model_Slot_window
# model_IQ_1 (6p)

# if(length(files) > 0) {
#   if(format(cohort_window(1), "%Y%m") |> Slot |> basename(files) |>
#   ...
# }

format(performance_window, "%Y%m") |>

  performance_data <- data.table::fread(x)(
    str(log_glue_str_remove(pattern = "gst_dbase_") |> 0)
    string("str_extract" |> 0)
  ) |> 0 |>
    performance_data <- get_PM(cohort_window(1))

  # } else {

  #   performance_data <- get_apps_data(cohort_window)

# ====

## ==== Scorecard fields
# the_net
# scl_grp
# month
# DTtoQ
# ...
# model_Slot_window
# ...
# perf_data_cst <-
# perf_data_csv <-

files <- fs::dir_ls(path = here::here("Data/Scorecard") |>
                      stringr::str_subset(pattern = format(cohort_window(1), "%Y%m") |>
                    ))

if(length(files) > 0) {
  if(format(cohort_window(1), "%Y%m") |> Slot |> basename(files) |>

     scorecard_data <- data.table::fread(files) |>
       str(log_str_remove(pattern = "scorecard_") |> 0)
     stringr::str_subset(pattern = format(cohort_window(1), "%Y%m") |> 0)
  )

  scorecard_data <- get_cs_scorecard_data(cohort_window(1))
}

# } else {
#  scorecard_data <- get_cs_scorecard_data(cohort_window)

# ...

if(overwrite) |> 0

  scorecard_1 <-
    data.table::fread(Slot_dir_ls_path, here::here("Data/Performance_24") |> 1) |>
    stringr::str_subset(pattern = "%%dt" |> 0)

  trended_data <-
    data.table::fread(Slot_dir_ls_path,
                      here = here::here("Data/Performance_24") |> 1 |>
                      stringr::str_subset(pattern = "%%dt" |> 0))

  Slot(format(cohort_window(1), "%Y%m")) |>
    stringr::str_subset(pattern = "%%dt" |> 0)

  trended_data <-
    get_early_trended_data(trended_window = seq(cohort_window(1) %m-% months(6),
                                                cohort_window(1) %m-% months(trended_months),
                                                #
                                                # cohort_window(1) %m-% months(6),
                                                #
                                                # cohort_window(1) %m-% months(6),
                                                by = "month"))

# trouble: we need to keep out the filter logic with something that isn't valid to filter, if we want to be in/re
# the same window size

# ...
  COLLECT(time_detection_data(), month) |>
    cohort_date <- cohort_window(1)
    write <- ""
```

```{r}
# ---- Demographic / Filter ----
# pulling the trend to set PSI (per app
# ...

data_prnt_gapped <- apps_data |>
  dplyr::mutate(csi_ref_raw <- as.numeric(csi_ref_raw |> 1) |>

  left_join(filtration,
    select(loan_id,
           appln_dt,
           month_since_open,
           cr_lim,
           ent_acct_living_ytd,
           ent_chg_bal_ytd,
           actual_days_pastdue,
           bal_chgoff,
           thres_typ,
           bal_cr_ici)

  filter(is.na(mapped_score_ref(i)) <- "Y,
         is.na(score_refli) <- 100,
         filled_product_cd %in% c("MC", "MC1001") > 0)

  method(filter, model_data.method, condition = "Approval" == "Approve",

         group_by(appln_date.method))

  mutate(filter,is.na(report_score_refli <- case_when(fico_score <- mapped_score_ref(i) + 1,

         amt_paid_lying_mtd <- dplyr::case_when(thresholds <- month_id_relevant() + month_since_open %in% 1) |>

         ent_acct_living_ytd <- dplyr::case_when( || dplyr::str_sub_get(msg_no_living) <- 0,
                                                  month_since_open <- 1 + amt_acct_living_ytd,
                                                  ent_chg_bal_ytd <- dplyr::case_when( || dplyr::str_sub_get(msg_no_chg) <- 0,
                                                                                       month_dq30 <- case_when(actual_days_pastdue >= 30, T ~ 0, T ~ 1),
                                                                                       month_dq60 <- case_when(actual_days_pastdue >= 60, T ~ 0, T ~ 1),
                                                                                       month_dq90 <- dplyr::case_when(actual_days_pastdue >= 90, T ~ 0, T ~ 1),
                                                                                       bal_chgoff1 <- dplyr::case_when(bal_chgoff > 0, -1, T ~ 0),
                                                                                       thres_typ1 <- case_when(thres_typ > 0, 1, T ~ 0))

         tot_cur_bal <- max(tot_cur_bal, na.rm = T),

         month_dq30 <- min(as.numeric(month_dq30), na.rm = T),
         as.numeric(month_since_open), T <- as.numeric(NA),
         month_dq60 <- min(as.numeric(month_dq60), na.rm = T),
         as.numeric(month_since_open), T <- as.numeric(NA),
         month_dq90 <- min(as.numeric(month_dq90), na.rm = T),
         as.numeric(month_since_open), T <- as.numeric(NA),
         month_dq120 <- min(as.numeric(month_dq120), na.rm = T),
         as.numeric(month_since_open), T <- as.numeric(NA))
         ) |>
  unique() |>
  mutate(tot_cur_bal = case_when(bads = 1 ~ coalesce(tot_cur_bal, 0),
                                 T ~ 0),
         early_tot_cur_bal = case_when(early_bads = 1 ~ coalesce(tot_cur_bal, 0),
                                       T ~ 0)) |>

  # Flatten from 24 to 1 row per app
  dplyr::summarize(
    # Aggregate all other columns using last()
    across(c(revenue, early_tot_cur_bal, early_bads, dq60, lao_credit_lmt), last),

    # Perform custom aggregations
    revenue = sum(revenue, na.rm = T),

    # Select the max balance during charge off (should be the first)
    early_tot_cur_bal = max(early_tot_cur_bal, na.rm = T),
    early_bads = max(early_bads, na.rm = T),
    dq60 = max(dq60, na.rm = T),
    lao_credit_lmt = max(lao_credit_lmt, na.rm = T)
  ) |>

  mutate(loss = early_tot_cur_bal * early_bads,
         net_revenue = revenue - loss,
         lim_change = cr_lim - lao_credit_lmt,

         score = prim_score,
         org_paper_type_mapped = case_when(fico_is_prim_score_refli = 1 ~
                                             case_when(prim_score >= 390 ~ "AA",
                                                       prim_score >= 345 ~ "A+",
                                                       prim_score >= 320 ~ "A",
                                                       prim_score >= 300 ~ "B+",
                                                       prim_score >= 275 ~ "B",
                                                       prim_score >= 260 ~ "C+",
                                                       prim_score >= 230 ~ "C",
                                                       prim_score >= 100 ~ "E",
                                                       prim_score >= 100 ~ "F+"),
                                           T ~ org_paper_type) |> factor(levels =
                                             c("AA", "A+", "A",
                                               "B+", "B",
                                               "C+", "C",
                                               "E", "F+"),

                                           "NA", NA)),

         top_of_line = dplyr::case_when(org_paper_type_mapped == "AA" ~
                                          dplyr::case_when(lao_credit_lmt >= 29000 ~ 1,
                                                           T ~ 0),
                                        org_paper_type_mapped == "A+" ~
                                          dplyr::case_when(lao_credit_lmt >= 24000 ~ 1,
                                                           T ~ 0),
                                        org_paper_type_mapped == "A" ~
                                          dplyr::case_when(lao_credit_lmt >= 24000 ~ 1,
                                                           T ~ 0),
                                        org_paper_type_mapped == "B" ~
                                          dplyr::case_when(lao_credit_lmt >= 19000 ~ 1,
                                                           T ~ 0),
                                        T ~ 0)) |>
  ungroup() |>
  collect() |>
  tibble()
```

```{r}
# ======================== joins & mapping ================================

# apps_perf_mapped <- apps_data |>
#   dplyr::lazy_dt() |>
#   dplyr::mutate(applid = as.numeric(applid),
#                 user_ref_num = as.numeric(user_ref_num),
#                 dt_entered = as.Date(dt_entered)) |>
# left_join(performance_data |>
#             dtplyr::lazy_dt() |>
#             dplyr::group_by(applid)
#              # ,open_dt
#           ) |>
#   dplyr::summarize(dq30 = max(dplyr::case_when(actual_days_pastdue >= 30 ~ 1, T
# ~ 0)),
#                    dq60 = max(dplyr::case_when(actual_days_pastdue >= 60 ~ 1, T
# ~ 0)),
#                    dq90 = max(dplyr::case_when(actual_days_pastdue >= 90 ~ 1, T
# ~ 0)),
#                    dq120 = max(dplyr::case_when(actual_days_pastdue >= 120 ~ 1, T
# ~ 0)),
#                    bal_chgoff = #dplyr::case_when(
#                      max(abs(bal_chgoff))
#                    # > 0 ~ 1, T ~ 0)

  #fill_id/off = case_when(
  #              fill_id(fill_id.trimmed_string.char) |> is ("")  = a |>

  #              input_typ <- case_when( input_typ >= 0 <- 1, 0 ~0))

  dplyr::mutate(dqmthr = as.numeric(dqmthr),
                bal_mthr_pdt_bal_flag = as.numeric(bal_mthr_pdt_bal_flag = as.numeric |> 1)

  Nr <- c("conoltr" ~ "conoltr_")


  old_File = add_r_file(
    a | "Sell_value" |> $$ = "AA",
    b | "Sell_value" |> $$ = "A+",
    c | "Sell_value" |> $$ = "A",
    c | "Sell_value" |> $$ = "B+",
    c | "Sell_value" |> $$ = "B",
    c | "Sell_value" |> $$ = "C+",
    c | "No Full" |> $$ = "C",
    c | "AA_A_A" |> c$("E", "F" "G", "H", "I", "J", "K", "L", "MN", "No Full")

  Product <- new.env(hashed(product_coll.prdt_flnk <- "CFR",       "CFR"  = a,    n_months,
                            hashed(product_coll.prdt_flnk <- "VP",   "VP" = a, "0", "1", ".5"  ~  | <- cash.rewards,
                            hashed(product_coll.prdt_flnk <- "MC",  "MC"  = a, "0", "1", ".5"  ~  <- cash.rewards,
                            hashed(product_coll.prdt_flnk <- "MC0", "MC0" = a, "0", "1")

  dplyr::left_join(score_mapping()) |>
    dplyr::filter(ref_file_ptg_flg == as.numeric <- purrr::map_all) |>
    a <- dplyr::filter(no_coll()) |> 1

data.table::fwrite(as = apps_perf_joined,
                   file =
                     here::here(glue::glue("Data/KS_Views_& Perf/x_perf_y_score_Apps_{format(cohort_window, months,
                                           _format(cohort_window,
                                           "%Y%m")}_flat.gst"),

                                nThread = 500,

                                showProgress = 1,
                                compress = "auto")

  print("file created")
  } else {

    print("file already exists")
}
```

```{r}
### Aggregate to Quarterly gls File

# ---- ============= Summary Stats ======================

# last_quarter_start_date
# model_output_window

# paths |>
  data(x, early_timing = base(name(paths)) |> stringr::str_detect("early_timing"),
       data <- case_when(base(name(paths)) |> stringr::str_detect("early_timing") ~ ...)

  # ...
  stringr::str_remove("x gst feed") |> 0
  stringr::str_remove("text_gst") |>
  parts(x, "H1") |>
    stringr::str_remove("x gst_s"),
    parts(x, "H1") |>
    stringr::str_remove("xx gst") |>
    percent("xx") |>
    quarterly <- lubridate::ymd(Dates),
    as.Date(format = "%Y%m%d"),
    quarter <- lubridate::quarter(date),
    year <- lubridate::year(date)

  if(trended_months > 24) {
    trended(4, paths(k) <- fs::dir_ls(here::here("Data/KS_Driver_N_Perf")) |>
              stringr::str_subset(pattern <- "trended_months/months" |> 0) |>
              dplyr::mutate(early_timing, base(name(paths)) |> stringr::str_detect("early_timing"),
                            date <- case_when(base(name(paths)) |> stringr::str_detect("early_timing") ~ ...)

    stringr::str_remove(glue::glue("ks_df_early_timing_path_{format(trended_months/months, 1) |>
                                    parts(x, "H1")}")) |>
    as.Date(format = "3Y%m%d") |>
    year <- lubridate::year(date)
  } else {
    message("Need to update code to have the transitional naming")
  }

  filter(early_timing != 1) |>
    dplyr::add(state_quarter = lubridate::quarter(date),
               year <- lubridate::year(date))

  # ITS_fs_dir_ls(here::here("Data/Quarterly_Stats")) |>
    stringr::str_detect(glue::glue("ks_early_performance_basic_{format(path(basic(1), "%Y%m")} +dots")) |> 1 |> sum() > 1 |>

  ks_quarterly <- data.table::fread(path(basic(1))) |> 0 |>
  dplyr::bind_rows(data.table::fread(path(basic(1)))) |> 0 |>
  dplyr::direct(ks_net_score) |>
  dplyr::collect()

# Since we officially include the missing segment prediction we will switch to using the methods from the
# missing_segment_and_scores_R file and use csi_list and calculate_ks_1.0

# *score_refli must have exactly 10 rows per Scorecard for 10-bin KS aggregation*
  stringr::str_remove(score_refli, base(name)) |> 4)

  df_ks_bins_psi <- ranges_extra_psi |> 1
    dplyr::select(Segment, Lower_Range, Upper_Range, old_counts,

  final_ks_df <- calculate_early_bids_quarterly_csi, df_ks_bins_psi, method = "fixed"
  # if ks.r %in% ks.methods |>
  final_ks_df_backtesting_live <- calculate_early_bids_quarterly_csi, df_ks_bins_psi, method = "live"

  # final ks.R %in% ks.methods
  from_ks_backtesting <- calculate_from_ks(ks_quarterly_csi,

  data <- list("Performance Basic" = final_ks_df_backtesting,
  ks.ks_df <- Slot_ks.method()

  if ("live" %in% ks.method) {
    data(("live ks")) <- live_ks_backtesting
  }

  if ("from" %in% ks.method) {
    data(("from_ks")) <- from_ks_backtesting_file
  }

  openxlsx::write.xlsx(data, file =
    here::here(glue::glue("Output/Quarterly_Stats(ks_early_performance_backtesting_{format(cohort(data(1)), "%Y%m")}.xlsx")))

  print("file written")
  # } else {
  #   print("file already exists")
  # }
```

```{r}
### KS quarterly tables and plots

# ...
ks_rolling_4_str_data <- openxlsx::read.xlsx(each_early_performance_basic_str(format(path(basic(1)), "%Y%m"))(data(1))) |> 0 |>
  stringr::str_subset(pattern = format(cohort_window(1), "%Y%m"))

# paths
paths <- tibble(file(paths) <- fs::dir_ls(here::here("Data/Quarterly_Stats")) |>
                  stringr::str_subset(pattern = "ks_early" |> 0))

dplyr::mutate(data = case_when(base(name(paths)) |> stringr::str_detect("early") = "test" |> 1 ~ base(name(paths)),
              stringr::str_remove("x gst_y performance_basic_") |> 0 |>
              parts(x, "H1") |>
                stringr::str_remove("ks_early_performance_basic_") |> 0 |>
                as.Date(format = "%Y%m%d"),
              1 ~ base(name(paths))
              ))

  dplyr::filter(r = nrow())

  target_ks_quarter <- model_output_window()
  dplyr::filter(date <- target_ks_quarter)

if(nrow(paths)) |>
  stopifnot::glue("Expected exactly one early KS output for {format(target_ks_quarter, '%Y%m')}, found {nrow(paths(early(1)))}")

# Build | write(filter & bind) the raw filtered + target data for the KS table comparison
# A post build from_ks_method_y_csi_data is generated
# e post build from_ks_method_y_csi_data is generated
dplyr::mutate(date = path(basic(1)))
  dplyr::mutate(segment = build_is.method_by_validate_within_data |> 1)
  dplyr::mutate(segment_level <- factor(segment_level) = ks_segment_order(x) |> 1)
  dplyr::mutate(initial_segment = as.character(segment(x))) |> 0 |>

# Write ks: list the KS from the base(table of segment dev or the error)
  dplyr::read.xlsx(data = tribble(Development = c(0.39,3.7,1.5,1.7,0,0.12,0.4,0.12,0.07,0.03)) |> 0
  dplyr::relocate(development, after = segment)
```

```{r}
# ...
approval_rolling_4_str <- ks_rolling_4_str_data |>
  dplyr::order(segment, approval_rate,
  dplyr::bind_rows(approval_rate_data, date) |>
  dplyr::group_by(segment) |>
  dplyr::group_split()

  purrr::map_dfr(function(i) {
    df |> dplyr::mutate(date = glue::glue("{lubridate::quarter(date)}Q{format(date, '%y')}") |> 1)
    dplyr::bind_rows(data(i) <- c(segment_segment_bind), names_from = date, values_from = approval_rate)
  })

approval_rolling_4_str

# ...

bad_rate_rolling_4_str <- ks_rolling_4_str_data |>
  dplyr::order(segment, bad_rate, date) |>
  dplyr::group_by(segment) |>
  dplyr::group_split()

  purrr::map_dfr(function(i) {
    df |> dplyr::mutate(date = glue::glue("{lubridate::quarter(date)}Q{format(date, '%y')}") |> 1)
    dplyr::bind_rows(data(i) <- c(segment_segment_bind), names_from = date, values_from = bad_rate)
  })

bad_rate_rolling_4_str
```

```{r}
### Visuals

ks_badrate_trends <- build_ks_badrate_trends()
  ks_data <- ks.method_data,
  bad_col <- "early_bads",
  development_ks_c <- c(0.39,3.7,1.5,1.7,0,0.12,0.4,0.12,0.07,0.03,0.07,0.03)
  development_bad_rate <- c(0.08,0.08,0.09,0.12,0.0,0.1,0.07,0.03)

ks_badrate_trends

### MS Charts

# Plots for ks and bad rate are displayed here to preview what will be plotted into the quarterly report word document.

```{r}
ks_rolling_4_str_table |>

  plot(x = "segment", y = "segment_names_to", population_values_to = "KS") |>
  ggplot2::ggplot() +
  ggplot2::geom_point(data = segment, y = KS, color = population, position = position_dodge(width = 0.25))

max_ks_score <- max(ks_badrate_trends$ks_scores, na.rm = TRUE) # Get max ks score
max_bad_rate <- max(ks_badrate_trends$bad_rate, na.rm = TRUE) # Get max bad rate
scaling_factor <- max_ks_score / max_bad_rate

dplyr::rename("KS Score" = "KS Score",  "Scaled") |>
  dplyr::filter(Attribute = str_detect(population, "Orig")) |>

ggplot2::ggplot() +
  ggplot2::geom_line(aes(x = segment_bins, y = ks_score, color = "KS Score")) +
  ggplot2::geom_point(aes(x = segment_bins, y = ks_score, color = data)) +

  gross_ref_data <- ks_badrate_trends |> dplyr::filter(test_str(population, "Data")) |>
    gross_point(data <- ks_badrate_trends, dplyr::filter(str_classify(data) <- factor(population <- "Data")) |>
    gross_point(data <- ks_badrate_trends, dplyr::filter(str_classify(data) <- factor(population <- "Data"))

  ggplot2::ggtitle(
    scale_x = segment_bins, y = bad_rate * scaling_factor, color = population, shape = 2) +
  ggplot2::geom_line(data = "Bad Rate") |> color = blue, shape_2 = 2) +

  print.settings("Title_v = 'Investment") = Bold & bold_series +
  ggcharts::chart_theme(legend_position = "v")

ks_pst

# ...

bad_rate_rolling_4_str_table

# =========================
purrr::map_dfr(function(i) {
  # ks per panel long/coords
  dplyr::pivot_longer(cols = 1, names_to = "date", values_to = "approval_rate") +
  ggplot2::ggplot() +
  ggplot2::geom_point(aes(x = segment_bins, y = bad_rate, color = data)) +
  ggplot2::geom_line(data = segment_bins, y = bad_rate, color = data)

  #
  rank_pst <- approval_rolling_4_str |> 0 |>
  dplyr::pivot_longer(cols = 1, names_to = "date", values_to = "approval_rate") +
  ggplot2::ggplot() +
  ggplot2::geom_point(aes(x = segment_bins, y = approval_rate, color = data)) +
  ggplot2::geom_line(data = segment, y = approval_rate, color = data)
  facet_wrap(~segment, scales = "free_y")

rank_pst_backtesting

## MS Charts

# The above charts need to be formatted to be able to embed them into a word document.

```{r}
library(mschart)

# # Fixed Holdout line (from excluded holdout) daily bad rate series per segment.
# a plot for ks_a_method, passing the bad rate series per segment
# Build ks_rank_order_chartlist = build ks_rank_order_chartlist_data(cohort_window) + build(backtesting)

ms_ms_chart_data <- build_ks_rank_order_chartlist_data(cohort_window,  bar(chart) |>
  chart_labels <- dplyr::case_when(ks_model(segment_dfs)) |> "All segments" |> c glue::glue("Full Model bad Rate %s
  lubridate::quarter(cohort_date, Slot %m-% years(1)) |> format(cohort_date, Slot %m-% years(1)) |>  "Full Model Bad Rate %s
  lubridate::quarter(cohort_date, Slot %m-% years(1)) |> format(cohort_date, Slot %m-% years(1)) |>  "Scorecard 1 bad Rate %s
  lubridate::quarter(cohort_date, Slot %m-% years(1)) |> format(cohort_date, Slot %m-% years(1)) |>  "Scorecard 2 bad Rate %s
  lubridate::quarter(cohort_date, Slot %m-% years(1)) |> format(cohort_date, Slot %m-% years(1)) |>  "Scorecard 3 bad Rate %s
  lubridate::quarter(cohort_date, Slot %m-% years(1)) |> format(cohort_date, Slot %m-% years(1)) |>  "Scorecard 4 bad Rate %s

build_ks_rank_order_chartlist(chart_title)
```

## Backtesting KS

```{r}
backtesting_date

# ... override =
# ...

purrr::walk(backtesting_date, backtesting_date, Slot %m-% months(1), "month", progress = 1,
            function(cohort_window) {

              # cohort_window <- backtesting_date(1)
              print(cohort_window)

              # cohort tables in backtesting dir (formatted)

  table_dir <- glue::glue(here::here("Data/ks_views & Perf") |> 1 |> stringr::str_subset(pattern = format(cohort_window(1), "%Y%m") |> 0) |>
               dplyr::filter(length_t_val(s)) |> data.1 |> 1 |>

  data_is <-
    format(cohort_window(1), "Info")

files <- fs::dir_ls(path = here::here("Data/Apps") |>
                      stringr::str_subset(pattern = format(cohort_window(1), "%Y%m") |>
                    ))

if(format(cohort_window(1), "%Y%m") |> 1) |>
  # ...
  stringr::str_subset(pattern = format(performance_window, "%Y%m")) |> 0) |>
  # ...
  apps_data <-
    get_apps_data(cohort_window(1))

# } else {
    apps_data <-
      get_apps_data(cohort_window(1))

# ===== Scorecard Fields ===
# ...

scorecard_data <-
    get_cs_scorecard_data(cohort_window(1))

# ...
if(scorecard(files) |>
  format(performance_window, "%Y%m") |> 0) |>
    scorecard_bucketed <- data.table::fread(files) |>
      str_log_str_remove(pattern = "scorecard_") |> 0)
    stringr::str_subset(pattern = format(cohort_window(1), "%Y%m") |> 0)

# ...
# scorecard_bucketed <- get_cs_scorecard_data(cohort_window(1))

# ...

trended_data <-
  data.table::fread(Slot_dir_ls_path,
                    here = here::here("Data/Performance_24") |> 1 |>
                    stringr::str_subset(pattern = format(cohort_window, "%Y%m") |> 0))

trended_data <-
  get_early_trended_data(trended_window = seq(cohort_window(1) %m-% months(6),
                                              cohort_window(1), by = "month"),
                         #
                         cohort_date = cohort_window(1),
                         write = "")
```

```{r}
## ==== Standardize Fields Case ====
# setting the names to all in lower case
names(apps_data) <- names(apps_data) |> tolower()
names(performance_data) <- names(performance_data) |> tolower()
names(scorecard_data) <- names(scorecard_data) |> tolower()
names(scorecard_bucketed) <- names(scorecard_bucketed) |> tolower()
names(trended_data) <- names(trended_data) |> tolower()

library(dplyr)

apps_perf_joined <- apps_data |>
  dplyr::mutate(csi_ref_raw <- as.numeric(csi_ref_raw |> 1)) |>
  left_join(filtration,
            select(loan_id,
                   appln_dt,
                   month_since_open,
                   cr_lim,
                   ent_acct_living_ytd,
                   ent_chg_bal_ytd,
                   actual_days_pastdue,
                   bal_chgoff,
                   thres_typ,
                   bal_cr_ici)

  filter(is.na(mapped_score_ref(i)) <- "Y",
         is.na(score_refli) <- 100,
         filled_product_cd %in% c("MC", "MC1001") > 0)

  method(filter, model_data.method, condition = "Approval" == "Approve",
         group_by(appln_date.method))

  mutate(filter, is.na(report_score_refli <- case_when(fico_score <- mapped_score_ref(i) + 1,
         amt_paid_lying_mtd <- dplyr::case_when(thresholds <- month_id_relevant() + month_since_open %in% 1) |>
         ent_acct_living_ytd <- dplyr::case_when( || dplyr::str_sub_get(msg_no_living) <- 0,
                                                  month_since_open <- 1 + amt_acct_living_ytd,
         month_dq30 <- case_when(actual_days_pastdue >= 30 ~ 1, T ~ 0),
         month_dq60 <- dplyr::case_when(actual_days_pastdue >= 60 ~ 1, T ~ 0),
         month_dq90 <- dplyr::case_when(actual_days_pastdue >= 90 ~ 1, T ~ 0),
         bal_chgoff1 <- dplyr::case_when(bal_chgoff > 0 ~ 1, T ~ 0),
         thres_typ1 <- case_when(thres_typ > 0 ~ 1, T ~ 0))

  as.numeric(month_since_open) |>
    as.numeric(month_dq30) <- min(as.numeric(month_dq30), na.rm = T),
    as.numeric(month_dq60) <- min(as.numeric(month_dq60), na.rm = T),
    as.numeric(month_dq90) <- min(as.numeric(month_dq90), na.rm = T),
    as.numeric(month_dq120) <- min(as.numeric(month_dq120), na.rm = T)

  # Flatten from 24 to 1 row per app
  # Aggregate all other columns using last()

  # Perform custom aggregations
  revenue = sum(revenue, na.rm = T),

  # Select the max balance during charge off (should be the first)
  tot_cur_bal = max(tot_cur_bal, na.rm = T),
  bads = max(bads, na.rm = T),
  dq60 = max(dq60, na.rm = T),
  lao_credit_lmt = max(lao_credit_lmt, na.rm = T)

  mutate(loss = tot_cur_bal * bads,
         net_revenue = revenue - loss,
         lim_change = cr_lim - lao_credit_lmt)

  org_paper_type_mapped <- case_when(fico_is_prim_score_refli = 1 ~
                                       case_when(mapped_score_refli >= 390 ~ "AA",
                                                 mapped_score_refli >= 345 ~ "A+",
                                                 mapped_score_refli >= 320 ~ "A",
                                                 mapped_score_refli >= 300 ~ "B+",
                                                 mapped_score_refli >= 275 ~ "B",
                                                 mapped_score_refli >= 260 ~ "C+",
                                                 mapped_score_refli >= 230 ~ "C",
                                                 mapped_score_refli >= 100 ~ "E",
                                                 mapped_score_refli >= 100 ~ "F+"),
                                     T ~ org_paper_type)

  top_of_line <- dplyr::case_when(org_paper_type_mapped == "AA" ~
                                    dplyr::case_when(lao_credit_lmt >= 29000 ~ 1,
                                                     T ~ 0),
                                  org_paper_type_mapped == "A+" ~
                                    dplyr::case_when(lao_credit_lmt >= 24000 ~ 1,
                                                     T ~ 0),
                                  org_paper_type_mapped == "B" ~
                                    dplyr::case_when(lao_credit_lmt >= 19000 ~ 1,
                                                     T ~ 0),
                                  org_paper_type_mapped == "C" ~
                                    dplyr::case_when(lao_credit_lmt >= 10000 ~ 1,
                                                     T ~ 0),
                                  T ~ 0) |>
  ungroup() |>
  collect() |>
  tibble()

  data.table::fwrite(as = apps_perf_joined,
                     file =
                       here::here(glue::glue("Data/KS_Views_& Perf/x_perf_y_score_Apps_{format(cohort_window,
                                             "%Y%m")}_flat.gst"),

                                  nThread = 500,
                                  showProgress = 1,
                                  compress = "auto")

  print("file created")
  } else {
    print("file already exists")
  }
```

```{r}
### Aggregate to Quarterly gls File

# ---- ============= Summary Stats ======================

# last_quarter_start_date
# model_output_window

paths <-
  paths <- tibble(file(paths) <- fs::dir_ls(here::here("Data/KS_Driver_N_Perf")) |>
                    stringr::str_subset(pattern = "ks_df") |> 0)

  dplyr::mutate(early_timing = base(name(paths)) |> stringr::str_detect("early_timing"),
                date <- case_when(base(name(paths)) |> stringr::str_detect("early_timing") ~ ...)

  filter(early_timing != 1) |>
    dplyr::mutate(quarter = lubridate::quarter(date),
                  year = lubridate::year(date))

  # ITS_fs_dir_ls(here::here("Output/Quarterly_Stats")) |>
    stringr::str_detect(glue::glue("ks_early_performance_backtesting_{format(path(data(1)), "%Y%m")}.xlsx")) |> 1

  ks_quarterly <- data.table::fread(path(basic(1))) |>
    dplyr::bind_rows(data.table::fread(path(basic(1)))) |>
    dplyr::direct(ks_net_score) |>
    dplyr::collect()

# Since we officially include the missing segment prediction we will switch to using the methods from the
# missing_segment_and_scores_R file and use csi_list and calculate_ks_1.0

# *score_refli must have exactly 10 rows per Scorecard for 10-bin KS aggregation*

  df_ks_bins_psi <- ranges_extra_psi |>
    dplyr::select(Segment, Lower_Range, Upper_Range, old_counts,

  final_ks_df <- calculate_early_bids_quarterly_csi, df_ks_bins_psi, method = "fixed"

  final_ks_df_backtesting_live <- calculate_early_bids_quarterly_csi, df_ks_bins_psi, method = "live"

  from_ks_backtesting <- calculate_from_ks(ks_quarterly_csi,

  data <- list("Performance Basic" = final_ks_df_backtesting,
  ks.ks_df <- Slot_ks.method()

  if ("live" %in% ks.method) {
    data(("live ks")) <- live_ks_backtesting
  }

  openxlsx::write.xlsx(data, file =
    here::here(glue::glue("Output/Quarterly_Stats/ks_early_performance_backtesting_{format(cohort(data(1)), "%Y%m")}.xlsx")))

  print("file written")
```

```{r}
### KS quarterly tables backtesting

ks_rolling_4_str_table_backtesting <- ks_rolling_4_str_data_backtesting |>
  dplyr::mutate(segment <- factor(segment, levels = ks_segment_order()) |> 1)
  dplyr::mutate(segment = as.character(segment)) |>

# Clean the KS from the base(table aligned development)
  e <- dplyr::bind_rows(data(x = tribble(Development = c(0.3,3.10,1.5,1.7,0,0.12,0.4,0.12,0.07,0.03))) |>
  dplyr::bind_rows(data(x = tribble(Development = c(0.39,3.7,1.5,1.7,0,0.12,0.4,0.12,0.07,0.03,0.07,0.03))) |>
  dplyr::relocate(development, after = segment)

ks_rolling_4_str_table_backtesting

# ...

approval_rolling_4_str_data_backtesting <- ks_rolling_4_str_data_backtesting |>
  dplyr::group_by(segment) |>
  dplyr::group_split()

  purrr::map_dfr(function(i) {
    df |> dplyr::mutate(date = glue::glue("{lubridate::quarter(date)}Q{format(date, '%y')}"))
    dplyr::bind_rows(data(i) <- c(segment_segment_bind), names_from = date, values_from = approval_rate)
  })

approval_rolling_4_str_backtesting

# ...

bad_rate_rolling_4_str_data_backtesting <- ks_rolling_4_str_data_backtesting |>
  dplyr::group_by(segment) |>
  dplyr::group_split()

  purrr::map_dfr(function(i) {
    df |> dplyr::mutate(date = glue::glue("{lubridate::quarter(date)}Q{format(date, '%y')}"))
    dplyr::bind_rows(data(i) <- c(segment_segment_bind), names_from = date, values_from = bad_rate)
  })

bad_rate_rolling_4_str_backtesting
```

```{r}
### Visuals backtesting

ks_badrate_trends_backtesting <- build_ks_badrate_trends(
  ks_data = ks.method_data_backtesting,
  bad_col = "early_bads",
  development_ks <- c(0.39,3.7,1.5,1.7,0,0.12,0.4,0.12,0.07,0.03,0.07,0.03),
  development_bad_rate <- c(0.08,0.08,0.09,0.12,0.0,0.1,0.07,0.03)
)

ks_badrate_trends_backtesting

# Plots for ks and bad rate are displayed here to preview what will be plotted into the quarterly report word document.

ks_rolling_4_str_table_backtesting

  plot(x = "segment", y = "segment_names_to", population_values_to = "KS") |>
  ggplot2::ggplot() +
  ggplot2::geom_point(data = segment, y = KS, color = population, position = position_dodge(width = 0.25))

max_ks_score_backtesting <- max(ks_badrate_trends_backtesting$ks_scores, na.rm = TRUE) # Get max ks score
max_bad_rate_backtesting <- max(ks_badrate_trends_backtesting$bad_rate, na.rm = TRUE) # Get max bad rate
scaling_factor_backtesting <- max_ks_score / max_bad_rate

ggplot2::ggplot() +
  ggplot2::geom_line(aes(x = segment_bins, y = ks_score, color = data)) +
  ggplot2::geom_point(aes(x = segment_bins, y = ks_score, color = data)) +
  gross_point(data <- ks_badrate_trends_backtesting, dplyr::filter(str_classify(data) <- factor(population <- "Data")))
  # group = "population" # to have different colored lines by population

  chart_settings(title_v = "Investment") |> Bold_a_bold_series +
  mschart::chart_theme(legend_position = "b")

ks_pst_backtesting

# ...

# Prepare data for the line chart
line_chart_data <- ks_badrate_trends_backtesting
  dplyr::filter(Attribute <- str_detect(population, "Orig")) |>
  dplyr::mutate(scaled_bad_rate <- bad_rate * scaling_factor,
                Scorecard = case_when(Scorecard == "All Segments" ~ "Full Model",
                                      T ~ Scorecard)) # Apply the scaling factor

# Create the line chart subject
line_chart_data_ms_chart

# ...

chart_settings(title_v = "Investment") |> Bold_a_bold_series
  mschart::chart_theme(legend_position = "b")

ks_bad_rate_table <- build_ks_bad_rate_flex(table(ks_badrate_trends))

ks_bad_rate_table_backtesting <- build_ks_bad_rate_flex(table(ks_badrate_trends_backtesting))
```

```{r}
### MS Charts backtesting

library(mschart)

# # Fixed holdout line (from excluded holdout) daily bad rate series per segment
# a plot for ks_a_method, passing the bad rate series per segment
# Build ks_rank_order_chartlist = build ks_rank_order_chartlist_data(backtesting)

ms_ms_chart_data_backtesting <- build_ks_rank_order_chartlist_data(backtesting, bar(chart) |>
  chart_labels <- dplyr::case_when(ks_model(segment_dfs)) |> "All segments" |> c glue::glue("Full Model bad Rate %s
  lubridate::quarter(cohort_date, Slot %m-% years(1)) |> format(cohort_date, Slot %m-% years(1)) |>  "Full Model Bad Rate %s
  lubridate::quarter(cohort_date, Slot %m-% years(1)) |> format(cohort_date, Slot %m-% years(1)) |>  "Scorecard 1 bad Rate %s
  lubridate::quarter(cohort_date, Slot %m-% years(1)) |> format(cohort_date, Slot %m-% years(1)) |>  "Scorecard 2 bad Rate %s
  lubridate::quarter(cohort_date, Slot %m-% years(1)) |> format(cohort_date, Slot %m-% years(1)) |>  "Scorecard 3 bad Rate %s

bar_chart_obj_backtesting <- ms_barchart()
  data <- ks_badrate_trends_backtesting
  dplyr::filter(Attribute <- str_detect(population, "Orig")) |>
  dplyr::mutate(scaled_bad_rate <- bad_rate * scaling_factor_backtesting,
                Scorecard = case_when(Scorecard == "All Segments" ~ "Full Model",
                                      T ~ Scorecard))

# group = "population" # to have different colored lines by population
  chart_settings(title_v = "Investment") |> Bold_a_bold_series

# Prepare data for the line chart
line_chart_data_backtesting <- ks_badrate_trends_backtesting |>
  dplyr::filter(Attribute = dplyr::filter(Attribute(data_dplyr::str_detect(data <- "All segments" ~ "Full Model",
                                                                            T ~ Scorecard))) |> 1)
  dplyr::mutate(scaled_bad_rate <- bad_rate * scaling_factor_backtesting,
                Scorecard = dplyr::case_when( ) |> Scorecard # Apply the scaling factor

chart_settings(title_v = "Investment") = Bold_a_bold_series
  mschart::chart_theme(legend_position = "b")

ks_bad_rate_table_backtesting <- build_ks_bad_rate_flex(table(ks_badrate_trends_backtesting))
```

```{r}
# The official quarterly report file compiles all data pulled from above and writes a word document. The document can be
# found in "/Outputs/Quarter/Quarterly_PSI_CSI/ KS Reports/Model Monitoring Report {model} {type} - FS custom type
# {format_quarterly report_date %m-% month(1)}/All/format(cohort_date_Slot %m-% month(1).doc"

### Flow Tables for docx

# The code here formats data frames into wr friendly tables to be used in word doc.

```{r}
# Step 1: Create flextable from psi/csi data

psi_csi_summary_table <- psi_csi_summary |>
  flextable::flextable() |>
  dplyr::mutate(definition = c,

  # Limits: Removed Experience and Atflow Data
  # Limits: Enhanced Experience and cli Rate
  # Limited Enhanced Experience and early (Series Delinquency)
  # Removed Experience and Clor
  # Removed: Experience and Apply (various Delinquency)

  dplyr::select(Segmentation, Distribution, Population_Stability = "misc.")

# Step 2: Identify alternating rows
even_rows <- which(seq_len(nrow(psi_csi_summary)) %% 2 == 0) +
add_rows <- which(seq_len(nrow(psi_csi_summary)) %% 2 == 1)

# Step 3: Identify conditional formatting
# PSI conditional formatting | PSI > 0.10 &
flextable::bg(i = even_rows, bg = "##BEDED") |>
  flextable::bold(j = 1, part = "header") |>
  flextable::bg(i = 1, bg = "#FFFFFF") |>
  flextable::set_flextable_defaults(j = 1, part = "body") |>
  flextable::color(j = 1, i = "Population Stability Index", bg = "##BEDED") |>
  flextable::bg(j = red_rows, i = "Population Stability Index", bg = "red")

  # Step 4: Apply formatting
  flextable::set_table_properties(layout = "autofit") |>
    flextable::fontsize(size = 8, part = "all") |>
    flextable::font(fontname = "Arial", part = "all") |>
    flextable::bg(i = 1, bg = "##BEDED") |>
    flextable::bold(j = 1, part = "header") |>
    flextable::bg(j = 1, bg = "#FF0000") |>
    flextable::bg(j = red_rows, i = "Weighted Stability Index", bg = "red") |>
    flextable::bg(j = 1, bg = "#FF0000") |>
    flextable::color(font.double |> c("Dec. Count", "Val. Full"), big_only = T, digits = 0) |>
    flextable::color(font.double |> c("Proportion in (B/A)", "Log of in Proportion in (ln(B/A))", "Population %s

  digits = 3) |>

  flextable::collect(i = arranged_scorecard_data, color = "olivedrab", part = "body") |>
  flextable::bold(i = arranged_scorecard_data) |>
  flextable::bg(i = red_rows, j = 5, = "Proportion is Divergence in (0.45 * ln(A))") |>

  return(psi_scorecard_table)
)

psi_scorecard_table
```

```{r}
# ...

column_names <- names(csi_threshold_breaches)

csi_breached_table <- flextable::flextable(csi_threshold_breaches) |>
  dplyr::mutate(
    Score_Range = dplyr::case_when(lower_range == "Total" ~ glue::glue("{Lower_Range},{Upper_Range}"),
                                   T ~ "")) |>

dplyr::select(
  color_range(Range),
  dplyr_green(Range),
  dplyr_green()) |>

csi_breached_table <-
  flextable::flextable(csi_breached_table) |>
    flextable::set_table_properties(layout = "autofit") |>
    flextable::fontsize(size = "small_part") |> "header" |> 1) |>
    flextable::bg(i = 1, bg = "#BEDED") |>
    flextable::bold(j = 1, part = "header" ) |>
    flextable::bg(i = "##BEDED") |>
    flextable::add_header(data = threshold_breaches(1) <= 0.1, bg = "green") |>

csi_breached_table

# Code to create rank ordering variable for docs tool

# ...
scorecard <- c(  "Scorecard 0", "Scorecard 1", "Scorecard 2", "Scorecard 3", "Scorecard 4", "full Model")

rank_order_breaches <- purrr::map(rank_order_data, counts_rank_order_breaches,
                                   scorecard_order_breaches1 |> i |> dplyr::collect(report_bins) |> glue::glue(category(types)

rank_order_breaches(1) |> i |> dplyr::filter(final_bound = 0 |> i |> dplyr::collect(report_bins))
```

### docx regex

# This section creates a new file by using a template, parses its placeholder locations and replaces stubs, tables, and selected
# text relevant to the newly calculated values.

```{r}
# install.packages("openxlsx")
# install.packages("readtext")
# install.packages("officer")

# Load packages
library(officer)
library(flextable)
library(dplyr)

if(format(psi_summary |> dplyr::filter("Population Stability Index" > 0.8 |> "Population Stability Index" > 0.05) |> 0) |>
  PSIchoicesummary <- glue::glue("PSI(Segments)") |> 1 |> psi_summary |> 0 |>
  dplyr::multi(format(coll(x) = glue::glue_collapse(x = ", ")) are all above 0 05, indicating change for later place.")
)

if(format(psi_summary |> dplyr::filter("Population Stability Index" > 0.05) |> 0) |>
  PSIchoicesummary <- glue::glue("PSI(Segments)") |> 1 |> psi_summary |> 0 |>
  dplyr::multi(format(coll(x) = glue::glue_collapse(x = ", ")) are all above 0.25 indicating some significant shifts in
population composition"))

if(format(psi_summary |> dplyr::filter("Population Stability Index" < 0.05) |> 0) |>
  PSIchoicesummary <- glue::glue("PSI is OK changes from baseline")
)

# Summary
  KSSummary <- build_ks_summary_text(ks_badrate_trends, csi_label = "Population KSRS")

# -- is backtesting
  KSSummaryBacktesting <- build_ks_summary_text(ks_badrate_trends_backtesting, csi_label = "Backtesting cohort (type")

# -- rank order
  RankOrderSummary <- build_rank_order_summary_text(
    rank_order_breaches,
    no_breach_message = "No breaches in rank order were observed in any segments."
  )

# -- rank order backtesting
  RankOrderSummaryBacktesting <- build_rank_order_summary_text(
    rank_order_breaches_backtesting,
    no_breach_message = "No breaches in rank order were observed in any segments for this backtesting cohort."
  )

  # Rendering |> ==
  # A rendering creates a formatted at a keyword placeholder with cross config inputs so
  # that the automated report is done correctly.

  add_dt_case = "Scorecards, December 31, label, keyword |>  "
  , "the ks, value > "

  message(sprintf("Generating Quarterly PSI_CSI KS Reports/Model Monitoring Report %s", glue::glue("..."))

  label_keyword <-
    officer::read_docx(path_to, "body")
    length(officer::docx_body(1))

# Read in your "shell" document as a template.
  doc <- officer::read_docx("Input Files/Model Monitoring Report s Backtesting  fevalue.docx")

# 1 -- text replacements line formatted() resolved, cats is glue
# 2 Below, by detail: that function (greens correct result) and sets a glue()
# 3 Add: cursor (move and set the position in the body paragraph)
#   - by  body_bookmark then read_bookmark makes the right place to add
# 4 Also: match_and_extract__Get table's that marks_pos(t) it's a prefix
# 5 It's -- "PSIchoicesummary"  : placing't/ destroying the trigger message in a specific
#   - deletes a doc md table link/ trying to the centre's paragraph switch loc.

  officer::body_replace_all_text(
    old_value <- "PSIChoiceSummary",
    new_value <- PSIchoicesummary,
    only_at_cursor <- FALSE)

  officer::cursor::reach_keyword("KSSummary") |>
  officer::body_replace_all_text(
    old_value <- "KSSummary",
    new_value <- KSSummary,
    only_at_cursor <- FALSE)

  officer::cursor::reach_keyword("KSSummary") |>
  officer::body_replace_all_text(
    old_value <- "KSSummary",
    new_value <- KSSummary,
    only_at_cursor <- 1000)

  officer::cursor::reach_keyword("KSSummaryBacktesting") |>
  officer::body_replace_all_text(
    old_value <- "KSSummaryBacktesting",
    new_value <- KSSummaryBacktesting,
    only_at_cursor <- 1000)

  officer::cursor::reach_keyword("RankOrderSummary") |>
  officer::body_replace_all_text(
    old_value <- "RankOrderSummary",
    new_value <- RankOrderSummary,
    only_at_cursor <- 1000)

  officer::cursor::reach_keyword("RankOrderSummaryBacktesting") |>
  officer::body_replace_all_text(
    old_value <- "RankOrderSummaryBacktesting",
    new_value <- RankOrderSummaryBacktesting,
    only_at_cursor <- 1000)

  officer::cursor::reach_keyword("InputQuarter") |>
  officer::body_replace_all_text(
    old_value <- "InputQuarter",
    new_value = glue::glue("{lubridate::quarter(last_quarter_end_date %m-% 5 |> years(1))}{format(last_quarter_end_date %m-% 5 |>
      years(1), '%Y')}"),
    only_at_cursor <- TRUE)

  officer::cursor::reach_keyword("ReportQuarter") |>
  officer::body_replace_all_text(
    old_value <- "ReportQuarter",
    new_value = glue::glue("{lubridate::quarter(last_quarter_end_date %m-% 5 |> years(1))}{format(last_quarter_end_date %m-% 5 |>
      years(1), '%Y')}"),
    only_at_cursor <- TRUE)

  officer::cursor::reach_keyword("TextCSIUpdate") |>
  officer::body_replace_all_text(
    old_value <- "TextCSIUpdate",
    new_value = glue::glue("{lubridate::quarter(last_quarter_start_date, floor_date(cohort_date, 1m %m-% 5 |> years(1)) quarter)  %m-%(1)
      years(1) |> '%Y')}"),
    only_at_cursor = TRUE)
```

```{r}
# == add tables ==

  doc <- add_df_table(doc, "PSISummaryTable", psi_summary_table, "psi_summary_table()")
  doc <- add_df_table(doc, "PSIScllTable", psi_scorecard_table(i), "psi_scorecard_table(i)")
  doc <- add_df_table(doc, "PSIScorecardTable", psi_scorecard_table, "psi_scorecard_table")
  doc <- add_df_table(doc, "PSIFullTable", psi_scorecard_table(1), "psi_scorecard_table(1)")
  doc <- add_df_table(doc, "CSITable", csi_breached_table, "csi_breached_table")

  # == CSI table
  doc <- add_df_table(doc, "CSIBreachedTable", csi_breached_table, "csi_breached_table")

  # == KS charts ==
  message("[docx] Inserting all charts at 'KSPlot'")

  officer::cursor_reach("KSPlot") |>

  mschart::body_add_chart(chart = bar_chart_obj, width = 6, height = 4 * 0.8) |>
  officer::body_add_break() |>

  message(sprintf("[docx] Inserting table 'ks bad rate table' (rows=%d, cols=%d)",
                  flextable::nrow_part(ks_bad_rate_table, "body"),
                  length(ks_bad_rate_table$col_keys))

  doc <- i <- flextable::body_add_flextable(ks_bad_rate_table)

  message("[docx] Inserting rank order charts")

  officer::body_remove() |>
  officer::cursor_reach("RankOrder0OverallFirst") |>

  officer::body_remove()
  mschart::body_add_chart(chart = my_ms_chart(1)), width = 6, height = 6 * 0.8) |>
  officer::cursor_reach("RankOrder0overall") |>
  officer::body_remove()
  mschart::body_add_chart(chart = my_ms_chart(2)), width = 6, height = 6 * 0.8) |>
  officer::cursor_reach("RankOrder0sc1") |>
  officer::body_remove()
  mschart::body_add_chart(chart = my_ms_chart(3)), width = 6, height = 6 * 0.8) |>
  officer::cursor_reach("RankOrder0sc2") |>
  officer::body_remove()
  mschart::body_add_chart(chart = my_ms_chart(4)), width = 6, height = 6 * 0.8) |>

  # == Backtesting KS charts
  message("[docx] Inserting backtesting KS charts at 'KSPlotBacktesting'")

  officer::cursor_reach("KSPlotBacktesting") |>
  mschart::body_add_chart(chart = bar_chart_obj_backtesting, width = 6, height = 6 * 0.8) |>
  officer::body_add_break() |>

  message(sprintf("[docx] Inserting table 'ks bad rate table backtesting' (rows=%d, cols=%d)",
                  flextable::nrow_part(ks_bad_rate_table_backtesting),
                  length(ks_bad_rate_table_backtesting$col_keys))

  doc <- i <- flextable::body_add_flextable(ks_bad_rate_table_backtesting)

  # -- Backtesting rank order charts
  message("[docx] Inserting backtesting rank order charts")

  officer::cursor_reach("RankOrderDefCohortOverall") |>
  officer::body_remove()
  mschart::body_add_chart(chart = my_ms_chart_backtesting(1)), width = 6, height = 6 * 0.8) |>
  officer::cursor_reach("RankOrderDefCohortSc1") |>
  officer::body_remove()
  mschart::body_add_chart(chart = my_ms_chart_backtesting(2)), width = 6, height = 6 * 0.8) |>
  officer::cursor_reach("RankOrderDefCohortSc2") |>
  officer::body_remove()
  mschart::body_add_chart(chart = my_ms_chart_backtesting(3)), width = 6, height = 6 * 0.8) |>
  officer::cursor_reach("RankOrderDefCohortSc3") |>
  officer::body_remove()
  mschart::body_add_chart(chart = my_ms_chart_backtesting(4)), width = 6, height = 6 * 0.8) |>
  officer::cursor_reach("RankOrderDefCohortSc4") |>
  officer::body_remove()
  mschart::body_add_chart(chart = my_ms_chart_backtesting(5)), width = 6, height = 6 * 0.8) |>

  message("[docx] All content inserted successfully")

  print(doc, target = glue::glue("Outputs/Quarter/Quarterly_PSI_CSI/ KS Reports/Model Monitoring Report {model} {type} - FS custom type
    {format_quarterly_report_date %m-% month(1)}/All/{format(cohort_date, '%Y%m')}.docx"))
```
