---
title: "CC Custom Scorecard Quarterly Report"
author: "Bryan Thomas"
date: "2026-04-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Desktop/Professional/Projects/CC_Model_Monitoring")
here::i_am("orchestration_2.Rmd")
```

## Overview

Member demographic data and application data is sent to Equifax on a monthly basis and uploaded into 9 tables within Ignite. The workflow below should be ran on a monthly basis to generate the 9 files needed to be sent to Equifax.

## Running the Workflow

### 1) Renv Initialization

If this is the first time pulling the project, you will need to initialize the renv.lock file. This will set the environment dependencies in sync with what was used during project development. Run the init function below.

You should see this prompt:

``` r
renv::init()
this project already has a lockfile. What would you like to do?

1: Restore the project from the lockfile.
2: Discard the lockfile and re-initialize the project.
3: Activate the project without snapshotting or installing any packages.
4: Abort project initialization.
```

Select option 1 and the environment will be set up appropriately.

```{r}
# renv::init()
```

### 1) Creating the Keyring File

The set_keyring function is an internal designed function which will set up a keyring file in the posit environment for the user. This keyring file will handle user credentials when connecting with databases (e.g. 'EDWPROD', 'PRODODBC', 'Impala64', 'TSYS_DV_DB2', 'ASL', 'cpspace', 'MySQL_CPSpace', 'edu_lending'). The function has three inputs - db, test_passwords, and reset_outdated. Leaving the function empty will run the default settings. This will check for the existence of a keyring file with the 8 db connection details. It will then test the connections to each db to ensure the keyring file is up to date. If any passwords are outdated, the user will be prompted for a new password to save to the keyring file. Updates made here only updated the credentials saved in the keyring file.

```{r}
# Source the keyring setup function (uncomment if needed)
# source(file = here::here('R/set_keyring.R'))
#
# Run to create/update keyring file (uncomment if needed)
# set_keyring(#db = c("EDWPROD", "PRODODBC", "ASL"),
#             test_passwords = T,
#             reset_outdated = T)
```

### 2) Setting the Project Paths

All pointers in this project use soft paths via the {here} package. To ensure that the pointers are correct. Be sure that the `MPM_CCCustomScore` project is opened before proceeding. This ensures the working directory is set appropriately.

Code and reference files are sourced within the `MPM_CCCustomScore` repo. Data is written in this directory as well as a mirrored location at opt/rspro/home/b9800/projects/shared_data/MPM_CCCustomScore/. This location will house data for collaboration without allowing contributors to edit original data sets.

### 3) Loading Functions & Globals

Source all required R scripts and load necessary libraries. Set global variables for cohort dates and file paths.

```{r}
library(lubridate)
library(ggplot2)
library(data.table)

set.seed(42)
options(scipen = 999)
cohort_date <- as.Date(glue('{lubridate::floor_date(Sys.Date(),"quarter")}')) # Is lubridate::floor_date('quarter')
backfilling_date <- cohort_date %m-% months(6)

# Gates which R methodologies can/cannot, wired into logic starting [checkpoint 5
ks_methods <- c('live', 'fixed', 'true')
stopifnot(all(unlist(ks_methods %in% c('live', 'fixed', 'true'))))

source('R/pull_apps.R')
source('R/function_cc_scorecard_data.R')
source('R/pull_trended_data.R')
source('R/pull_early_trended_data.R')
source('R/function_join_apps_perf.R')
source('R/pull_score_mapping.R')
source(here::here('R/calculate_early_ks.R'))
source(here::here('R/calculate_true_bad_ks.R'))
source(here::here('R/build_ks_report_tables.R'))
source(here::here('R/build_ks_rank_order.R'))

fs::dir_create('data/performance_24')
apps_path <- fs::dir_ls('data/apps')
perf_paths <- fs::dir_ls('data/performance_24/')
```

## 4) Folder Init

This section checks for required directories and creates them if missing. Run once per new project setup.

**MRM** - after folder creation, copy all data from the mirrored shared directory into the cloned repo to preserve file pointers and code like: cp -r /mnt/c/sp/custom/path/AAAA/projects/shared_data/MRM_illustrations_/MRM_[UNCLEAR]/monitor/ to move files into the needed locations

```{r, echo=FALSE}
#------------------------------- Folder Structure ---------------------------------
fs::dir_create(c('data', 'data/dq_24_mos', 'data/ks_driver_w_perf', 'data/performance_24'))
fs::dir_create(c('output_files', 'output_files/quarterly_stats'))
```
# Quarterly Report

This section processes scorecard and application data, calculates PSI, CSI, KS, bad rate, and approval rate metrics, and prepares summary tables.

PSI and CSI evaluate the most recent window of through the door (TTD) applications. This window is considered the model input.

## PSI

The chunk below pulls the most recent Starters application and scorecard data from PATH if it is not already held within the local repository and writes the data as a .txt.gz file. This allows us to avoid repetitious pulls when looking over windows or different report iterations.

```{r}

paths <- fs::dir_ls('data/scorecard')[!which(basename(fs::dir_ls('data/scorecard')) %in% c(
  glue::glue('scorecard_{format(as.Date(cohort_date), "%Y%m")}.txt.gz'),
  glue::glue('scorecard_{format(as.Date(cohort_date) %m+% months(1), "%Y%m")}.txt.gz'),
  glue::glue('scorecard_{format(as.Date(cohort_date) %m+% months(2), "%Y%m")}.txt.gz')))]

if(length(paths) != 3){
  scorecard <- purrr::map_dfr(seq(cohort_date, cohort_date %m-% months(2), 'month'),
                              .progress = TRUE,
                              function(model_input_window){

                              df <- get_cc_scorecard_data(performance_window = model_input_window,
                                                          write = T)
                              return(df)
                              })
}


paths <- fs::dir_ls('data/apps/')[which(basename(fs::dir_ls('data/apps/')) %in% c(
  glue::glue('(apps_{format(as.Date(cohort_date), "%Y%m")}.txt.gz'),
  glue::glue('(apps_{format(as.Date(cohort_date) %m+% months(1), "%Y%m")}.txt.gz'),
  glue::glue('(apps_{format(as.Date(cohort_date) %m+% months(2), "%Y%m")}.txt.gz')
))]

if(length(paths) != 3){
  scorecard <- purrr::map_dfr(seq(cohort_date, cohort_date %m-% months(2), 'month'),
                              .progress = TRUE,
                              function(model_input_window){

                              df <- get_apps_data(performance_window = model_input_window,
                                                          write = T)
                              return(df)
                              })
}

gc()
```

This section pulls in the most recent quarter of application and scorecard data and uses predefined custom score ranges to set PSI bins in accordance with the model development population.

```{r}
number_of_month_window <- 3

scorecard <- purrr::map_df(c(1:number_of_month_window),
                function(i) {
                  
                  df <- data.table::fread(glue::glue('data/scorecard/scorecard_{format(cohort_date %m+ months(i - 1), "%Y%m")}.txt.gz'))
                  
                  })

apps <- purrr::map_df(seq(number_of_month_window),
                function(i) {
                  
                  df <- data.table::fread(glue::glue('data/apps/apps_{format(cohort_date %m+ months(i - 1), "%Y%m")}.txt.gz'))
                  
                  })

names(apps) <- names(apps) |> tolower()
names(scorecard) <- names(scorecard) |> tolower()
```

```{r}
apps |>
  filter(!client_product_cd %in% c('SEC','MSC')) |>
  mutate(
    user_ref_num = as.numeric(user_ref_num),
    copied_flag = case_when(is.na(copied_from) ~ 1,
                             T ~ 0)
    ) |>
  left_join(scorecard |> mutate(user_ref_num = as.numeric(user_ref_num))) |>
  group_by(has_score = case_when(is.na(prim_score) ~ 0,
                                 prim_score < 100 ~ -1,
                                 prim_score > 450 ~ 9999,
                              T ~ 1),
           has_segment = case_when(is.na(segment) ~ 0,
                                   T ~ 1),
           data = zoo::as.yearqtr(dt_entered)) |>
      summarize(dt_counts_pre = n_distinct(app_num)) |>
left_join(
  apps |>
  filter(!client_product_cd %in% c('SEC','MSC')) |>
  mutate(
    user_ref_num = as.numeric(user_ref_num),
    from_value = as.numeric(substr(stringr::str_extract(copied_from, "(?<=FROM ) \\d+"),1,14)),
    to_value = as.numeric(substr(stringr::str_extract(copied_from,"(?<=TO ) \\d+"),1,14)),
    copied_flag = case_when(is.na(copied_from) ~ 1,
                             T ~ 0),
    user_ref_num = case_when(is.na(from_value) ~ user_ref_num,
                             T ~ from_value)) |>
    left_join(scorecard |> mutate(user_ref_num = as.numeric(user_ref_num))) |>
  group_by(has_score = case_when(is.na(prim_score) ~ 0,
                                 prim_score < 100 < -1,
                                 prim_score > 450 ~ 9999,
                              T ~ 1),
           has_segment = case_when(is.na(segment) ~ 0,
                                   T ~ 1),
           data = zoo::as.yearqtr(dt_entered)) |> 
    summarise(app_counts_post = n_distinct(app_num))
  )

```

```{r}
 psi_df <- apps |> 
  mutate(app_num = as.numeric(app_num),
         user_ref_num = as.numeric(user_ref_num),
         from_value = as.numeric(substr(stringr::str_extract(copied_from, "(?<=FROM ) \\d+"),1,14)),
    to_value = as.numeric(substr(stringr::str_extract(copied_from,"(?<=TO ) \\d+"),1,14)),
    copied_flag = case_when(is.na(copied_from) ~ 1,
                             T ~ 0),
    user_ref_num = case_when(is.na(from_value) ~ user_ref_num,
                             T ~ from_value)) |>
    left_join(scorecard |>
                mutate(user_ref_num = as.numeric(user_ref_num))) |>
  mutate(has_score = case_when(is.na(prim_score) ~ 0,
                                 prim_score < 100 < -1,
                                 prim_score > 450 ~ 9999,
                              T ~ 1),
           has_segment = case_when(is.na(segment) ~ 0,
                                   T ~ 1)) |>
  filter(!client_product_cd %in% c('SEC', 'MSC'),
         !is.na(prim_score),
         has_segment == 1,
         prim_score >= 100)

  # Define vigintile breaks per segment (20 buckets each)
  # Breaks represent score thresholds; labels are auto-generated as "lower to upper"
  segment_breaks <- list(
    "All Segments" = c(100, 117, 134, 151, 168, 185, 202, 219, 236, 253,
                       270, 287, 304, 321, 338, 355, 372, 389, 406, 423, 450),
    "0" = c(100, 112, 124, 136, 148, 160, 172, 184, 196, 208,
            220, 232, 244, 256, 268, 280, 292, 304, 316, 328, 450),
    "1" = c(100, 118, 136, 154, 172, 190, 208, 226, 244, 262,
            280, 298, 316, 334, 352, 362, 372, 382, 392, 410, 450),
    "2" = c(100, 120, 140, 160, 180, 200, 220, 240, 260, 280,
            300, 315, 330, 345, 360, 375, 390, 405, 420, 435, 450),
    "3" = c(100, 125, 150, 170, 190, 210, 230, 250, 270, 290,
            310, 325, 340, 355, 370, 385, 395, 405, 420, 435, 450),
    "4" = c(100, 130, 155, 180, 200, 220, 240, 260, 280, 300,
            320, 335, 350, 365, 380, 390, 400, 410, 425, 440, 450)
  )

  # Helper: cut scores into labeled bins using segment-specific breaks
  bucket_scores <- function(scores, breaks) {
    labels <- paste(head(breaks, -1), tail(breaks, -1), sep = " to ")
    cut(scores, breaks = breaks, labels = labels, include.lowest = TRUE, right = TRUE)
  }

  # "All Segments" row
  psi_all <- psi_df |>
    dplyr::mutate(all_bucket_aligned = bucket_scores(prim_score, segment_breaks[["All Segments"]])) |>
    dplyr::group_by(all_bucket_aligned) |>
    dplyr::summarise(counts = dplyr::n_distinct(user_ref_num)) |>
    dplyr::mutate(segment = 'All Segments')

  # Per-segment rows
  psi_by_seg <- psi_df |>
    dplyr::mutate(segment = as.character(as.numeric(segment))) |>
    dplyr::group_by(segment) |>
    dplyr::group_modify(~ {
      brks <- segment_breaks[[.y$segment]]
      .x |>
        dplyr::mutate(all_bucket_aligned = bucket_scores(prim_score, brks)) |>
        dplyr::group_by(all_bucket_aligned) |>
        dplyr::summarise(counts = dplyr::n_distinct(user_ref_num), .groups = 'drop')
    }) |>
    dplyr::ungroup()

  psi <- dplyr::bind_rows(psi_all, psi_by_seg) |>
    dplyr::select(segment, counts, all_bucket_aligned) |>
    dplyr::arrange(segment, desc(all_bucket_aligned))
        
  
psi_raw_data <- psi |>
  tidyr::separate(all_bucket_aligned, c('Lower_Range', 'Upper_Range'), sep = ' to ') |>
  dplyr::mutate(Lower_Range = as.numeric(Lower_Range),
                Upper_Range = as.numeric(Upper_Range)) |>
  dplyr::rename(Scorecard = segment)

psi_raw_data
```

# QC: Validated

We use the following chunk to load-in a whole-file to provide a template

```{r}                                                                                                    

albefile <- 'Output/Quarterly_Q2_1/loan_and_cd_event_DEFAULT.xlsx'

glue_names = c(glue::glue("sheet-open-mu-getSheetName([slot[1]][1])"),
               glue::glue("sheet-open-mu-getSheetName([slot[1]][2])"),
               glue::glue("sheet-open-mu-getSheetName([slot[2]][1])"),
               glue::glue("sheet-open-mu-getSheetName([slot[2]][2])"),
               glue::glue("sheet-open-mu-getSheetName([slot[3]][1])"),
               glue::glue("sheet-open-mu.getSheetName([slot[3]][2])"))

this_a_df_list = list(openxlsx::read.xlsx(albefile, sheet=openxlsx::getSheetName([slot[1]][1])),
                      openxlsx::read.xlsx(albefile, sheet=openxlsx::getSheetName([slot[1]][2])),
                      openxlsx::read.xlsx(albefile, sheet=openxlsx::getSheetName([slot[2]][1])),
                      openxlsx::read.xlsx(albefile, sheet=openxlsx::getSheetName([slot[2]][2])),
                      openxlsx::read.xlsx(albefile, sheet=openxlsx::getSheetName([slot[3]][1])),
                      openxlsx::read.xlsx(albefile, sheet=openxlsx::getSheetName([slot[3]][2])))

names(this_a_df_list) <- glue_names

albefile_q_dft <- input_file(slot_1.deft.xlsx

# names = c(glue::glue("sheet-[sheet-open-mu].getSheetName([slot[1]][1])"),
# 0         glue::glue("sheet-[sheet-open-mu].getSheetName([slot[1]][2])"),
# 0         glue::glue("sheet-[sheet-open-mu].getSheetName([slot[2]][1])"),
# 0         glue::glue("sheet-[sheet-open-mu].getSheetName([slot[2]][2])"))

# albefile_q_role_list = list(openxlsx::read.xlsx(albefile_q_dft, sheet=openxlsx::getSheetName([slot[1]][1])),
# 0                           openxlsx::read.xlsx(albefile_q_dft, sheet=openxlsx::getSheetName([slot[1]][2])),
# 0                           openxlsx::read.xlsx(albefile_q_dft, sheet=openxlsx::getSheetName([slot[2]][1])),
# 0                           openxlsx::read.xlsx(albefile_q_dft, sheet=openxlsx::getSheetName([slot[2]][2])))

```
#---------------------------------------------------------------------------
# spreads: read.xlsx(albefile, sheet=openxlsx::getSheetName([slot][1])),
# openxlsx::read.xlsx(albefile, sheet=openxlsx::getSheetName([slot][2])))

# names(this_q_refit_list_1) = names,

albelile <- input_file(slot_core.refit_Development_est_bin.xlsx)

names = c(
  glue::glue("sheet-[sheet-openxlsx::getSheetName([slot[1]][1])]"),
  glue::glue("sheet-[sheet-openxlsx::getSheetName([slot[1]][2])]"),
  glue::glue("sheet-[sheet-openxlsx::getSheetName([slot[2]][1])]"),
  glue::glue("sheet-[sheet-openxlsx::getSheetName([slot[2]][2])]"),
  glue::glue("sheet-[sheet-openxlsx::getSheetName([slot[3]][1])]"))

this_q_refit_list = list(
   openxlsx::read.xlsx(albefile, sheet=openxlsx::getSheetName(albefile.old[1])),
   openxlsx::read.xlsx(albefile, sheet=openxlsx::getSheetName(albefile[1])),
   openxlsx::read.xlsx(albefile, sheet=openxlsx::getSheetName(albefile[2])),
   openxlsx::read.xlsx(albefile, sheet=openxlsx::getSheetName(albefile[3])),
   openxlsx::read.xlsx(albefile, sheet=openxlsx::getSheetName(albefile[4])),
   openxlsx::read.xlsx(albefile, sheet=openxlsx::getSheetName(albefile[5])))

names(this_q_refit_list) <- names

# ranges
# p <- [UNCLEAR]
#          function(X, Y){
  # browser()
  # i = 0
  # for s, t of [UNCLEAR] ->  all [UNCLEAR]
  # p = "THIS - All [UNCLEAR]"

# names = c("Lower Range", "Upper Range","[UNCLEAR]", "Percent_A", "Scorecard

data_1 = cell1 openxlsx.fromexcel([UNCLEAR]Asterix[UNCLEAR]) [UNCLEAR]
# [UNCLEAR] inputsheetid = X2 spread = [("lower_range", input_Range, [UNCLEAR] [UNCLEAR]
# [UNCLEAR]-width)[scorecard.id)] [UNCLEAR]
#     width_scorecard = grub["d/s"]["item"]["lower_range", [UNCLEAR] input_name[UNCLEAR])]
#         grub["d/s"]["[UNCLEAR]"]["lower_range"] / [UNCLEAR] = [UNCLEAR] names[UNCLEAR]);
        cell_counts = X2,
        cell_[UNCLEAR] = X1,
selectfill_col_value(A, B)
}  [UNCLEAR] [UNCLEAR] call

# names(data_1) = names

# data_2 = data_1[
#     (scorecard, lower_range, Upper_Range, oblivious, Percent_A)

# return(data_2)

for (i in 1:1){
  dlplt.group_by(scorecard)
  # lower_range = dlplt[upper_whentimer.Type == scorelower_range, is.na = 0] > lower_range_i,
  #   0           lower_range = dlplt[upper_whentimer.Type = lower_range,
  #                lower_range = dlplt.dlplt [lower_range, is.na(i) = 0] #
  #   0           lower_range = dlplt.dlplt [lower_range, is.na(i) + 1] %
  #                              lower_range,  dlplt.isAtleast(range + 1 = lower_range + 1),
  #                              / lower_range),
  # scorecard  "All Segments"

ranges_refit
outer.paste.strsplit(this_q_refit_list,
             names(this_q_refit_list))
  function(d,i){
  # browser()
  # i = 0
  # x = (this_p_qq_list[i][[1]] - Scorecard #
  # x = (this_q_qq_list[i] & POS.list[i] - Scorecard

  # names = c("Lower Range", "Upper_Range", "[UNCLEAR]_counts", "Percent_A", "Scorecard

  # browser()
  data_1 <- x [dlplt.input[UNCLEAR]]{
       filterScore.range_info <- table_info = c("lower_range", "inner_Range",[UNCLEAR] = 0) |>
           color = color(scorecard) = clrboard,
Scorecard = Scorecard }})
.strip = str_remove("Scorecard") ))
.string = str_remove(# dplyr),
Lower_Range = as.numeric [["", "" Lower Range]] is as.numeric(),
Lower_Range = case_when(Lower_Range > min(Lower_Range) - 10L, ~ Lower_Range),
Percent = as.numeric[[]][[]]] is as.numeric(),
Upper_Range = case_when(Upper_Range == max(Upper_Range) - 410, T ~ .Upper_Range),
totals = totals / sum(totals),
Percent = totals / sum(totals)) is as.numeric() ))
select(
Lower_Range,Upper_Range, totals, Percent, Scorecard
)

names(data_1) = .names

data_1 <- data_1 |>
dplyr::select(Scorecard, Lower_Range, Upper_Range, old_counts, Percent_A)

return(data_1)
}

ranges_refit
# ranges_1
ranges_refit3
# ranges
dplyr::group_by(Scorecard) |>
dplyr::mutate(Lower_Range = dplyr::case_when(Lower_Range >= min(Lower_Range, na.rm = T) - Lower_Range + 1,
Lower_Range = dplyr::case_when(Lower_Range > min(Lower_Range, na.rm = T) ~ 100,
~ Lower_Range),
Upper_Range = dplyr::case_when(Upper_Range > min(Upper_Range, na.rm = T)) &
# (Lower_Range = dplyr::lead(Lower_Range, n = 1) / (Lower_Range - 1)),
Scorecard = dplyr::case_when(Scorecard == (Overall) ~ "All Segments",
~ Scorecard)
)

ranges <- ranges_refit
ranges_refit_plt <- ranges_refit#

pol_data <- ranges |>
dplyr::group_by(Scorecard) |>
dplyr::mutate(Lower_Range = dplyr::case_when(abs(Lower_Range) >= 185 ~ 184,
~ Lower_Range),
Lower_Range = dplyr::case_when(Lower_Range == 1386 &
~ Lower_Range - dplyr::lead(pol_Range) * 3) * (Lower_Range -
4)),
Upper_Range = dplyr::case_when(Upper_Range >= max(Upper_Range, na.rm = T) ~ 816, )

.Upper_Range:
Lower_Range = dplyr::case_when(Lower_Range == min(Lower_Range, na.rm = T) ~ 399, )
.Lower_Range,
dplyr::full_join(pol.trim.data
dplyr::mutate(Lower_Range = case_when(abs(Scorecard) > 1 ~ "All Segments",
.glue::glue("{Scorecard}")) |>
Lower_Range = dplyr::case_when(abs(Lower_Range) >= 385 ~ 385,
~ Lower_Range),
Lower_Range = dplyr::case_when(Upper_Range) > ~ 100 #
~ (Lower_Range) - dplyr::lead(pol_Range) * 1) * (Lower_Range -
2) = Lower_Range)) ))

# table_refit(d) |>
dplyr::mutate(totals = sum(d_counts, na.rm = T),
totals = sum(totals, na.rm = T),
Percent_B = counts / totals,
Percent_A = Percent_B - Percent_A,
Proportion (B/A) = Percent_B / Percent_A,
Log of Proportion (B/A) = log(Proportion (B/A) ),
Population Divergence (D-A) = (p(B/A) - (Bit. Difference (B-A) - log_of Proportion
jack(A)) ) ))
dplyr::select(-totals, -sd.totals) |>
dplyr::group_split() |>
purrr::map(function(a){
# |>
dplyr::mutate(Upper_Range = as.character(Upper_Range),
Lower_Range = as.character(Lower_Range) ) |>
dplyr::bind_rows(tibble::tibble(Scorecard = (Scorecard[[1]]),
Lower_Range = "Totals",
Upper_Range = "Totals",
old_counts = sum(old_counts),
Percent_B = sum(Percent_B, na.rm=T),
Percent_A = sum(old_Percent_A),
counts = sum(counts)),
Bit. Difference (B-A) = NA,
}}

psi_summary <- psi_data |>
population_map_dt(function(x){
x |> dplyr::summarise(Scorecard = dplyr::first(Scorecard),
Population_Stability_Index = max( Population_Divergence_(D-A) * (x[b/A] ))
})
})

psi_summary
?
```

```{r}
#PSI-CSR Team

# Features used to feed the system view model are pulled each quarter here. We load in the development
# population features used and the value stability index measurements so we can compare the distributions against
# current calculations.

--- {-}
# model input window(B)
# model input window(A)

keyring::keyring_unlock(password = 'keyring')

keys <- keyring::key_list()

host <- 'adv-2496822760[UNCLEAR].ll.azuredatabricks.net'
subscription_name <- 'SPACE-IT-PROD-BI'
crdbplly_compute <- 'ascii-clust[UNCLEAR]/[UNCLEAR]2501[UNCLEAR]8[UNCLEAR]QI[UNCLEAR]-[UNCLEAR]1880-abKQgphre'
sql_cmd <- DBI[UNCLEAR] <- DBI::dbConnect(drv,
host = dplyr::filter(service == 'BI') |> dplyr::call().username),
password = keyring::key_get('BI'),
subscription_name = crdbplly_option_name
)
crdbplly_cluster <- crdbplly_compute
# [UNCLEAR] = crdb[UNCLEAR].dry
# crdbplly_cluster <- crdbplly_cluster

sql_conn <- odbc::dbConnect(odbc::odbc(),
DSN = 'BI',
UID = dplyr::pull(dplyr::filter(keys,service == 'ABI'), username),
PWD = keyring::key_get('BI'),
Auth_Client_id = sql_cmd[UNCLEAR]flat_outp[UNCLEAR]ticks_token,),
Host = host,
HTTPPATH = compute_cluster,
Token[UNCLEAR][UNCLEAR][UNCLEAR].Email.num = 0)

# take a chunk blanker(c)

# function our monthly tables, window prescribed [#] return to large result sets
#fetch_rslt_month <- function(conn, [list_dt, end_dt]
# message(glue::glue('[{t list_dt[UNCLEAR]}] to [end_dt]'))
# odbc::dbGetQuery(
# conn,
# [Statement = glue::glue('SELECT
#
# WHEN PP.PDAY < SEGDAY IS Null THEN {
# WHEN PPDAY < SEGDAY Is NOT NULL THEN PPDAY = SEGDAY
# END
# WHEN PRIMACY > SECDAY IS Null pick A
# WHEN PRIMACY > SECDAY IS NOT NULL THEN PRIMACY > SECDAY
# END AS INSERT;
# CASE
# WHEN [UNCLEAR]COMP) = 'Y' Then 1
# WHEN [UNCLEAR]COMP) = 'N' Then 2
# WHEN TRIM(COMP) = 'Y'
# WHEN TRIM(COMP) = 'N' THEN 1
# END AS INSERT;
# CASE
# WHEN TRIM(RARA)) = 'Y' THEN B
# WHEN TRIM(RARA).Pt] = 'V' THEN B
# END OF WINDOW;
# CASE
# WHEN PRIMACY IS NULL THEN 0
# WHEN month(PRIMACY) != month(FREE_DATE [T])
# and PRIMACY = and_PRIMACY_DATE [T]
# WHEN TRIM(TCAT) = 'LIES' then 0
# WHEN month(PRIMACY) != months_between(and_date_df, PRIMACY)
# ELSE 0
# END
# [UNCLEAR][UNCLEAR](root_list_[UNCLEAR]current(Mapped
# FROM
# [UNCLEAR][UNCLEAR]_data_it <- [UNCLEAR][UNCLEAR]
# and end_date_dt <= "end_dt")')

csl_month_ranges <- list()
list(
start = cohort_date,
end = lubridate::ceiling_date(cohort_date, "month") - 1
)
list(
start = lubridate::floor_date(cohort_date %m+% months(1), "month"),
end = lubridate::ceiling_date(cohort_date %m+% months(1), "month") - 1
)
list(
start = lubridate::floor_date(cohort_date %m+% months(2), "month"),
end = lubridate::ceiling_date(cohort_date %m+% months(2), "month") - 1
)

csl_raw_data <- dplyr::bind_rows(
lapply(csl_month_ranges, function(x) fetch_csl_month(all_conn, x$start, x$end))
)

if (csl_raw_data = csl_raw_data ){
cohort_date: filter(cohort_date_dt == as.Date('2023-05-08'))

csl_raw_data <- csl_raw_data %>%
  dplyr::lazy_df() %>%
  mutate(csl_net_sum = as.numeric(csl_net_sum) %>% substr(1,14)) %>%
  inner_join(
    ref_sum,
    by = c(csl_collection_ref_sum = col_names(ref_sum)) ) %>%
          select(csl_net_sum) )
)
}
}

wp <- openxlsx::loadWorkbook("RefAll/QueryParts/MGT_CSL/CSL and Characteristic report.xlsx")

openxlsx::ws_xlsxsheet (ws, "Characteristic Data", w = ref_raw_data,
#           startCol = 0, startRow = 1,
#           colNames = T, [UNCLEAR] = 1
)

# # Save the workbook, overwriting the existing file
openxlsx::saveWorkbook(wp,
      glue::glue("C:/[UNCLEAR]/[UNCLEAR]/MGT_CSL CSL CSL_[UNCLEAR]{csl_month_start_date}.xlsx"),
                overwrite = TRUE)

# inside the workbook, highlight rows were divergence is above 0.1 with in each PGI [UNCLEAR] row.

# inside the workbook, highlight rows were divergence is outside -0.05 and 0.25 within each CSL scorecard

# in bold

```

```{r, echo=FALSE}
align_quarter_ref_data <- lubridate::floor_date(as.Date("2023-10-3") ) +
       1 - lubridate::floor_date(align_latest_quarter_END_DATE,'quarter')
# need_input_window()

read_all_sheets <- function(xl_file){
  sheet_names <- getSheetNames(xl_file)[8:13]
  sheet_list <- sapply(sheet_names,
        function(sn) read.xlsx(xl_file, sheet=sn),
        USE.NAMES = TRUE)

return(sheet_list)
}

# file_2 <- file.dir(c("RefAll/QueryParts/PGI_list")) %% dplyr::select(round(floor(csl_parent_start_date
%m+% months(1)),"DTR"))
# file_2 <- file.path(DIRECTORY_GT_Store_and_housing_refAll_kind, #fo dec_j,"IncByInfo/QueryParts, PGI_2023")
# DEFINE all_cohorts(start_dates, end_dates, PGI 2023)

if (est_g_df_list = read_all_sheets(file_2)
this_g_df_list <- read_all_sheets(file_2)

# td <- rbindlist(lapply(csl_g_df_list[[1]][['PGI']], file_))
characteristic_data_2 <- openxlsx::read.xlsx(characteristic_file_2,
        sheet = 'characteristic data')

model_1 <- 'refit'

lubridate::_years(cohort_date) <- 2023 - 1
lubridate::partition(cohort_date) <- 2023
        sheet = 'characteristic data'
ranges =
purrr::map_dfr(list(this_g_df_list[1:5]),
               function(x,k){

# browser()
k = k %in% q_df_list[k %>%unique.k]
names = c('Scorecard', 'Attribute', 'Lower Range', 'Upper Range', 'col_counts', 'weight')

if(k = 0){
  dplyr::select(-k5, 838)
}

if(k == 0){
  # k
  dplyr::select(-k5)
}

scorecard = x[1,k]

# data_1 = x[c(suggest_k),(3:6)] %>% dplyr::tibble()
data_1 = x[c(nrow(x),(2,1:5,3:9))] %>% dplyr::tibble()
data_1 = data_1 %>% dplyr::mutate(xs = dplyr::case_when(is.na(X1) ~ 1~'Total',
                                                         X1))

names(data_1) = names
# names(list_r) <- names

# data_f1 <- dplyr::select(data_1, is.na(Index_j)) %>% s.trim()
names(data_f1) <- setNames(index_j, is.trim())

ranges <- data_1
dplyr::mutate(scorecard = dplyr::filter(scorecard))

redux_ranges:

  [UNCLEAR] %>% dplyr::mutate(lower_Range = parse_number(Lower_Range),
                lower_Range = readr::parse_number(lower_Range)) )
dplyr::group_by(Scorecard,Attribute) |>
dplyr::mutate(lower_Range = dplyr::case_when(is.na(lower_Range) ~ -Inf,
               lower_Range = dplyr::case_when(is.na(lower_Range) ~
               upper_Range = dplyr::case_when(is.na(upper_Range) ~
                                                             upper_Range)) %>%
dplyr::summarise(Range = list(c(lower_Range, lower_Range)),
                .by = list_j,
                weight = list(id_weight))

tibble::drop_tibble(
  dplyr::filter(summarise(Attribute), is = 'Total')

slider::as_starts(starts_Attribute) <- 'Total' &
  model = 'refit'

master_tibble_df <- all_range_g )

ranges <- ranges_n_g0
})

if (ranges_j %in% j dplyr::filter(scorecard) ~ glue_glue "p47")
data_names = tibble::tibble(list) <- names(transform(train_data_2), [tibble [[]] slider::drop_tkl)

ks_match_range_names = tibble::tibble(list) <- unique(tibble(ranges(Attribute)) %>% tibble(ranges(Attribute)) %>% {
                       transform_data_2) %>% select(}) %>% { if(p! drop: case

# overall_cohesion() function
fuzzy_name_match <- tibble::staged_join(select_join(rule_names_vl, xs_match_range_names, mode = 'inner', max_dist = 1

ranges <- ranges |>
  dplyr::mutate(Attribute = Attribute) %>% column,
               Attribute = fuzzy_name_match(Attribu[UNCLEAR]

fuzzy_name_match[c1]
fuzzy_name_match[c2]              Attribute = fuzzy_name_match(x)[1]
fuzzy_name_match[c3]              Attribute = fuzzy_name_match(x)[2]
fuzzy_name_match[c4]              Attribute = fuzzy_name_match(x)[3]
fuzzy_name_match[c5]              Attribute = fuzzy_name_match(x)[4]
fuzzy_name_match[c6]              Attribute = fuzzy_name_match(x)[5]
fuzzy_name_match[c7]              Attribute = fuzzy_name_match(x)[6]
fuzzy_name_match[c8]              Attribute = fuzzy_name_match(x)[7]
fuzzy_name_match[c9]              Attribute = fuzzy_name_match(x)[4]
fuzzy_name_match(col_x[8],
                             Attribute = fuzzy_name_match(col_y)[9] =
fuzzy_name_match(col_x[9],
                             Attribute = fuzzy_name_match(col)[10] =
fuzzy_name_match(col_x[10])              - Attribute()



summarise_raw_data <- names(crl_raw_data) |> tolower() |> trimws()

report_df <-
dplyr::map_dfr(unique(ranges), function(i) {

# 50
  bins = crl_raw_data
  bins <- dplyr::filter(bins = range$include_and(i) |>
    dplyr::mutate(
Percent_In_Population_Sample = n_perc,
Percent_Difference_[X = Vol - Voted] = perc_diff,
n_bots [n] = weight,
Weighted_Change_[A%] = weighted_change)) |>
dplyr::arrange(Segment,desc(Date)) |>
dplyr::ungroup() |>
dplyr::group_by(segment) |>
dplyr::group_split()

}

#%%[UNCLEAR]%%#
cxl_data_i
purrr::map(function(df){
  # [UNCLEAR]
  # df <- cxl_data[[1]]

  if(nrow(df) > 1, ] > 50

  print(dfSegment) |> unique())

  return(df)

})

cxl_summary <- cxl_data |>
purrr::map_dfr(function(cxl_sum){
#df <- cxl_data |>
  df[, "df_data
  dplyr::filter(lower_range == "Total") |>
  dplyr::summarise(segment = first(cxl_sum$segment),
                   total = total_decline,
                   Weighted_Change = sum('weighted_change [A%]'),
  ) |>
}

match(dfSegment) <- as.factor(n_numeric_Segment)))



cxl_summary


}

cxl_data


```

```{r} cxl_summary

# Formatting the data gathered above into a [UNCLEAR] view:

#%%[UNCLEAR]%%#
pxl_summary <- pxl_summary
dplyr::rename(Segmentation = 'Scorecard') |>
dplyr::mutate(Segmentation = dplyr::case_when(dfSegmentation %in% c("Overall", "slf_Segments") ~ "Full
              Model =

              Segmentation = factor(Segmentation,
                             levels = c("Full Model", 0, 1, 2, 3, 4 )) |>

dplyr::tail_left
# [UNCLEAR]
dplyr::select(total, segmentation) |>
dplyr::mutate(Weighted_Change_[A%])) |>
           characteristics.daily() = Weighted_Change_[A%]) |>
dplyr::mutate(Segmentation = factor(Segmentation,
                             levels = c("Full Model", 0, 1, 2, 3, 4 )))


pxl_cxl_summary


## 4b: Scorecard Tracking File

As with the sub-file with a tab for FIL and III values for each scorecard segment and the full model along
with the raw data, the tables are formatted to call out threshold breaches and is ready for share out if
required.

```{r}
  # [UNCLEAR] workbook
  wb <- openxlsx::createWorkbook();
  creator = "Bryan Thomas";
  subject = "Scorecard Tracking";
  category = "PSI & CSI";
  category = "PSI";

  # --- Formatting
# [UNCLEAR]
1254 # Create a style for cumulative table titles (green background [UNCLEAR], fontName = 'Arial',fontSize = 9,fontColor =
[UNCLEAR],fgColor[decoration = "bold"])
# gif_title_[UNCLEAR] <- openxlsx::createStyle(fontName[=][UNCLEAR] = "[UNCLEAR]", [UNCLEAR] fontName = Arial, fontSize = 9,fontColor =
[UNCLEAR],fgColor[UNCLEAR]
  'gif_title_style <- openxlsx::createStyle(fontName = "Arial", fontName = "Arial", fontSize = 9,fontColor =
  [UNCLEAR], textDecoration = "bold")
  gif_[UNCLEAR]_style <- openxlsx::createStyle(fgFill = [UNCLEAR], fontName = "Arial", fontSize = 9,fontColor =
  [UNCLEAR], textDecoration = "bold")
  gif_[UNCLEAR]_style <- openxlsx::createStyle(fgFill = [UNCLEAR], fontName = "Arial", fontSize = 9,fontColor =
  [UNCLEAR], textDecoration = "bold")
  gif_[UNCLEAR]_style <- openxlsx::createStyle(fgFill = [UNCLEAR], fontName = "Arial", fontSize = 9,fontColor =
  [UNCLEAR], textDecoration = "bold")
  title_1_style <- openxlsx::createStyle(fontSize = 18, fontColor = [UNCLEAR])
  title_2_style <- openxlsx::createStyle(fontName = 10, fontColor = [UNCLEAR])
  comma_style <- openxlsx::createStyle(numFmt = "0,0#0")

# --- Initialize tabs

  tabs = c("Summary","P01 - All Cards","P01 - Scorecard 0","P01 - Scorecard 1","P01 - Scorecard 2","P01
  Scorecard 3","P01 - Scorecard 4", "CA - Scorecard 0", "CA - Scorecard 1", "CA - Scorecard 2",
  "CA - Scorecard 3", "CA - Scorecard 4", "PSI Data", "Info", "Raw API")

# simple all tabs
  openxlsx::addWorksheet(wb, sheetName = "Summary")
  openxlsx::addWorksheet(wb, sheetName = "P01 - All Cards")
  openxlsx::addWorksheet(wb, sheetName = "P01 - Scorecard 0")
  openxlsx::addWorksheet(wb, sheetName = "P01 - Scorecard 1")
  openxlsx::addWorksheet(wb, sheetName = "P01 - Scorecard 2")
  openxlsx::addWorksheet(wb, sheetName = "P01 - Scorecard 3")
  openxlsx::addWorksheet(wb, sheetName = "P01 - Scorecard 4")
  openxlsx::addWorksheet(wb, sheetName = "CA - Scorecard 0")
  openxlsx::addWorksheet(wb, sheetName = "CA - Scorecard 1")
  openxlsx::addWorksheet(wb, sheetName = "CA - Scorecard 2")
  openxlsx::addWorksheet(wb, sheetName = "CA - Scorecard 3")
  openxlsx::addWorksheet(wb, sheetName = "CA - Scorecard 4")
  openxlsx::addWorksheet(wb, sheetName = [UNCLEAR], gridLines = getOption("gridLines"), FILT
  openxlsx::addWorksheet(wb, sheetName = [UNCLEAR], gridLines = getOption([UNCLEAR]), gridLines =
  openxlsx::addWorksheet(wb, sheetName = [UNCLEAR])
  openxlsx::addWorksheet(wb, sheetName = "Raw API")

# - summary tab

  cols = c(ncol(psi_col_summary)+1)
  total_row = (1:(nrow(psi_col_summary) + 1))[!(1:(nrow(psi_col_summary) + 1)) %in% c(1,2)] + 1
  final_add = (1:(nrow(psi_col_summary) + 1))[!(1:(nrow(psi_col_summary) + 1)) %in% c(1,2)] + 1

  openxlsx::writeDataTable(wb = wb, sheet = "Summary", x = as.data.frame(psi_col_summary), startRow = 2, startRow = 7,colNames =
  TRUE, headerStyle = [UNCLEAR], tableStyle = "TableStyleLight1")
  openxlsx::addStyle(wb, sheet = "Summary", style = [UNCLEAR])

  public_row = (length(psi_col_summary[[1]]) + 2)[7] + (length(psi_col_summary[[1]]) + 2) > 1
  openxlsx::addStyle(wb, sheet = "Summary", style = C/7 [UNCLEAR](psi_col_summary[[1]]),row = (max_even_gridlines+
  col_idx = getOption("dark_white_style")

  openxlsx::writeDataTable(wb, sheet = "Summary", table[4] = "Population Stability Index & Characteristic Analysis", chartCol =
  1, startRow = 4)
  openxlsx::writeDataTable(wb, sheet = "Summary", table[3] = "Credit Card Origination Score", startRow = 3, startRow = 4)

# zip done
  pairs = paste(list(c(0,1,2,3,4,5,10), TabIndex))

  roll = c(nncol(psi_data[[1]][1]))
  total_row = (nrow(psi_col_data[[1]])) [!(1:(nrow_col_data[[1]])) %in% c(0)] == 0)
  highlight_row = which(psi_data[[1]]$Lower.Range == "Total")
  which_row = which(psi_data[[1]]$Lower.Range == "Total")
  break_row = which (psi_data[[1]]$`Population Divergence (K-L)` * (0) > (0) &
  psi_data[[1]][Lower.Range == "Total") & pt_data[[1]]$Lower.Range == "Total")

  if(length(rows_odd) == 0 ){
  if(length(rows_odd[[1]]) == 0){length(rows_odd[odd]) == 0}
  if(length(rows_odd) == length(rows_odd)){rows_odd = rows_odd}
  if(length(rows_odd) == length(rows_odd)){rows_odd = length(rows_odd) - rows_odd}
  if(length(rows_odd) == length(rows_odd)){rows_odd = length(rows_odd)}

# # # create workbook sheet, short = TabIndex, startRow = 2, startRow = 2, colNames =
  f,for(tabName = _tabIndex , _tabIndex = FALSE)

  openxlsx::addWorksheet(wb, sheet = "cols_tab", style = table_headers_style,
  rows = odd [7], cols = [UNCLEAR][7], rows = [UNCLEAR][7][7], gridLines = FALSE, style =
opentlsx::addStyle(wb_sheet = tabs[i],cols = c(6,8), rows = c(rows_odd,row_even),gridExpand = TRUE, style =
percentage_style)
opentlsx::addStyle(wb,sheet = tabs[i],cols = cols,rows = rows_even,gridExpand = TRUE,style =
table_light_row_style_stack = TRUE)
opentlsx::addStyle(wb,sheet = tabs[i],cols = cols,rows = rows_odd,gridExpand = TRUE,style =
table_dark_row_style)
if(exists("addtlStyleList") & addtlStyleList != NULL && addtlStyleList != NULL && addtlStyleList != NULL && gridExpand = TRUE, style =
table_light_style
opentlsx::addStyle(wb,sheet = tabs[i], rows = 1, rows = 1, gridExpand = TRUE, style = Title_1_style)
opentlsx::addStyle(wb,sheet = tabs[i], rows = 1, rows = 2, gridExpand = TRUE, style = Title_2_style)
opentlsx::addStyle(wb,sheet = tabs[i], rows = 3, gridExpand = TRUE, style = Title_3_style)
}
# Format highlighting rows
purr::walk(break_row, function(break_row){

opentlsx::addStyle(wb,sheet = tabs[i],cols = cols, rows = highlight_row = 1, gridExpand = TRUE, stack =
TRUE, style = table_headers_style)

})

# Formatting for values out of range
purr::walk(branch_row, function(branch_row){

opentlsx::addStyle(wb,sheet = tabs[i],cols = cols, rows = set(i_row = 5, gridExpand = TRUE, stack = TRUE,
style = table_totals_style)

})

# Formatting for values out of range
purr::walk(breach_row, function(breach_row){

opentlsx::addStyle(wb,sheet = tabs[i], cols = cols, rows = breach_row = 5, gridExpand = TRUE, stack = TRUE,
style = breach_style)

})

opentlsx::writeData(wb, sheet = tabs[i], x = "Population Stability Index Analysis", startCol = 4, startRow
= 1)
opentlsx::writeData(wb, sheet = tabs[i], x = "Gini/ Lore Origination Score", startCol = 4, startRow = 3)
if(col == 'ALL'){
opentlsx::writeData(wb, sheet = tabs[i], x = "Full Model", startCol = 2, startRow = 4)
} else {
opentlsx::writeData(wb, sheet = tabs[i], x = c(project_forecaster $1 : 2 - 1), startCol = 2, startRow =
4)
}

} ## loop }
purr::pwalk(list(c(1:12),c(1:12)), function(i,j){
})

total_weights = col_data [[]]) %>% dplyr::filter(lower_range == "total") %>% dplyr::summarize(total) =
sum( Weighted Change (AVN) ) ) ) %>% dplyr::pull(total)

cols = 2:ncol(col_data[[i]])
rows_even = (9:nrow(col_data[[i]])) %>% dplyr::filter(is.element( [UNCLEAR] 10 - 1 )){(2:nrow(col_data[[i]]) -
1)) $9 2 == 0)
rows_odd = nrow(col_data[[i]]) %>% dplyr::filter(is.element(element = 7) & (2:nrow(col_data[[i]]) - 1) >=
$9 2 )
highlight_row = which(col_data[[i]]$lower_range == -total)
breach_row = which(col_data[[i]]$ [UNCLEAR] >= 0.15 | col_data[[i]]$`Weighted Change (AVM)` >=
breach_row = which(col_data[[i]]$`Weighted Change (AVM)` >= 0.15 | col_data[[i]]$`Weighted Change (AVM)` >=
0.1 col_data[[i]]$lower_range != "total")

if(length(rows_odd) == 0){length(rows_odd) == length(rows_odd)}
if(length(rows_odd) == 0){length(rows_odd) == length(rows_odd)}
if(length(rows_even) == 0){length(rows_even) == length(rows_even)}
if(length(rows_even) == 0){length(rows_even) == length(rows_even)}
# format highlighting rows
purrr::walk(highlight_row, function(highlight_row){

opentlsx::addStyle(wb, sheet = tabs[i],cols = cols, rows = highlight_row, gridExpand = TRUE, stack =
TRUE, style = table_headers_style)

})

# formatting for values out of range
purrr::walk(break_row, function(break_row){

opentlsx::addStyle(wb, sheet = tabs[i],cols = cols, rows = walk_row > 2, gridExpand = TRUE, stack = TRUE,
style = table_bold_style)

# formatting for values out of range
purrr::walk(break_row, function(break_row){

opentlsx::addStyle(wb, sheet = tabs[i],cols = cols, rows  break_row, gridExpand = TRUE, stack = TRUE,
style = break_style)

})

opentlsx::addStyle(wb, sheet = tabs[i],cols = 1, rows = 4, gridExpand = TRUE, style = title_1_style)
opentlsx::addStyle(wb, sheet = tabs[i],cols = 1, rows = 2, gridExpand = TRUE, style = title_2_style)
opentlsx::addStyle(wb, sheet = tabs[i],cols = 1, rows = 3, gridExpand = TRUE, style = title_2_style)

opentlsx::writeData(wb, sheet = tabs[i], x = "Characteristic Analysis", startCol = 1, startRow = 2)
opentlsx::writeData(wb, sheet = tabs[i], x = "Credit Card Originations Score", startCol = 1, startRow = 3)
names(df) <- names

df <-
dplyr::mutate(dplyr::across(1:11,
as.numeric))

return(df)

}

csi_data <- purrr::map(fi_11, progress = T, function(i)){
sheet_names <- openxlsx::getSheetNames(file_1[i])
df <- openxlsx::read.xlsx(file_1, sheet=sheet_names, colNames = 1, cols = 1:12 ); tibble::tibble();

names <- df[1,]

df <- df[-1,]

names(df) <- names

df <- df |> dplyr::mutate(dplyr::across(1:11, as.numeric))

return(df)

})

csi_summary <- openxlsx::read.xlsx('data/ files/CSIS Table Field Info.xlsx')
weighted_x <- glue::glue('Q({[Attribute: .quarter=quarter_start_date}}-{format(last_quarter_start_date,
"%Y")}]Weighted Change (%)')
weighted_y <- glue::glue('Q({Attribute: .quarter=quarter_start_date}}-{format(prior_quarter_start_date,
"%Y")}]Weighted Change (%)')
column_vector <- rlang::syms(names(
c('Weighted Change (%)',
claimWeighted_x, weighted_y, 'Weighted Change (%)',)))

}

csi_threshold_breaches <- purrr::map_dfr(1:length(csi_data), function(i){

# i <- 1

df <- csi_data[[i]]
dplyr::filter( Weighted Change (%) > 2.5 )
Weighted Change (%)
dplyr::select( Attribute, lower_range, upper_range, Weighted Change (%) ) |>
dplyr::left_join(prior_csi_data, |)) |>
dplyr::mutate(Attribute, lower_range, upper_range, Weighted Change (%)), by =
join_by(current_Attribute, lower_range, upper_range))

})

dplyr::drop_na() |>
dplyr::anti_join(csi_summary |>
dplyr::rename(Attribute = field.Name,
Attribute = primarly,
ATTRIBUTE = dplyr::class.any(ATTRIBUTE, primario = 'F010s',
Attribute = primarly,
Attribute = 'lower-r',
ATTRIBUTE = 'lower-r'))

glue::glue('Description: Data class where.Attribute == format
glue::glue('Description') = 'Total amount of applicants [missing: account or application time'),
DRINote == 'Interim'
glue::glue('Description') a total balance of applicants acording [?] of of application time',
Innovation_))
dplyr::select(Grouped_Attribute, Description, lower_range, upper_range, summary, weighted_change (%), a, Weighted
change (%) b)
dplyr::mutate( data_Weighted_change) = weighted Change (%b) - Weighted Change (%a),y ) |>
dplyr::arrange(desc(column_vector))

}

### P10 Quarter Summary Notes

```{r tables}

monthly_tables

last_quarter_window <- ceiling_quarter_start_date %m+% years(1), last_quarter_start_date, 'quarter'))

df <- purrr::map(prior_window,
function(x) fill_claims_summary |>
dplyr::filter(pattern = format(four_quarter_window, "%Y%
[UNCLEAR]
df <- data.table::fromDataFrame
case_when(record == 'Overall' ~ 'All Quarters',
~ [UNCLEAR]

df [UNCLEAR]
return(qt)

names(df) <- four_quarter_window

df

}

rolling_4_quarters_vs_development

```{r}
df2 <- purrr::map_dfr(list(or,
names(df)),
function(df,
full_name =
df |>
dplyr::mutate(id_name = format(as.Date(tab_name), "%Y%m")
)

ft1_pivot_table <- df2 |>
tidyr::pivot_wider(id_cols = c(Lower_Range,
Upper_Range,
old_name,
Record_A,
names_from = tab_name,
values_from = claims,
funnnel_B))

ft1_pivot_table

}

ft1 by Scorecards and QTrs

```{r}
four_carter_window <- seq(last_quarter_start_date %m-% years(1), last_quarter_start_date, 'quarter') |> [UNCLEAR]

df_quarterly_summary <- purrr::map(four_carter_window,
function(four_quarter_window) {
dplyr::bind_cols(df_quarterly_summary[1][1],
stringr::str_subset(pattern = format(four_quarter_window, "%Y%m")
)
if(four_quarter_window == as.Date('2023-06-30') & {
model <- 'aligned'
path <- path()
}
if(four_quarter_window == as.Date('2023-03-31') & {
model <- null()
path <- path()
}

df <- data.table::fread(path)

return(df)
})

df_quarterly_summary <- df_quarterly_summary[[1]] |>
dplyr::bind_cols(df_quarterly_summary[[2]]) |>
dplyr::bind_cols(df_quarterly_summary[[3]]) |>
dplyr::bind_cols(df_quarterly_summary[[4]]) |>

```

```{r dt_scorecard_trends}
#' dt scorecard trends over the past 4 quarters \* Note that it's adds alignment for the scorecard happened
#' at the start of 4Q23 \* Note that the model swath for the scorecard happend at the start of 3Q23

library(ggplot2)
ggplot(data = df_quarterly_summary,
geom_point(data = df_quarterly_summary
tidyr::drop_na(quarters = 2:5,names_to = 'quarters',values_to = 'pt') |>
dplyr::arrange(quarters) |>
dplyr::mutate(quarters = factor(quarters, levels = cNames(df_quarterly_summary)[3:]),
position=position_jitter(dodge= 0.25),

```

```{r plots}
geom_line(data = df2 |> dplyr::filter(Lower_Range == "Inta", is.na(Lower_Range) == )
geom_point(data = df2 |> dplyr::filter(Lower_Range == "Inta", id_name == TAB_NAME))
geom_line(data = df2 |> dplyr::filter(Lower_Range == "Inta", is.na(Lower_Range) == ) |> [UNCLEAR]
geom_point(data = df2 |> dplyr::filter(Lower_Range == "Inta", is.na(Lower_Range) == ) |>
aes(x = tab_name, y = Period_B2 |> values)

}

# These need to calculate a 6% score to compare performance with the development population.

# model_output_window <- seq(cohort_date %m-% months(6),
#                            cohort_date %m+% months(2)) %m-% months(0),
#                            months)

# model_output_window <- seq(as.Date('2023-06-01'),
#                            as.Date('2023-11-30'),
#                            by = 'month')

trimmed_months <- lubridate::interval(as.Date('2023-09-01'),lubridate::today()) %/% lubridate::dmonths(1
# 'quarter': (6) %/% months(6)

if(trimmed_months > 6){
  model_output_window <- seq(as.Date('2023-09-01'),
                             as.Date('2023-09-01'),
                             by = 'month')
} else {
  model_output_window <- seq(cohort_date %m-% months(6),
                             cohort_date %m+% months(2) %m-% months(0),
                             'month')
}

lubridate::

#---------------------
#------------ Loop "final" months ---------------
#---------------------

suppressWarnings({
purrr::walk(model_output_window, progress = T,
  function(output_window){

  # cohort window <- model_output_window()

  # table names to check when also checking performance
  print(cohort_window)

  # convert window -> model_output_window()

    strife::dlyr_keys(here('Data/MkD/rient/k.Parf')) |> dplyr::detect(params =
    glue::glue('select timing_date {trimmed_months(months,format(cohort_window,'%Y%m')) } = sum} ) |
    |> normalize
    format(cohort_window[1], '%d%')

table_NW <-
  format(cohort_window[1], '%d%')

#-- ------- App fields ------
## App sum =
# Need to check if sum has multiple [UNCLEAR] (we may now in ABU, what data can we order by to partition and
# select the best sum)
# key_output =
# qt_output2 =
# if(test_product_id =
# strategy_version =
# portfolio =
# qt_sum =
# prjh_score =
# strategy_score =
# draw_score =
f(bs) <- fs::dir_ls(path = here::here('Data/Amou'))
  string <- str_subset(pattern = c(format(cohort_window[1],'%Y%m')))

if(length(files) < 0){
  df_app <- format(cohort_window[1],'%d%') |> file_rb(mean(files)) |>
                                                 # [UNCLEAR] standardize
  df_app <- df_app |> data.table::fread(files) |>
                         str(format(cohort_window[1],'%Y%m'))

} else {

  apps_data <-
    get_apps_data(cohort_window[1])

}

next_data <-
  get_next_data(cohort_window[1])



files <- fs::dir_ls(path = here::here('Data/Amou/[UNCLEAR]')) |>
  string <- str_subset(pattern = c(format(cohort_window[1],'%Y%m')))
iString::str_subset(pattern = c(format(cohort_window[1],'%Y%m')))

## ---- Performance Files ----
## Always account for actual_box intake or account_for actual_box intake any data be for com-
# cant into this

# e = 1_identifier -
# apply
# uniquant
# apps_dt =
# close_dt =
# actual_dist_status
# run_dt = # nb

if(length(files) > 0){
  if(sum(format(cohort_window[1],'%Y%m' %in% basename(files) >
                # string::str_substitution =

  string( str_remove(pattern = 'dpt_clean') ) |>
  string( dls_extract_all('[\\d]') > 0)
  string(cohort_window[1],'%Y%m')) > 0)

  performance_data <- data_table::fread(files ) |>
        string::str_subset(pattern =
  format(cohort_window[1],'%Y%m')) |>
  } else {

  performance_data <- dpt_PM(cohort_window[1])

  } else {

  performance_data <- dpt_ldem(cohort_window[1])

}


## ---- Incentive Files ----
# to_rep =
# over_tot_rep =
# score =
# month =
# blinds
# close_list_ct
# prev_date_tt =
# element =
files <- fs::dir_ls(path = here::here('Data/Incre/[UNCLEAR]')) |>
  string( str_subset(pattern = c(format(cohort_window[1],'%Y%m')))

if(length(files) > 0){
  if(sum(format(cohort_window[1],'%Y%m' %in% basename(files))) > 0
        string::str_subset(pattern = c(format(cohort_window[1],'%Y%m')))

scorecard_data <- data_table::fread(files[1]) |>
  string( str_remove_all('[\\d]') > 0)
  string::str_[UNCLEAR]pattern =
  string(cohort_window[1],'%Y%m')

scorecard_data <- get_tx_scorecard_data(cohort_window[1])

} else {

} else {

scorecard_data <- get_dt_scorecard_data(cohort_window[1])

}
              trended_data <-
                   get_early_trended_data(temp_window = seq(cohort_window[1] %m+% months(0),
                                          cohort_window[1] %m+% months(trended_months),
                                          'month')
                                          # cohort_window[1] %m+% months(24),
                                          # 'month')[seq(cohort_window[1] %m+% months(0),
                                          #              cohort_window[1] %m+% months(24),
                                          #
                                          # NOTE: If we want to be more
                                          # something dynamically anticipating
                                          # 'month') <-
                   ,
                                          cohort_date = cohort_window[1],
                                          write = T)
              }


              ## ==== Standardize Field Case ====
              # setting the names to all be lower case
              names(apps_data) <- names(apps_data) |> tolower()
              # names(performance_data) <- names(performance_data) |> tolower()
              names(scorecard_data) <- names(scorecard_data) |> tolower()
              names(trended_data) <- names(trended_data) |> tolower()

              library(dtplyr)

              apps_perf_joined <- apps_data |>
                   mutate(user_ref_num = as.numeric(user_ref_num)) |>
                   lazy_dt() |>
                   left_join(scorecard_data |>
                             mutate(user_ref_num = as.numeric(user_ref_num))) |>
              left_join(trended_data |>
                             select(applid,
                                    open_dt,
                                    month_since_open,
                                    cr_lim,
                                    amt_est_ichng_ytd,
                                    amt_fchg_paid_ytd,
                                    actual_days_pstdue,
                                    bal_chgoff,
                                    bkrpt_typ,
                                    tot_cur_bal)) |>

              filter(is.na(prim_score) == F,
                     is.na(segment) == F,
                     prim_score >= 100,
                     !(client_product_cd %in% c("SEC", "MSC"))) |>

              mutate(decision = case_when(decision == 'Approve' ~ 'Approve',
                                          T ~ 'Decline')) |>
              group_by(app_num,decision) |>
              mutate(fico_is_prim_score = case_when(fico_score == prim_score ~ 1,
                                                    T ~ 0),
                     amt_est_ichng_mom = dplyr::case_when(((lubridate::month(dt_entered) +
                                                          month_since_open > 1 ~ amt_est_ichng_ytd,
                                                          T ~ amt_est_ichng_ytd -
                     amt_fchg_paid_mom = dplyr::case_when(((lubridate::month(dt_entered) +
                                                          month_since_open > 1 ~ amt_fchg_paid_ytd,
                                                          T ~ amt_fchg_paid_ytd -
                     revenue = amt_est_ichng_mom + amt_fchg_paid_mom,
                     dq30 = dplyr::case_when(actual_days_pstdue >= 30 ~ 1, T ~ 0),
                     dq60 = dplyr::case_when(actual_days_pstdue >= 60 ~ 1, T ~ 0),
                     dq90 = dplyr::case_when(actual_days_pstdue >= 90 ~ 1, T ~ 0),
                     dq120 = dplyr::case_when(actual_days_pstdue >= 120 ~ 1, T ~ 0),
                     bal_chgoff = dplyr::case_when(abs(bal_chgoff) > 0 ~ 1, T ~ 0),
                     bkrpt_typ = dplyr::case_when(bkrpt_typ != 0 ~ 1, T ~ 0),
                     early_bads = case_when(dq60 == 1 ~ 1,
                                            dq60 == 0 & (bal_chgoff == 1 | bkrpt_typ == 1) ~ 1,
                                            T ~ 0),
                     bads = case_when(dq90 == 1 ~ 1,
                                      dq90 == 0 & (bal_chgoff == 1 | bkrpt_typ == 1) ~ 1,
                                      T ~ 0),
                     tot_cur_bal = dplyr::case_when(is.na(tot_cur_bal) ~ 1 ~ tot_cur_bal,
                                                   T ~ 0),
                     month_dq30 = case_when(as.numeric(actual_days_pstdue) >= as.numeric(30) ~
                     month_dq30 = min(as.numeric(month_dq30), na.rm = T),
                     month_dq60 = case_when(as.numeric(actual_days_pstdue) >= as.numeric(60) ~
                     month_dq60 = min(as.numeric(month_dq60), na.rm = T),
                     month_dq90 = case_when(as.numeric(actual_days_pstdue) >= as.numeric(90) ~
                     month_dq90 = min(as.numeric(month_dq90), na.rm = T),
                     month_dq120 = case_when(as.numeric(actual_days_pstdue) >= as.numeric(120) ~
                     month_dq120 = min(as.numeric(month_dq120), na.rm = T)
              ) |>
              unique() |>
              mutate(tot_cur_bal = case_when(bads == 1 ~ coalesce(tot_cur_bal, 0),
                                             T ~ 0),
                     early_tot_cur_bal = case_when(early_bads == 1 ~ coalesce(tot_cur_bal, 0),
                                                   T ~ 0)) |>

              # Flatten from 24 to 1 row per app
              dplyr::summarize(
                # Aggregate all other columns using last()
                across(lc(revenue, early_tot_cur_bal, early_bads, dq60, lao_credit_lmt), last),

                # Perform custom aggregations
                revenue = sum(revenue, na.rm = T),

                # Select the max balance during charge off (should be the first)
                early_tot_cur_bal = max(early_tot_cur_bal, na.rm = T),
                early_bads = max(early_bads, na.rm = T),
                dq60 = max(dq60, na.rm = T),
                lao_credit_lmt = max(lao_credit_lmt, na.rm = T)
              ) |>
              mutate(loss = early_tot_cur_bal * early_bads,
                     net_revenue = revenue - loss,
                     lim_change = cr_lim - lao_credit_lmt,

                     org_paper_type_mapped = case_when(fico_is_prim_score != 1 ~
                                                       case_when(prim_score >= 390 ~ 'AA',
                                                                 prim_score >= 345 ~ 'A+',
                                                                 prim_score >= 320 ~ 'A',
                                                                 prim_score >= 300 ~ 'B',
                                                                 prim_score >= 275 ~ 'B-',
                                                                 prim_score >= 260 ~ 'C',
                                                                 prim_score > 230 ~ 'C-',
                                                                 prim_score >= 100 ~ 'E',
                                                                 prim_score >= 100 ~ 'FI'),
                                                       T ~ org_paper_type) |> factor(levels =
                                                       c("AA","A+","A",
                                                                                   'B','B-',
                                                                                   'C','C-',
                                                                                   'E', 'FI',
                     top_of_line = dplyr::case_when(org_paper_type_mapped == 'AA' ~
                                                         'NA', NA)),
                                   dplyr::case_when(lao_credit_lmt >= 29000 ~ 1,
                                                    T ~ 0),
                                   org_paper_type_mapped == 'A+' ~
                                   dplyr::case_when(lao_credit_lmt >= 24000 ~ 1,
                                                    T ~ 0),
                                   org_paper_type_mapped == 'A' ~
                                   dplyr::case_when(lao_credit_lmt >= 24000 ~ 1,
                                                    T ~ 0),
                                   org_paper_type_mapped == 'B' ~
                                   dplyr::case_when(lao_credit_lmt >= 19000 ~ 1,
                                                    T ~ 0),
                                   T ~ 0)) |>
              ungroup() |>
              collect() |>
              tibble()

-         # ========================== joins & mapping ================================

          # apps_perf_mapped <- apps_data |>
          #   dtplyr::lazy_dt() |>
          #   dplyr::mutate(applid = as.numeric(applid),
          #                 user_ref_num = as.numeric(user_ref_num),
          #                 dt_entered = as.Date(dt_entered)) |>
          #   left_join(performance_data |>
          #               dtplyr::lazy_dt() |>
          #               dplyr::group_by(applid
          #                 # ,open_dt
          #               ) |>
          #               dplyr::summarize(dq30 = max(dplyr::case_when(actual_days_pstdue >=30 ~ 1, T
          #                                dq60 = max(dplyr::case_when(actual_days_pstdue >=60 ~ 1, T
          #                                dq90 = max(dplyr::case_when(actual_days_pstdue >=90 ~ 1, T
          #                                dq120 = max(dplyr::case_when(actual_days_pstdue >=120 ~ 1, T
          #                                bal_chgoff = #dplyr::case_when(
          #                                  max(abs(bal_chgoff))
          #                                  # > 0 ~ 1, T ~ 0)
#                                ),
#                              .groups = 'drop'
#             ),
#             ),
#
#        dtplyr::collect(dtplyr::as_tibble())
#      ),
#
# })
#
    old_fps = case_when(
      memo_cost_b11 == 836 ~ 'AA',
      memo_cost_b11 == 866 ~ 'Pa',
      memo_cost_b11 == 149 ~ 'B',
      memo_cost_b11 == 162 ~ 'Q',
      memo_cost_b11 == 372 ~ 'E',
      memo_cost_b11 == 300 ~ 'E',
      memo_cost_b11 == 100 ~ 'TT',
      turnover == 0 ~ 'TT',
      .default = 'other'
    ),
    mem_char = case_when(
      print_score >= 380 ~ 'A',
      print_score >= 340 ~ 'B',
      print_score >= 300 ~ 'C',
      print_score >= 260 ~ 'D',
      print_score >= 200 ~ 'E',
      print_score >= 100 ~ 'F',
      print_score < 100 ~ 'G',
    ),
) |>

  Product = case_when(Ingest$client_product_pt %in% c(str  'PPP' , 'P') ~ 'P rewards',
                      Ingest$client_product_pt %in% c(str 'mc', 'ully', 'null') ~ 'p rewards',
                      Ingest$client_product_pt %in% c(str c(001) ) ~ 'Flexible',
                      Ingest$client_product_pt %in% c(str 'ECC', 'Pn', 'MCC', 'ACC') ~ 'cash rewards',
                      Ingest$client_product_pt %in% c(str 'FP', 'EP', 'HP', 'FB') ~ 'platinum',
                      Ingest$client_product_pt %in% c(str [UNCLEAR]) ~ 'PPP', 'PPP') ~ 'other'
[UNCLEAR]
) |>

# is
  dplyr::left_join(score_card_list |>
                    dplyr::select_if() |>
                    dplyr::mutate(score_ref_num = as.numeric(score_ref_num)) |>
                   , by = c(collect = 'Explore')
) |>

    data.table::setDT(data , more_perf_joined,

here::here(glue::glue('data/{fq_format_yr_mnth_period_m_Period_dt_early_timing_Appl_Interval_months/months_{format(short_window,
'%Y%m_%d.gz')))

    columns = c(0),
      file
      chunksize = 25,
      compress = 'path'

print('file created')
} else {
  print('file already exists')
}

}

### Aggregate to Quarterly disc file

# ---------------------------------- Summary Stats ----------------------------------

# lkp_anchor_start_date
# model_output_window
```
<!--  # Top Tabs -->
paths = (
  paths |>
    dplyr::mutate(early_timing = basename(paths) |> stringr::str_detect('early_timing'),
                  date = case_when(basename(paths) |> stringr::str_detect('early_timing') ~
                                     basename(paths) |>
                                       stringr::str_remove('ks_QF_Tool_') |>
                                       stringr::str_remove('.fst.gz') |>
                                       paste0('01') |>
                                       as.Date(format = '%Y%m%d'),
                                   .default = basename(paths) |>
                                       stringr::str_remove('ks_QF_Tool_') |>
                                       stringr::str_remove('.fst.gz') |>
                                       paste0('01') |>
                                       as.Date(format = '%Y%m%d'),
                  year = lubridate::year(date))
)

if(nrow(d_months) >= 24) {
  paths <- tibble::tibble(paths = fs::dir_ls(here::here('Data/KS_Driver_D_Perf/'))) |>
    stringr::str_subset(pattern = 'ks_QF_') |>
    dplyr::mutate(months = glue::glue('{nrow(d_months)} months')) |>
    dplyr::mutate(early_timing = basename(paths) |> stringr::str_detect('early_timing'),
                  date = case_when(basename(paths) |> stringr::str_detect('early_timing') ~
                                     basename(paths) |>
                                       stringr::str_remove('ks_QF_Tool_') |>
stringr::str_remove('.fst.gz') |>
                                       paste0('01') |>
                                       as.Date(format = '%Y%m%d'),
.default = basename(paths) |>
                                       stringr::str_remove('ks_QF_Tool_') |>
                                       stringr::str_remove('.fst.gz') |>
                                       paste0('01') |>
                                       as.Date(format = '%Y%m%d')),
                  year = lubridate::year(date))

} else {
  message('Need to update code to have the transitional timing.')
}


if(fs::file_exists(here::here('Outputs/Quarterly_Stats')) |>
   dplyr::filter(plan = ks_early_performance_tab |> format(path(Outputs/{State}[1], '%Y%m')) |> sum() > 1) {
  outPaths <- []
}

  ks_quarterly <- data.table::fread(pathPaths[1]) |>
    dplyr::bind_rows(data.table::fread(pathPaths[2])) |>
    dplyr::select(-dq_num_cases) |>
    unique() |>
    as.tibble()


# Once we officially replace the missing-segment properties we will switch to using the methods from the
# missing_segment_and_score.R file and use lis_and calculate by Q/M
# stopifnot(
#   "range_ref[i] must have exactly 48 rows per Scorecard for 10-bin KS aggregation":
#     all(dplyr::count(range_ref, lower_Range, upper_Range, ole count),
# )

## ks_bins_pct <- ranges_ref[i] pct
  dplyr::rename(segment = Scorecard) |>
  dplyr::count(segment, lower_Range, upper_Range, ole count)

final_ks_QF  = calculate_early_ksks_quarterly_QF_ks_tile_pct, method = 'tiles')
# final_ks_QF_live  = calculate_early_ksks_quarterly_QF_ks_bins_pct, method = 'live')


if ('live' %in% ks_methods) {
  ks_ks_pct_live = calculate_bks_quarterly_ks)
}


data = list(Performance_Basic = (read_ks_QF)
if('live' %in% ks_methods) {
  data(live_ks) = ks_methods
}
if('live' %in% ks_methods) {
  data[['live_KS_summary']] = live_ks_calculate_summary
}

saveRDS(data, here::here('Outputs/Quarterly_Stats/ks_early_performance_basic_{format(withDates[1], '%Y%m')}.sls'))

print('file written')
} else {
  print('file already exists')
}

### If quarterly, table_one_view

[UNCLEAR] fread(plan | select('Outputs/ks_manual_performance_calc_{format(withDates[1], '%Y%m')}.sls'))
paths <- fRead(here::here('Outputs/Quarterly_Stats/ks_performance_basic_{format(withDates[1], "%Y%m")}.sls'))

paths <- tibble(tibble(paths) <- fy: dbl_ls_here (here_'Outputs/Quarterly_Stats/')) |>
  dplyr::mutate(date = case_when(str_remove(paths) |> stringr::str_detect('test') == T ~ basename(paths) |>
    stringr::str_remove('ks_performance_basic_here_') |>
    basename('d') |>
    as.dist(format = "%Y%m"),
    basename(paths) |> stringr::str_detect('detect_test') == F ~ basename(paths) |>
      str_remove_ks_early_performance_basic_') |>
      stringr::str_remove('.sls') |>
      as.Date(format = "%Y%m") ))

dplyr::filter(paths, stringr::str_detect(path, 'c=h')) |>
  dplyr::arrange(date)


target_ks_quarter <- model_output_window()
paths <- paths |>
dplyr::filter(date == target_ks_quarter)

if(nrow(paths) == 0){
  stop(glue::glue('function expects one early KS output for {format(target_ks_quarter, "%Y%m")}, found {nrow(paths)}'))
}

ks_rolling <- readRDS(paths[[1]])

for rolling_4_qtr data <- cumulate::read_xls(rds(joinpoints[1])) |>
  dplyr::mutate(date = getDate(ks)) |>
  dplyr::arrange(abs())

target_ks_quarter <- model_output_window()
paths <- pathsdur()
target_ks_quarter <- -- target_ks_quarter

if(nrow(paths) == 0){
  stop(glue::glue('function expects one early KS output for {format(target_ks_quarter, "%Y%m")}, found {nrow(paths)}'))
}

```

# NULL method (tibble filter for [UNCLEAR] format output for the KS table creation
# Note: data must come from ks_rolling_4_qtr_data as [UNCLEAR] iter s in the method
# data built from ks_rolling_4_qtr_data ks methods ks methods
```{r ks_method_data}
  ks_method_data <- read_methods(paths(paths[1]), ks methods)
  dplyr::mutate(data <- pathsdur()) |>

for a qtr table - for id_d method & values ks method_data |>
  dplyr::mutate(segment = as.character(segment))
  dplyr::pivot_wider(names_from = method, values_from = ks_scores) |>

ks method data filter the KS from the base table against the output
  dplyr::read_cols(table(Development = c(W,P,E,S,13,10,2D))) |>
  dplyr::relocate(basename, .after = segment)

ks_rolling_4_qtr_table


approval_rolling_4_qtr <- ks_rolling_4_qtr_data |>
  dplyr::select(segment_bins, approval_rate, date) |>

for approval_rate_rolling_4_qtr_data <- [UNCLEAR]
  dplyr::mutate(date = glue::glue('{lubridate::quarter(date)}{format(date, "%y")}')) |>
  tidyr::pivot_wider(cols = -segment_bins, names_from = date, values_from = approval_rate)

approval_rolling_4_qtr


bad_rate_rolling_4_qtr <- ks_rolling_4_qtr_data |>
  dplyr::select(segment_bins, bad_rate, date) |>

for bad_rate_rolling_4_qtr_data <- [UNCLEAR]
  dplyr::mutate(date = glue::glue('{lubridate::quarter(date)}{format(date, "%y")}')) |>
  tidyr::pivot_wider(cols = -segment_bins, names_from = date, values_from = bad_rate)

bad_rate_rolling_4_qtr

```


```{r}
ks_badrate_trends <- build_ks_badrate_trends(
  ks_data = ks_method_data,
  bad_col = 'early_data',
  development_ks = c(10,20,30,40,50,60),
  development_bad_rate = c(0.06,0.08,0.12,0.01,0.07,0.07)
)

ks_badrate_trends

#### Visuals

# Plots for ks and bad rate are displayed here to preview what will go into the quarterly report word document.

# {r}
ks_seg_bad_4_qtr_table |>
  tidyr::pivot_longer(cols = -segment_names, to = 'population', values_to = 'Q1') |>
  ggplot() +
  geom_point(aes(x = segment, y = Q1, color = population), position=position_dodge(width = 0.25))

# ```

# {r}
max_ks_score <- max(ks_badrate_trends$ks_scores, na.rm = TRUE) # for max ks score
max_bad_rate <- max(ks_badrate_trends$bad_rate, na.rm = TRUE) # for max bad rate
scaling_factor <- max_ks_score / max_bad_rate

# KS lift - ggplot
grow_roll_data <- ks_badrate_trends |> dplyr::filter(!str(ks_ctr$starts(cumulative, 'Total')) |>
  dplyr::mutate(segment = as.factor(segment_bins), population = population, 'Total') |>
  dplyr::mutate(segment = as.factor(segment_bins))

grow_roll_data <- ks_badrate_trends |> dplyr::filter(population = 'Total') |>
  dplyr::mutate(
    aes(x = segment, y = 'bad_rate' * scaling_factor, color = 'population', shape = ) )
  grow_roll_data <- ks_badrate_trends |> dplyr::filter(population = 'Total')
  geom_point(data = ks_badrate_trends |> dplyr::filter(population == 'Total')) +
  geom_point(aes(x = segment, y = bad_rate * scaling_factor), color = [UNCLEAR], size = 2 +
    scale_y_continuous(name = "KS Score") +
    labs(x = "no issues") +
    [UNCLEAR] axis <- sec_axis(~./scaling_factor, name = "Bad Rate") + breaks = "every main scaled by 10

ks_plt

```

```{r}#ks_rolling_4_qtr_{}
#err? map_df(function(df){
  #iter::pivot_longer(cols = 1,upto_to = 'date',values_to = 'bad_rate')

ggplot() +
  geom_line(aes(x = segment_bins, y = bad_rate, color = date)) +
  geom_point(aes(x = segment_bins, y = bad_rate, color = date)) +
  #labs(x = segment_names) +
  theme(angle = segment_names) + 'Free_y'

```

```{r}
mod_plt <- approval_rolling_4_qtr |>
  #err? map_df(function(df){
  #iter::pivot_longer(cols = 1,upto_to = 'date',values_to = 'approval_rate')

ggplot() +
  geom_line(aes(x = segment_bins, y = approval_rate, color = date)) +
  geom_point(aes(x = segment_bins, y = approval_rate, color = date)) +
  facet_wrap(~segment_bins, scales = 'Free_y')

mod_plt

```

#### My Charts

# the above charts need to be formatted to be able to embed them into a word document.

```{r}
library(mschart)

# Since this is a mix (from markdown, bulleted) skills had some syntax per segment.
# All plots from here on out make charts formatted for a Word document.
ks_rank_order_data <- build_ks_rank_order_data(ks_method_data)

(lubridate::quarter(cohort_date %in% q_years(1)))format(cohort_date %in% q_years(2), "%y")) Booked"),
                                                    season(dfPayment) ~ "]" glue::glue("Scorecard 2 Bad Rate in
                                                    sn(dpPayment) ~ "]" glue::glue("Scorecard 2 Bad Rate \n
(lubridate::quarter(cohort_date %in% q_years(2)))(format(cohort_date %in% q_years(2), "%y")) Booked"),
(lubridate::quarter(cohort_date %in% q_years(2)))format(cohort_date %in% q_years(2)(2), "%y")) Booked"),
(lubridate::quarter(cohort_date %in% q_years(2)))format(cohort_date %in% q_years(3), "%y")) Booked")))

build_ks_rank_order(df, chart_title)
}

```

```{r}
library(mschart)

max_ks_score <- max(ks_badrate_trends(ks_scores, na.rm = TRUE) # Get max ks score
max_bad_rte <- max(ks_badrate_trends(bad_rte, na.rm = TRUE) # Get max bad rate
scaling_factor <- max_ks_score / max_bad_rte

bar_chart_obj <- ms_barchart(
  dat <- filter(ks_badrate_trends) )
      datar <- filter(ratings(chr_charts(population, 'bills'))
      dpar <- filter(chr_charts(chr_charts_show_all('all Segments' - 'Full Model',
                                                      ~ segment)) )

  dplyr::rename("KS Score", 'ks_scores'),
  x = "Scorecard",
  y = "KS Score",
  group = 'population') # to have different colored bars for population
)
chart_theme <- theme(legend.position = 'p')

# Prepare data for the line chart
line_chart_data <- ks_badrate_trends()
      datar <- filter(ratings(chr_charts(population, 'bills'))
      dplyr::mutate(scaled_bad_rate = bad_rate * scaling_factor)
                  .label = dplyr::case_when(segment == 'All Segments' ~ 'Full Model',
                                             ~ segment) ) # Apply the scaling factor

# Create the line chart Altcost object
linechart_obj <- ms_linechart(
  data = line_chart_data |> dplyr::mutate(Scorecard = dplyr::case_when(Scorecard == 'All Segments' ~ 'Full Model', ~
  Scorecard), .label = dplyr::case_when("KS Min Bad Rate"
  x = "Scorecard",
  y = "KS Min Bad Rate",
  group = 'population') # to have different colored lines for population
)
chart_settings(style = 'lineshown') $ob $ add_series
chart_theme(legend.position = 'p')

## bad rate table - Build ks bad rate flextable(ks_badrate_trends)

## bad rate table
```

## Backtesting #3 & OOT Bank Ordering

---

```{r}
backtesting_data

overwrite <-
lookout_months <- 36

# progress/messages: loop through slidom ~
suppressMessages(
  purrr::map(backtesting_data, backtesting_data %or% month(2), 'each'), .progress = -
  function(cohort_window) {
    backtesting_chart_window

    # cohort_window <- backtesting_data[[1]]
    # table save on saving performance
    print(cohort_window)

    # cohort_window <- backtesting_data[[1]]
    print(cohort_window)

  title_de <- tibble::tibble::here(Item = data.frame(here, [UNCLEAR]
      glue::glue(table::long_formatting(format(window, 'D%b')) > 1) == 1) } ) {
        subtitle

        table_sw <-
        format(chart_window[[1]], 'D%b')

        dt <-
        df <- ---- Adds Finally

  dt <- df$ Input bigl::bigl(date: base::data/quo()) ))
  stringr::str_subset(str_c(cohort_window[[1]], format(cohort_window[[1]], 'D%b'))

lengths(format(cohort_window[[1]], 'D%b') First (lookamont/line) ) )
```
if(sum(format(cohort_window()), '%b%') %in% basenames(files) )
          # string: str_subset(pattern = format(performance_window,'%b%')) &
          # string: str_remove(pattern = '.*') |
          # stringr: str_extract_all('\\d+')) > 0){
  apps_data <- data.table::fread(files |>
          stringr::str_subset(pattern = format(cohort_window[1], '%b%')))
  } else {
          stringr::str_subset(pattern = format(cohort_window[1], '%b%')))
  apps_data <-
    get_apps_data(cohort_window())

  } else {

  apps_data <-
    get_apps_data(cohort_window())


  # ---- Scorecard Files ----


        files <- fs::dir_ls(path = here('here/Data/Scorecard/') )
          stringr::str_subset(pattern = c(format(cohort_window[1],'%b%')))

        if(length(files) > 0){
        if(sum(format(cohort_window[1],'%b%') %in% basename(files) )
          format(performance_window,'%b%'))            stringr::str_subset(pattern =
                    stringr::str_remove(pattern = '.*scorecard') )
          stringr::str_extract_all('\\d+')) > 0){

          scorecard_data <- data.table::fread(files |>
            } else {
              stringr::str_subset(pattern = format(cohort_window[1],'%b%'))

        } else {
          scorecard_data <- get_cs_scorecard_data(cohort_window[1])

        } else {

          scorecard_data <- get_cs_scorecard_data(cohort_window[])


        # matching CSV files to select a table from c(ie
        files <- fs::dir_ls(path = here('here/Data/update/search_logging/')) |>
          stringr::str_subset(pattern = str_c(match(cohort_window[1],'%b%')))

        if(length(files) > 0){
          if(sum(str_c(format(match_cohort_window[1], '%b%') %in% basename(files),
                    format(performance_window, '%b%')) > 0){
          format_to(match_cohort_window[1], '%b%')

          } else {
            stringr::str_subset(pattern = '.*[_.].*') |>
            stringr::str_extract_all('\\d+')) > 0)
          } else {
            # scorecard_backend <- data.table::fread(files |>
            # stringr::str_subset(pattern =
                    stringr::str_extract_all('\\d+')) > 0)
            stringr::str_subset(pattern = format(cohort_window[1],'%b%'))

        } else {
          # places the null score mapping & function in this step?
          # scorecard_backend <- scorecard_data(cohort_window[1])

        } else {
          print('also- the null score mapping & function in this step'
          # scorecard_backend <- get_cs_scorecard_data(cohort_window[])


  filenames(fn ) <-
        format(cohort_window[1], '%b%') %in% if(!for_loop in here('here/Performance_56/') )
          # string: str_subset("merge") |>
          basename() |>
          # string: str_extract_all('\\d+')) |>
          as.int() |>
          # stringr: str_extract_all(filenames) |>
          unlist()

## ---- Standardize Fields Cases ----
# setting thr names to all be lower case
names(apps_data) <- names(apps_data) |> tolower()
n.name(performance_data) <- names(performance_data) |> tolower()
names(scorecard_data) <- names(scorecard_data) |> tolower()
names(scorecard_backtest) <- names(scorecard_backtest) |> tolower()
names(trended_data) <- names(trended_data) |> tolower()

library(dplyr)

apps_perf_joined <- apps_data |>
  filter(user_ref_num == as.numeric(user_ref_num)) |>
  lazy_dt() |>
  left_join(scorecard_data |>
              mutate(user_ref_num = as.numeric(user_ref_num)) |>
  left_join(scorecard_backtest|>
              mutate(user_ref_num = as.numeric(user_ref_num)) |>
  left_join(trended_data |>
              select(app_id,
                     open_dt,
                     month_since_open,
                     cr_am,
                     amt_act_lbng_ytd,
                     amt_fchg_paid_ytd,
                     actual_days_pd1bm,
                     tus_chgoff,
                     bkrpt_typ,
                     bal_ist_bal)) |>

  filter(is.na(mapped_score_refit) == F,
         is.na(segment) == F,
         mapped_score_refit > 100,
         !(last_product_of_hire %in% c('BCC', 'MCC'))) |>

  mutate(decision = case_when(decision_class_description == 'Approve',
                              'Decline')) |>

  group_by(app_num_decision) |>
  mutate(thin_is_mapped_score_refit = case_when(thin_score == mapped_score_refit - 1,
                                                1, 0)) |>

  set_net_lbng_mos = dplyr::case_when(filter(dates = month_dt_ordered) > month_since_open) %% 12 |>
) &
          month_since_open > 1 + amt_lbg_old_ytd,
          amt_fchg_paid_ytd) - dplyr::lag(amt_fchg_paid_ytd)),

  revenue = amt_ref_lbng_mos - amt_cost_mos - dplyr::lag(amt_lbng_mos),
  dp30 = dplyr::case_when(actual_days_pd1bm >= 30 , 1, 0),
  dp60 = dplyr::case_when(actual_days_pd1bm >= 60 , 1, 0),
  dp90 = dplyr::case_when(actual_days_pd1bm >= 90 , 1, 0),
  dp120 = dplyr::case_when(actual_days_pd1bm >= 120, 1, 0),
  at30 = dplyr::case_when(actual_days_pd1bm >= 30 , 1, 0),
  tol_chgoff = dplyr::case_when(abs(tol_chgoff) > 0, 1, 0),
  bkrpt_liq = dplyr::case_when(bkrpt_typ %in% c('1', '7', '13'), 1, 0),
  early_bad = case_when(bkpt  == 1 &
                           (mos <= 0 | is.na(bpt) == 1) | bkrpt_typ |= 1 | bkrpt_lss |= 1,
                        1, 0),
  bads = case_when(dp90 >= 1 |
                     dp30 >= dplyr::case_when(bkrpt_type[1] == 1, [UNCLEAR]target_type)-1,
                   1, 0),

  month_dp30 = case_when(as.numeric(first_dp30_filter >= as.numeric(90
as.numeric(month_since_open), 1, as.numeric(10)),
  month_dp60 = case_when(as.numeric(first_dp60_filter) >= as.numeric(90
as.numeric(month_since_open), 1, as.numeric(10)),
  month_dp90 = case_when(as.numeric(actual_days_pd1bm) >= as.numeric(90
as.numeric(month_since_open), 1, as.numeric(10)),
  month_dp4 = case_when(as.numeric(month_path4) is.na == 1
as.numeric(month_since_open), 1, as.numeric(10)),

  month_dp90 = case_when(as.numeric(month_path1) is.na == 1
as.numeric(month_since_open), 1, as.numeric(10)),
  month_dp4d0 = case_when(as.numeric(month_path2) is.na == 1
as.numeric(month_since_open), 1, as.numeric(10)),
  mutate(( )),
  mutate(month_dp30 = min(as.numeric(month_path1), is.na == 1) as.numeric(10)),

         (  )),
         early_for_cat_tol = case_when(early_bad %in% todos | 1 | radiolist_cat_tol, 90),
                                       1, [UNCLEAR]),

  # Filter to min of 12 obs per del
  # Aggregate all other inbers using list()
  summarise(across(c(app_id, month, dp30, dp60, los_events_ber), list),
            .groups = 'drop') |>

  # Further, other aggregates
revenue = sum(revenue, na.rm = T),

# Select the max balance during charge off (should be the first)
bal_co_bal = max(bal_co_bal, na.rm = T),
bads = max(bads, na.rm = T),
dp60 = max(dp60, na.rm = T),
lms_credit_lmt = max(lms_credit_lmt, na.rm = T)
) |>
mutate(title = tot_cat_bal,
net_revenue = revenue - title,
ltv_change = cr_lim - lms_credit_lmt,
) |>
org_paper_type_mapped = case_when(title is_mapped_score_refit) |>
case_when(mapped_score_refit == 44 ~ 'AA',
mapped_score_refit == 33 ~ 'A',
mapped_score_refit == 22 ~ 'B',
mapped_score_refit == 100 ~ 'B',
mapped_score_refit == 225 ~ 'C',
mapped_score_refit == 200 ~ 'C',
mapped_score_refit == 316 ~ 'D',
mapped_score_refit == 372 ~ 'D',
mapped_score_refit == 500 ~ 'E1',
~ org_paper_type) |> factor(levels = c('AA', 'A', 'A',
'B', 'C',
'D',
'E1', NA
)),

for_xt_lim = dplar(list(.ordering_paper_type_mapped == 'AA'
.value = case_when(lms_credit_lmt >= 25000 ~ 1,
.n = 1),
org_paper_type_mapped == 'A'
.value = case_when(lms_credit_lmt >= 25000 ~ 1,
lms_credit_lmt < 25000 ~ 0,
.n = 1),
org_paper_type_mapped == 'B'
[UNCLEAR] case_when(lms_credit_lmt >= 24000 ~ 1,
.n = 1),
org_paper_type_mapped == 'C'
.value = case_when(lms_credit_lmt >= 15000 ~ 1,
.n = 1),

[ -N] ),

ungroupu( ) |>
collect() |>
tibble() ,

data_table_fer(li,rs = open_port_friends,

----` Here_plan_plan('Data/04.9/rci_m.prefix_OF_early_trading_dp04_backtesting_[forecast]_coloring_window_
'ER6') |> gt(),
slope = 900,
score = ,
showProgress = T,
compress = 'bzip')

print('file Created')
} else {
print('file already exists')
}

}

}

### Aggregate to Quarterly Agg file

```

```{r}

############## Summary Stats ###########

# feat_counter_check_data
# backtesting_dat

path1 = tibble::tibble(paths = fs::dir_ls(here::here('Data/04.9/rci_m_Port'))) |>
stringr::str_subset(pattern = 'EA or ') |>
(stringr::str_subset(pattern = 'csv')
(stringr::str_subset(pattern = 'backtesting'))

paths

data = purrr::quietly_flung = base::sapply(paths) |> (stringr::str_detect('early_timing'),
paths) |> storage |> str_detect('early_timing') ~ '' |>
c(x = [UNCLEAR] |> lapply(4.B1 early timing backtesting_)) |>
(stringr::str_remove('[UNCLEAR] |> str_remove ('[UNCLEAR]
    stringr::str_remove( '[0-9]{1,}')
    unlist() |> )
  as.data.frame = tibble() |>

filter(early_timing == 1) |>
  dplyr::mutate(quarter = lubridate::quarter(date),
            year = lubridate::year(date))

paths = paths |> filter(date %in% ks$backtesting_date()) |> backtesting_date %in% methods(), 'month'))

if(fs::dir_ls(here::here('Outputs/Quarterly_Stats')) |>
  stringr::str_detect(glue::glue('ks_early_performance_backtesting_{format(paths$date[1], "%Y%m")}')))) |> sum() > 0 )
} else {

  ks_quarterly.data.table::fread(paths$paths[1]) |>
  dplyr::bind_rows(data.table::fread(paths$paths[2])) |>
  dplyr::bind_rows(data.table::fread(paths$paths[3])) |>
  dplyr::select(-PERMN, -ISIN) |>
  dplyr::lag_ks() |>
  dplyr::lag() |>
  dplyr::rollkrit()

# Here we officially include the missing segment simulation or will switch to using the methods from the
# paper and add upper score fill and use bin_aut calculate ks ()
  dt_ks_bins_pol = ranges_refit_pol |>
  dplyr::rename( = backtestard)
  dplyr::select(segment, Lower_Range, Upper_Range, old_score)

ks_quarterly_std = ks_quarterly |>
  dplyr::select(-dplyr::any_of('lag_score'), -early_bail)) |>
  dplyr::rename(prm_score = mapped_score_refit, early_bias = bad)

final_ks_df_backtesting = calculate_early_BL(ks_quarterly_std, df_ks_bins_pol, method = 'fixed')
if (1 == 1) {
  final_ks_df_backtesting_live = calculate_early_BL(ks_quarterly_std, df_ks_bins_pol, method = 'live')
}
if (!run_blik_ks_method) {
  from_ks_backtesting = calculate_from_BL(ks_quarterly_std)
}

data = [1]('Performance Back:' = final_ks_df_backtesting)
if(!is.null( blik_ks_method)) {
  data['live blik'] = final_ks_df_backtesting_live
}
if(!is.null( blik_ks_method)) {
  data['from blik'] = [1] ks_backtesting_summary
  data['from blik method'] = [UNCLEAR] ks_backtesting_pure
}

openxlsx::write.xlsx( x = data, file =
  here::here(glue::glue('Outputs/Quarterly_Stats/rk_early_performance_backtesting_{format(paths$date[1], "%Y%m")}.xlsx')))

print('File written')
} else {
  print('File already exists')
}
}

```

## R3 quarterly tables and stas:

```{r}
# here::here(glue::glue('Outputs/Quarterly'), 'Data/ks_po_[UNCLEAR]/data_perf_{format(paths$date[1], "%Y%m")}.xlsx'))

paths = tibble::tibble(paths = fs::dir_ls(here::here('Outputs/Quarterly_Stats')) )|>
  dplyr::mutate(date = lubridate::ymd( stringr::str_subset('Backtest')) |>
    stringr::str_remove( early_pearly_macro_backtesting_ ) |>
    stringr::str_remove( 'cfg_reset','cfg2') |>
    stringr::str_remove( '[UNCLEAR]') |>
    as.Date( format = "[UNCLEAR]") ) |>
ks_rolling_4_qtr_table_backtesting <- build_ks_method_ks_values_ks_sorted_data_backtesting() |>
  dplyr::mutate(segment = factor(segment, levels = ks_segment_order())) |>
  dplyr::arrange(segment) |>
  dplyr::mutate(segment = as.character(segment)) |>
  dplyr::pivot_wider(id_cols = segment, names_from = metric, values_from = ks_score) |>

# Does the ES from the backtesting aligned dt?
# dplyr::bind_cols(tibble::tibble(Development = c(10.3,31.3,33.3,46.3,32.2,37.1)))

# Does are the ES from the roll model
# dplyr::bind_cols(tibble::tibble(Development = c(46.31,32.71,28.36))) |>
  dplyr::relocate(Development, .after = segment)

ks_rolling_4_qtr_table_backtesting


```

```{r}
approval_rolling_4_qtr_backtesting <- ks_rolling_4_qtr_data_backtesting |>
  dplyr::select(segment_bins, approval_rate, date) |>
  dplyr::group_split() |>
  purrr::map(function(data) {
    dplyr::mutate(data, value = glue::glue({lubridate::quarter(date)}){format(date, "%y")},
      format(approval_rate_digits = format(approval_rate_digits))
    tidyr::pivot_wider(id_cols = c(segment_bins), names_from = data, values_from = approval_rate)
  })

approval_rolling_4_qtr_backtesting


```

```{r}
bad_rate_rolling_4_qtr_backtesting <- ks_rolling_4_qtr_data_backtesting |>
  dplyr::group_by(segment) |>
  dplyr::select(segment_bins, bad_rates, date) |>
  dplyr::group_split() |>
  purrr::map(function(data) {
    df |> dplyr::mutate(date = glue::glue({lubridate::quarter(date)}{format(date, "%y")}),
      format(bad_rate, digits = format(bad_rate_digits))
    tidyr::pivot_wider(id_cols = c(segment_bins), names_from = date, values_from = bad_rate)
  })

bad_rate_rolling_4_qtr_backtesting


```

```{r}
ks_badrate_trends_backtesting <- build_ks_tab_ks_trend(
  ks_data = ks_method_data_testing,
  bad_col = 'yearly_bads',
  development_ks = c(46.81,43.21,36.14,36.6),
  development_bad_rate = c(8.08,8.07,8.17,8.07,8.07,8.07)
)

ks_badrate_trends_backtesting


```

#### Visual

Plots for ks and bad rate are displayed here to preview what will be printed into the quarterly report word document.

```{r}
ks_rolling_4_qtr_table_backtesting |>
  tidyr::pivot_longer(cols = c(-segment_name_t), resolution_values_to = 'ks') |>
  ggplot() +
  geom_point(aes(x = segment, y = KS, color = population_position_position_dodge(width = 0.25),


```

max_ks_score_backtesting <- max_ks_badrate_trend_backtesting$ks_scores, na.rm = TRUE) # not max ks score
max_bad_rate_backtesting <- max(ks_badrate_trends_backtesting$bad_rate, na.rm = TRUE) # not max bad rate
scaling_factor_backtesting <- max_ks_score_backtesting / max_bad_rate_backtesting

do_plt_backtesting <- function() {
  ks_badrate_trends_backtesting |> dplyr::filter(!is.na(population), .data$population, 'digits',
    geom_point(aes(x = segment, y = ks_score, fill = population_position = 'dodge')
    geom_line(aes(x = segment, y = bad_rate * scaling_factor_backtesting, color = population, group = 1) +
    geom_point(aes(x = segment, y = bad_rate * scaling_factor_backtesting, color = population, shape = 1) +
    scale_y_continuous(
      name = 'Ks Scores',
      sec_axis = sec_axis(~./scaling_factor_backtesting, name = 'Bad Rate') # Example: secondary axis scaled by 10
    )
}

do_plt_backtesting


```

```{r}
#| fig-cap: "Rolling 4 Qtr Backtesting"

## [UNCLEAR] Apr/Oct [UNCLEAR]
server = max_Qtr(backtesting)

#bar(trends_logperiod = 5,nument_to = -data_values_to_be, bad_rate)

ggplot()
geom_line(aes(x = segment_bins, y = bad_rate, color = date))
geom_point(aes(x = segment_bins, y = bad_rate, color = date))
facet_wrap(~segment, scales = 'free_y')



```

rank_all_backtesting = appraisal_rolling_4_qtr_backtesting ||
params = dplyr_db(backtesting){
    if

geom_line(aes(x = segment_bins, y = appraisal_rate, color = date))
geom_point(aes(x = segment_bins, y = appraisal_rate, color = date))
geom_point(walk = appraisal_rate, scales = 'free_y')

rank_all_backtesting


```

## md_%Chart

The above charts need to be formatted to be able to embed them into a word document.

```{r}
library(mschart)

# bland Bicolor the limes enclosed, forecast Build bad rate bridge by segment
# given to by methods, create the doc series bad rate charts [UNCLEAR]
ms_on_chart_backtesting = [UNCLEAR] id_all_green_order_points_actual data backtesting)

ms_on_chart_backtesting = inner_map(ks_rank_order_data_backtesting, function(x){
chart_Main <- mscr_line(chartdata(x), [UNCLEAR] = "All segments", xlim= xlim("all Model bad data to
tab&table = quartile(subset_data $m %years), [UNCLEAR]([UNCLEAR] data $m %year(1), 'Qs') [UNCLEAR]

tab&table: quartile(subset_date $m %year(1))[UNCLEAR](subset_data $m %year(2), 'Qs') [UNCLEAR]
tab&table: quartile(subset_date $m %year(2))[UNCLEAR](subset_data $m %year(3), 'Qs') [UNCLEAR]
tab&table: quartile(subset_date $m %year(3))[UNCLEAR](subset_data $m %year(4), 'Qs') [UNCLEAR]
[UNCLEAR](subset_date $m %year([UNCLEAR]))[UNCLEAR](subset_data $m %year(4), [UNCLEAR]) [UNCLEAR] bad Rate to
tab&table: quartile(subset_date $m %year([UNCLEAR]))[UNCLEAR](subset_data $m %year(5), 'Qs') [UNCLEAR]
[UNCLEAR](subset_date $m %year([UNCLEAR]))[UNCLEAR](subset_data $m %year(6), 'Qs') [UNCLEAR] bad Rate to
tab&table: quartile(subset_date $m %year([UNCLEAR]))[UNCLEAR](subset_data $m %year(7), 'Qs') [UNCLEAR]

build_ks_rank_order_chart(KR, chart_title)

```

```{r}
library(mschart)

ms_badrate_backtesting <- main_badrate_trends_backtesting(ks_scores, as.na = full) # Qtr out to scale
max_bad_rate_backtesting = month_badrate_trends_backtesting() # Get out to scale and bad rate
scaling_factor_backtesting = max_ks_score_backtesting / max_bad_rate_backtesting

bar_chart_dbl_backtesting = ms_barchart(
    data = ks_badrate_trends_backtesting
    dplyr::filter(!dblcr.population, India) ||
    dplyr::mutate(board = dplyr::case_when(segment == 'All Segments' ~ 'Full Model',
                                            segment))
    dplyr::mutate("All Score" = 'Ks_scores')
) + #dplyr
group = "population" # to have different colour bars for population

mschart::chart_theme(legend_position = 'b')

# Mapping data for the line chart
line_chart_info_backtesting <- ks_badrate_trends_backtesting ||
    dplyr::mutate(scaled_bad_rate = bad_rate / scaling_factor_backtesting,
                 forecast = dplyr::case_when(segment == 'All Segments' ~ 'Full Model',
                                             segment)) # Apply the scaling factor

# create the line chart mschart object
line_chart_backtesting <- mscr_line(
    data = line_chart_backtesting, | xlab= month_backtesting, | dplyr::case_when(segment == "All Segments" ~ "Full
    ylab = 'Scaled Max bad Rate' 'bad_rate') %
) %+%
    group = "population" # to have different colour lines for population
)

chart_settings(style = "lineMarker") %>% # Add markers
    mschart::chart_theme(legend_position = 'b')


ks_bad_rate_table_backtesting <- build_ks_bad_rate_ftrs(abledata_ftmrate_trends_backtesting)

ks_bad_rate_table_backtesting



The official quarterly report now compiles all data pulled from sas+ and within a word document. The documents can be
found in '~/Reports/Standard-Quarterly/95.15/ R\Reports\Model Validating Report (model types)- {( custom type
The template can be found the R 8 year(s)/B\{deliverable}\cerCohort Jake Ba R year(s)() .docx

### {low tables for docs

The code here formats data frames into ms friendly tables to assist in word doc.

```{r}
# Step 0: Create flextable from original data

psl_col_summary <- psl_col_summary |>
    arrange(segmentation)

psl_col_summary_table <- flextable::flextable(
    psl_col_summary |>
        dplyr::mutate(Definition = ,

            [UNCLEAR] Scorecard Experience and Active Data',
            [UNCLEAR] Backcard Experience and Active Data',
            [UNCLEAR] Scorecard and Active Data (Serious Delinquency)',
            'Backcard Experience and Clss',
            'Backcard Experience and Early Closure (BC segment)
        ) |>
        dplyr::select(segmentation, Definition, Population Stability Index)
)

# Step 2: Identify alternating rows
even_rows <- which(seq_len(nrow(psl_col_summary)) %% 2 == 0)
odd_rows <- which(seq_len(nrow(psl_col_summary)) %% 2 != 0)

# Step 3: Identify conditional formatting rows
red_rows <- which(psl_col_summary$[UNCLEAR] 'Population Stability Index' ) < 0.10 &
            psl_col_summary$[UNCLEAR] 'Population Stability Index' >= 0.25)
red_rows <- which(psl_col_summary$[UNCLEAR] 'Population Stability Index' ) < 0.25)

# Step 4: Apply formatting
psl_col_summary_table <- psl_col_summary_table %>%
    flextable::set_table_properties(layout = 'autofit') |>
    flextable::fontsize(size = 8, part = 'all') |>
    flextable::font(fontname = 'Arial', part = 'all') |>
    flextable::bold(part = 'header', i = NULL, j = NULL) |>
    flextable::bold(row = [UNCLEAR], [UNCLEAR]) |>
    flextable::bg(i = even_rows, bg = '#D9D9D9') |>
    flextable::bg(i = odd_rows, bg = 'white') |>
    flextable::color(format_amber, 'Population Stability Index', digits = 2)
    flextable::color(format_amber, 'Population Stability Index', color = [UNCLEAR])
    flextable::color(i=red_rows, j = 'Population Stability Index', col = [UNCLEAR])

psl_col_summary_table



psl_scorecard_table <- purrr::map_psl_data, function(psl_data)
    p <- psl_data[[]]

    psl_scorecard_data
    {
        dplyr::case_when(lower_Range %in% 'total' ~ pbar_chart(lower_Range),(lower_Range),
                                                                             Total'),

        Percent_A = Percent_A * 100,
        Percent_B = Percent_B * 100,
        Diff_Difference = Diff_Difference (B-A) * 100 ) |>
        dplyr::select( Score Range = old_create,Percent_A,count,Percent_B, Diff_Difference (B-A) , Proportion
(B-A), Log of Proportion(stable)(B-A), part_Population Stability Index (B-A) * is part)
        flextable::flextable( , col_names = c(D-A) * 100 is |> count, Percent_B, Diff, Percent_B, Hist, count, Percent_B, Percent_B,
        Proportion to [UNCLEAR](B/A) Log of Proportion (stable)(B-A) Population \U Divergence (K-A) * /(B/A) = Population
Stability Index) |>
        [UNCLEAR] |>
        [UNCLEAR] |>

        # [UNCLEAR] the [UNCLEAR] range to 0 - note except the last row (total row)
        Score Range <- dplyr::if(group) {

            # use `[}` to access the psl_scoredata. hard match a literal
            score Range [group] <- lower_Range score)
            score Range }

addline_rows <- which(psi_scorecard_data$Population % Divergence \n (B/A) < (a(B/A) > 0.25 &
psi_scorecard_data$Population % Divergence \n (B/A) > (a(B/A) > 0.25 &
dplyr::row_number() != nrow(psi_scorecard_data)))

psi_scorecard_table <- flextable::flextable(psi_scorecard_data)

}

psi_scorecard_table

psi_scorecard_table <-
  flextable::set_table_properties(layout = 'autofit') |>
  flextable::fontsize(size = 9, part = 'all') |>
  flextable::color(color = 'auto', part = 'header') |>
  flextable::bold(part = 'header') |>
  flextable::bg(bg = [UNCLEAR], part = 'header') |>
  flextable::bg(i = which(max.Int(psi_scorecard_data$psi SS j > 0), bg = [UNCLEAR]) |>
  flextable::bg(i = which(max.Int(psi_scorecard_data$psi SS j > 0), bg = [UNCLEAR]) |>
  flextable::set_formatter_double <- c("Proportion \n (B/A)" = "Log of \n Proportion \n (stable)(B-A)","Population \n
Divergence (B-A) < (a(B/A) = ") |>
  flextable::bold(i = arrow(psi_scorecard_data), part = 'body') |>
  flextable::add(i = arrow(psi_scorecard_data), part = 'table') |>
  flextable::set_row_index_i = "Population \n Divergence in (0.10-0.2 * (a(B) <, bg = [UNCLEAR]) |>
  flextable::bg(i = "Population \n Divergence in (0.07 * (a(B/A) <, bg = [UNCLEAR]) |>

  return(psi_scorecard_table)

}


psi_scorecard_table


```

```{r}
column_names <- names(all_threshold_breaches)

all_breached_table <- flextable::flextable(all_threshold_breaches |>
  dplyr::select(
    'Score Range' = dplyr::case_when(lower_range == 'Total', 'glue','glue',[lower_range] %[upper_range]',
    dplyr::select(
      column_name(1),
      column_name(2),
      column_name(3),
      'Score Range',
      column_name(1),
      column_name(4)))

### breached_table
all_breached_table |>
  flextable::set_table_properties(layout = 'autofit') |>
  flextable::font(fontname = 'Arial', part = 'all') |>
#}
# install.packages("openxlsx")
# install.packages("dochart")
# install.packages("officer")
# install.packages("flextable")
# install.packages("rlottable")

# Load packages
# library(officer)
# library(flextable)
# library(rlottable)

#
# ----------- c, ""]
# If(min(psi_summary $s Order: Filter: Population Stability Index >= -.1 & Population Stability Index <= .25) > 0){
   #print("PSIChanges")glue::glue("PSIChanges{psi_summary}")
   # dplyr::filter(Population Stability Index >= -.1 & Population Stability Index <= .15) |>
   # all values of {psi_summary |> glue::glue_collapse(c ", ")} are above 0.25, indicating change has taken place."
#}

# If(min(psi_summary $s Order: Filter: Population Stability Index >= .251) > 0){
   # PSIChanges{glue::glue("PSIChanges{psi_summary}")(psi_summary |> format(psi_summary) |>
   #[?]  dplyr::pull(aresized) |> glue::glue_collapse(c ", ")} are all above 0.25 indicating some significant shifts in
   # the application population."
#}

# if(min(psi_summary $s Order: Filter: Population Stablity Tdex >= .1) == 0) {
   # PSIChanges <- glue::glue("No PSI changes from within")
#}

#
# MSsummary <- build_ms_summary_text(rs_hadoks_trends, in_label = "Simulation [UNCLEAR]")

# --- backtesting ---
# SummaryBacktesting <- build_ms_summary_text(rs_hadoks_trends_backtesting, eg_label= "Backtesting Cohort Oper

# ---- send order ----
RankOrderSummary <- build_rank_order_summary_text(
#see_application_breaches
   )
   # no_breach_message <- "no Breaches in rank order were observed in any segments."

# --- rank order backtesting ---
# rank_order_backtesting_data <- dplyr::map2(rank_order_data_backtesting,ransome_rank_order_breaches,
#rank_order_order_breachest)  |> overland

# RankOrderSummaryBacktesting <- build_rank_order_summary_text(
# rank_order_breaches_backtesting_data,
   #no_breach_message <- "no Breaches in rank order were observed in and expects for the backtesting cohort."
# )

# ReachTesting <- if(Test","Author","Send")

# Helper: creates a flextable of a keyword placeholder with console logging as
# a side effect and stores info together in a flexible variable — officer
add_ft_core <- function(token, keyword, ft, label, kparam) {
   report_out[["blah"]] <<- report_out[[token]] |>
      officer::body_replace_all_text(
         label, keyword,
         flextable::prop_part("ft","Body"),
         lengths(kpitem)))
   }

# officer::cursor_end(report_out)
   officer::body_remove() |>
      flextable::body_add_flextable()
   }

# Read in your existing word document (as a template)
# officer::read_docx(input_files/Model Monitoring Report & Backtesting - fracture.docx")

# Test replacements via flextable (revised, left in place)
# [UNCLEAR] officer_all_cursor (it's initialized on every loop iteration by next() call)
# Note, by default that function ignores cursor really and does a glob)
# query / col within the document, is a shorter bypass (e.g. 'FXSample') will
# also match   and correct   list nodes that match, correct it at a prefix
# (e.g., FXSample___blah)  —  silently destroying the longer prefix keyword.
# actually, can be read later cloning to the cursor paragraph module too.
# officer_ref:
#   officer::body_replace_all_text(
#   old_value = "blah",
      raw_value = glue::glue("Form(Variables::data[j, 'B4_B6_BY'])"),
      only_at_cursor = [UNCLEAR]
      # officer::body_replace_all_text("FXSIndex"
      [UNCLEAR]
#  officer::cursor_read(between "FXSRange") |>
#  dplyr::filter(list (body_cur))
# [UNCLEAR] left of right---
officer::body_replace_all_text(
old_value = "FXIChange",
new_value = FXIChangeSummary,
only_at_cursor = TRUE
)
officer::cursor_reach(keyword = "FXISummary") |>
officer::body_replace_all_text(
old_value = "FXISummary",
new_value = FXISummary,
only_at_cursor = TRUE
)
officer::cursor_reach(keyword = "FXSummaryBatchString") |>
officer::body_replace_all_text(
old_value = "FXSummaryBatchString",
new_value = FXSummaryBatchString,
only_at_cursor = TRUE
)
officer::cursor_reach(keyword = "RankOrderSummary") |>
officer::body_replace_all_text(
old_value = "RankOrderSummary",
new_value = RankOrderSummary,
only_at_cursor = TRUE
)
officer::cursor_reach(keyword = "RankOrderSummaryBatchString") |>
officer::body_replace_all_text(
old_value = "RankOrderSummaryBatchString",
new_value = RankOrderSummaryBatchString,
only_at_cursor = TRUE
)
officer::cursor_reach(keyword = "InputQuarter") |>
officer::body_replace_all_text(
old_value = "InputQuarter",
new_value = glue::glue("{Iri/video::quarter(last_quarter_end_date %m % years(k))}/{current_quarter_end_rate %m-%
only_at_cursor = TRUE
)
officer::cursor_reach(keyword = "OutputQuarter") |>
officer::body_replace_all_text(
old_value = "OutputQuarter",
new_value = glue::glue("{lubridate::quarter(serial_number_end_date %m-% years(2))@ |format(first_quarter_end_dur %m %
years)} - {1- 2%}"),
only_at_cursor = TRUE
)
officer::cursor_reach(keyword = "last(FXISqrtor") |>
officer::body_replace_all_text(
old_value = "last(FXISqrtor",
new_value = glue::glue("{lubridate::floor_date(submit_date %m-% years(k), 'quarter') - 1}/{format(lubridate::ceiling_date(submit_date %m-% years(k), 'quarter') - 1, '%Y')}"),
only_at_cursor = TRUE
)

doc = add_ft_table(doc, "FXISummaryTable", pxl_summary_table, pxl_alt_summary_table)
doc = add_ft_table(doc, "FXIcolTable", pxl_scorecard_table[0]], pxl_scorecard_table[1]])
doc = add_ft_table(doc, "FXIcolTable", pxl_scorecard_table[2]], pxl_scorecard_table[3]])
doc = add_ft_table(doc, "FXIcolTable", pxl_scorecard_table[4]], pxl_scorecard_table[5]])
doc = add_ft_table(doc, "FXIcolTable", pxl_scorecard_table[6]], pxl_scorecard_table[7]])
doc = add_ft_table(doc, "FXIcolTable", pxl_combined_table[4]], pxl_scorecard_table[8]])
doc = add_ft_table(doc, "FXIcolTable", pxl_scorecard_table[9]], pxl_scorecard_table[10]])

# ---- CSI table ----
doc <- add_ft_safe(doc, "CSIWatchTable", csi_breached_table, "csi_breached_table")

# ---- KS charts + table ----
message("[docx] Inserting KS charts at 'KSPlot'")
doc <- doc |>
  officer::cursor_reach("KSPlot") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = bar_chart_obj,  width = 6, height = 6 * 9/16) |>
  mschart::body_add_chart(chart = line_chart_obj, width = 6, height = 6 * 9/16)

message(sprintf("[docx] Inserting table 'ks_bad_rate_table' (rows=%d, cols=%d)",
                flextable::nrow_part(ks_bad_rate_table, "body"),
                length(ks_bad_rate_table$col_keys)))
doc <- doc |> flextable::body_add_flextable(ks_bad_rate_table)

# ---- rank order charts (forward pass) ----
message("[docx] Inserting rank order charts")
doc <- doc |>
  officer::cursor_reach("RankOrderPlotFull") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = my_ms_chart[[6]], width = 6, height = 6 * 9/16) |>
  officer::cursor_reach("RankOrderPlot0") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = my_ms_chart[[1]], width = 6, height = 6 * 9/16) |>
  officer::cursor_reach("RankOrderPlot1") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = my_ms_chart[[2]], width = 6, height = 6 * 9/16) |>
  officer::cursor_reach("RankOrderPlot2") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = my_ms_chart[[3]], width = 6, height = 6 * 9/16) |>
  officer::cursor_reach("RankOrderPlot3") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = my_ms_chart[[4]], width = 6, height = 6 * 9/16) |>
  officer::cursor_reach("RankOrderPlot4") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = my_ms_chart[[5]], width = 6, height = 6 * 9/16)

# ---- backtesting KS charts + table ----
message("[docx] Inserting backtesting KS charts at 'KSPlotBacktesting'")
doc <- doc |>
  officer::cursor_reach("KSPlotBacktesting") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = bar_chart_obj_backtesting,  width = 6, height = 6 * 9/16) |>
  mschart::body_add_chart(chart = line_chart_obj_backtesting, width = 6, height = 6 * 9/16)

message(sprintf("[docx] Inserting table 'ks_bad_rate_table_backtesting' (rows=%d, cols=%d)",
                flextable::nrow_part(ks_bad_rate_table_backtesting, "body"),
                length(ks_bad_rate_table_backtesting$col_keys)))
doc <- doc |> flextable::body_add_flextable(ks_bad_rate_table_backtesting)

# ---- backtesting rank order charts ----
message("[docx] Inserting backtesting rank order charts")
doc <- doc |>
  officer::cursor_reach("RankOrderPlotFullBacktesting") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = my_ms_chart_backtesting[[6]], width = 6, height = 6 * 9/16) |>
  officer::cursor_reach("RankOrderPlot0Backtesting") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = my_ms_chart_backtesting[[1]], width = 6, height = 6 * 9/16) |>
  officer::cursor_reach("RankOrderPlot1Backtesting") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = my_ms_chart_backtesting[[2]], width = 6, height = 6 * 9/16) |>
  officer::cursor_reach("RankOrderPlot2Backtesting") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = my_ms_chart_backtesting[[3]], width = 6, height = 6 * 9/16) |>
  officer::cursor_reach("RankOrderPlot3Backtesting") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = my_ms_chart_backtesting[[4]], width = 6, height = 6 * 9/16) |>
  officer::cursor_reach("RankOrderPlot4Backtesting") |>
  officer::body_remove() |>
  mschart::body_add_chart(chart = my_ms_chart_backtesting[[5]], width = 6, height = 6 * 9/16)

message("[docx] All content inserted - writing file")
print(doc, target = glue::glue("Reports/Standard_Quarterly_PSI_CSI_KS_Report/Model Monitoring Report ({model} Score) - CC Custom Score w Backtesting Fixed KS Bins {lubridate::quarter(cohort_date %m-% years(0))}Q{lubridate::year(cohort_date %m-% years(0))}.docx"))


*

