---
title: "CC Custom Scorecard Quarterly Report"
author: "Bryan Thomas"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Desktop/Professional/Projects/CC_Model_Monitoring")
# Clean slate: prevents objects from a previous cohort_date persisting across
# an interactive re-run. Knit starts fresh; this protects "Run All Chunks".
# NOTE: cohort_date must be overridden IN-FILE (line below), not at the console.
rm(list = ls())
here::i_am("orchestration_2.Rmd")
```

## Overview

TBD

## Running the Workflow

### 1) Renv Initialization

If this is the first time pulling the project, you will need to initialize the renv.lock file. This will set the environment dependencies in sync with what was used during project development. Run the init function below.

You should see this prompt:

``` r
renv::init()
this project already has a lockfile. What would you like to do?

1: Restore the project from the lockfile.
2: Discard the lockfile and re-initialize the project.
3: Activate the project without snapshotting or installing any packages.
4: Abort project initialization.
```

Select option 1 and the environment will be set up appropriately.

```{r}
# renv::init()
```

### 2) Credential Setup

Database credentials are supplied via environment variables from `.Renviron`;
see `.Renviron.example`. In the production environment this section configured
a credential store for the internal warehouses.

### 3) Setting the Project Paths

All pointers in this project use soft paths via the {here} package. To ensure that the pointers are correct. Be sure that the `CC_Model_Monitoring` project is opened before proceeding. This ensures the working directory is set appropriately.

Code and reference files are sourced within the `CC_Model_Monitoring` repo. Data is written in this directory as well as a local `data/` folder.

### 4) Loading Functions & Globals

Source all required R scripts and load necessary libraries. Set global variables for cohort dates and file paths.

```{r}
library(lubridate)
library(ggplot2)
library(data.table)

set.seed(42)
options(scipen = 999)
# --- COHORT DATE ---
# Override: uncomment and set to the quarter start date before running.
# Available quarters (generated data): 2025Q4, 2026Q1, 2026Q2, 2026Q3
cohort_date <- as.Date('2026-07-01')
if (!exists("cohort_date")) {
  cohort_date <- lubridate::floor_date(Sys.Date(), "quarter")
}
backfilling_date <- cohort_date %m-% months(6)

source('R/pull_apps.R')
source('R/function_cc_scorecard_data.R')
source('R/pull_features.R')
source('R/pull_performance.R')
```

### 5) Folder Init

This section checks for required directories and creates them if missing. Run once per new project setup.

**Note** — after folder creation, copy any required data files into the local `data/` directory to preserve file pointers.

```{r, echo=FALSE}
fs::dir_create(c('data', 'data/apps', 'data/scorecard', 'data/features', 'data/dq_12_mos'))
fs::dir_create(c('output_files', 'output_files/quarterly_stats',
                 'output_files/quarterly_stats/PSI',
                 'output_files/quarterly_stats/CSI',
                 'output_files/quarterly_stats/KS'))
```
# Quarterly Report

This section processes scorecard and application data, calculates PSI, CSI, KS, bad rate, and approval rate metrics, and prepares summary tables.

PSI and CSI evaluate the most recent window of through the door (TTD) applications. This window is considered the model input.

## PSI

PSI and CSI evaluate the current quarter's through-the-door applications —
the model's input distribution. Performance metrics (KS, DQ90) use a
different cohort; see the KS section for the two-cohort rationale.

Pull the current quarter's scorecard and application data from Supabase (or
read from local cache if already present) and write gzipped CSVs to `data/`.

```{r}

paths <- fs::dir_ls('data/scorecard')[which(basename(fs::dir_ls('data/scorecard')) %in% c(
  glue::glue('scorecard_{format(as.Date(cohort_date), "%Y%m")}.txt.gz'),
  glue::glue('scorecard_{format(as.Date(cohort_date) %m+% months(1), "%Y%m")}.txt.gz'),
  glue::glue('scorecard_{format(as.Date(cohort_date) %m+% months(2), "%Y%m")}.txt.gz')))]

if(length(paths) != 3){
  scorecard <- purrr::map_dfr(seq(cohort_date, cohort_date %m+% months(2), 'month'),
                              .progress = TRUE,
                              function(model_input_window){

                              df <- get_cc_scorecard_data(performance_window = model_input_window,
                                                          write = T)
                              return(df)
                              })
}


paths <- fs::dir_ls('data/apps/')[which(basename(fs::dir_ls('data/apps/')) %in% c(
  glue::glue('apps_{format(as.Date(cohort_date), "%Y%m")}.txt.gz'),
  glue::glue('apps_{format(as.Date(cohort_date) %m+% months(1), "%Y%m")}.txt.gz'),
  glue::glue('apps_{format(as.Date(cohort_date) %m+% months(2), "%Y%m")}.txt.gz')
))]

if(length(paths) != 3){
  apps <- purrr::map_dfr(seq(cohort_date, cohort_date %m+% months(2), 'month'),
                              .progress = TRUE,
                              function(model_input_window){

                              df <- get_apps_data(performance_window = model_input_window,
                                                          write = T)
                              return(df)
                              })
}
```

Read the cached scorecard and application files, join them, filter to the
scored population, and bin scores into frozen development-population vigintiles
for PSI comparison.

```{r}
number_of_month_window <- 3

scorecard <- purrr::map_df(c(1:number_of_month_window),
                function(i) {
                  
                  df <- data.table::fread(glue::glue('data/scorecard/scorecard_{format(cohort_date %m+% months(i - 1), "%Y%m")}.txt.gz'))
                  
                  })

apps <- purrr::map_df(seq(number_of_month_window),
                function(i) {
                  
                  df <- data.table::fread(glue::glue('data/apps/apps_{format(cohort_date %m+% months(i - 1), "%Y%m")}.txt.gz'))
                  
                  })

names(apps) <- names(apps) |> tolower()
names(scorecard) <- names(scorecard) |> tolower()
```

```{r}
 psi_df <- apps |> 
  mutate(app_num = as.numeric(app_num),
         user_ref_num = as.numeric(user_ref_num)) |>
    left_join(scorecard |>
                mutate(user_ref_num = as.numeric(user_ref_num))) |>
  mutate(has_score = case_when(is.na(prim_score) ~ 0,
                                 prim_score < 100 ~ -1,
                                 prim_score > 450 ~ 9999,
                              T ~ 1),
           has_segment = case_when(is.na(segment) ~ 0,
                                   T ~ 1)) |>
  filter(!client_product_cd %in% c('SEC', 'MSC'),
         !is.na(prim_score),
         has_segment == 1,
         prim_score >= 100)

  # Define vigintile breaks per segment (20 buckets each)
  # Breaks represent score thresholds; labels are auto-generated as "lower to upper"
  segment_breaks <- list(
    "All Segments" = c(100, 117, 134, 151, 168, 185, 202, 219, 236, 253,
                       270, 287, 304, 321, 338, 355, 372, 389, 406, 423, 450),
    "0" = c(100, 112, 124, 136, 148, 160, 172, 184, 196, 208,
            220, 232, 244, 256, 268, 280, 292, 304, 316, 328, 450),
    "1" = c(100, 118, 136, 154, 172, 190, 208, 226, 244, 262,
            280, 298, 316, 334, 352, 362, 372, 382, 392, 410, 450),
    "2" = c(100, 120, 140, 160, 180, 200, 220, 240, 260, 280,
            300, 315, 330, 345, 360, 375, 390, 405, 420, 435, 450),
    "3" = c(100, 125, 150, 170, 190, 210, 230, 250, 270, 290,
            310, 325, 340, 355, 370, 385, 395, 405, 420, 435, 450),
    "4" = c(100, 130, 155, 180, 200, 220, 240, 260, 280, 300,
            320, 335, 350, 365, 380, 390, 400, 410, 425, 440, 450)
  )

  # Helper: cut scores into labeled bins using segment-specific breaks
  bucket_scores <- function(scores, breaks) {
    labels <- paste(head(breaks, -1), tail(breaks, -1), sep = " to ")
    cut(scores, breaks = breaks, labels = labels, include.lowest = TRUE, right = TRUE)
  }

  # "All Segments" row
  psi_all <- psi_df |>
    dplyr::mutate(all_bucket_aligned = bucket_scores(prim_score, segment_breaks[["All Segments"]])) |>
    dplyr::group_by(all_bucket_aligned) |>
    dplyr::summarise(counts = dplyr::n_distinct(user_ref_num)) |>
    dplyr::mutate(segment = 'All Segments')

  # Per-segment rows
  psi_by_seg <- psi_df |>
    dplyr::mutate(segment = as.character(as.numeric(segment))) |>
    dplyr::group_by(segment) |>
    dplyr::group_modify(~ {
      brks <- segment_breaks[[.y$segment]]
      .x |>
        dplyr::mutate(all_bucket_aligned = bucket_scores(prim_score, brks)) |>
        dplyr::group_by(all_bucket_aligned) |>
        dplyr::summarise(counts = dplyr::n_distinct(user_ref_num), .groups = 'drop')
    }) |>
    dplyr::ungroup()

  psi <- dplyr::bind_rows(psi_all, psi_by_seg) |>
    dplyr::select(segment, counts, all_bucket_aligned) |>
    dplyr::arrange(segment, desc(all_bucket_aligned))
        
  
psi_raw_data <- psi |>
  tidyr::separate(all_bucket_aligned, c('Lower_Range', 'Upper_Range'), sep = ' to ') |>
  dplyr::mutate(Lower_Range = as.numeric(Lower_Range),
                Upper_Range = as.numeric(Upper_Range)) |>
  dplyr::rename(Scorecard = segment)

psi_raw_data
```


Join the development population reference (generated by R/build_dev_population.R)
with psi_raw_data on Scorecard + Lower_Range + Upper_Range (numeric). Compute
PSI per segment: percent_dev, percent_current, difference, proportion, log of
proportion, and population divergence. Split into 6 tibbles (All Segments + 0-4)
and write to a cached xlsx with one tab per segment.

```{r}
# The original pipeline loaded development references from external xlsx.
# That function is now R/build_dev_population.R (and R/ks_baseline.R for KS).

# --- PSI Calculation ---
# Load shared stability index helper and development population reference
source(here::here("R/compute_si.R"))
source(here::here("R/build_dev_population.R"))
source(here::here("R/wilson_ci.R"))
source(here::here("R/bootstrap_ci.R"))
dev_pop <- build_dev_population(here::here("data/dev_population/dev_population.txt.gz"))

# Full join: dev side drives the 120-row frame; coalesce empty current bins to 0
psi_joined <- dplyr::full_join(
  dev_pop, psi_raw_data,
  by = c("Scorecard", "Lower_Range", "Upper_Range")
) |>
  dplyr::mutate(counts = dplyr::coalesce(counts, 0L))

# --- Assertions ---
stopifnot("Dev bins have NAs - join key mismatch" =
            sum(is.na(psi_joined$counts_dev)) == 0)
stopifnot("Expected 120 rows (6 segments x 20 bins)" =
            nrow(psi_joined) == 120)

# Zero-bin policy (D14): floor at epsilon to avoid ln(0) = -Inf.
psi_epsilon <- 0.0001

# PSI-specific: assert uniform 5% dev (guaranteed by construction for vigintiles)
dev_pcts <- psi_joined |>
  dplyr::group_by(Scorecard) |>
  dplyr::mutate(p = counts_dev / sum(counts_dev)) |>
  dplyr::pull(p)
stopifnot("Dev percentages are not all 5%" = all(dev_pcts == 0.05))

# Compute stability index (shared helper — also used by CSI)
psi_result <- compute_stability_index(psi_joined, epsilon = psi_epsilon)

# Stable column order for diffable xlsx output across quarterly runs.
psi_col_order <- c("Scorecard", "Lower_Range", "Upper_Range", "counts_dev",
                   "counts", "percent_dev", "percent_current",
                   "Difference (B-A)", "Proportion (B/A)",
                   "Log of Proportion (B/A)", "Population Divergence (K-L)",
                   "epsilon_floored", "epsilon_only")
psi_data_list <- purrr::map(psi_result$detail, function(tbl) {
  tbl |> dplyr::select(dplyr::all_of(psi_col_order))
})

psi_summary <- psi_result$summary |>
  dplyr::rename(Population_Stability_Index = SI_value)

psi_summary

# --- PSI Bootstrap CI ---
psi_boot <- bootstrap_ci(
  data      = psi_df |> dplyr::mutate(segment = as.character(as.numeric(segment))),
  group_col = "segment",
  stat_fn   = function(df) {
    boot_all <- df |>
      dplyr::mutate(all_bucket_aligned = bucket_scores(prim_score, segment_breaks[["All Segments"]])) |>
      dplyr::group_by(all_bucket_aligned) |>
      dplyr::summarise(counts = dplyr::n(), .groups = "drop") |>
      dplyr::mutate(Scorecard = "All Segments")
    boot_seg <- df |>
      dplyr::group_by(segment) |>
      dplyr::group_modify(~ {
        brks <- segment_breaks[[.y$segment]]
        .x |>
          dplyr::mutate(all_bucket_aligned = bucket_scores(prim_score, brks)) |>
          dplyr::group_by(all_bucket_aligned) |>
          dplyr::summarise(counts = dplyr::n(), .groups = "drop")
      }) |>
      dplyr::ungroup() |>
      dplyr::rename(Scorecard = segment)
    boot_psi <- dplyr::bind_rows(boot_all, boot_seg) |>
      tidyr::separate(all_bucket_aligned, c("Lower_Range", "Upper_Range"), sep = " to ") |>
      dplyr::mutate(Lower_Range = as.numeric(Lower_Range), Upper_Range = as.numeric(Upper_Range))
    boot_joined <- dplyr::full_join(dev_pop, boot_psi,
                                     by = c("Scorecard", "Lower_Range", "Upper_Range")) |>
      dplyr::mutate(counts = dplyr::coalesce(counts, 0L))
    boot_result <- compute_stability_index(boot_joined, epsilon = psi_epsilon)
    tibble::tibble(group = boot_result$summary$Scorecard,
                   value = boot_result$summary$SI_value)
  },
  B = 500
)

psi_summary <- psi_summary |>
  dplyr::left_join(
    psi_boot |> dplyr::select(group, ci_lower, ci_upper, B),
    by = c("Scorecard" = "group")
  ) |>
  dplyr::mutate(
    tier = dplyr::case_when(
      Population_Stability_Index < 0.10 ~ "stable",
      Population_Stability_Index <= 0.25 ~ "watch",
      TRUE ~ "investigate"
    ),
    tier_certain = !(
      (ci_lower < 0.10 & ci_upper >= 0.10) |
      (ci_lower < 0.25 & ci_upper >= 0.25)
    )
  )

psi_summary

# --- Write xlsx ---
wb <- openxlsx::createWorkbook()
purrr::walk(names(psi_data_list), function(nm) {
  openxlsx::addWorksheet(wb, nm)
  openxlsx::writeDataTable(wb, nm, psi_data_list[[nm]])
})
fs::dir_create(here::here("output_files"))
openxlsx::saveWorkbook(wb,
  here::here("output_files/psi_quarterly.xlsx"),
  overwrite = TRUE)
source(here::here("R/write_metrics_cache.R"))
psi_cache <- psi_summary |>
  dplyr::select(Scorecard, Population_Stability_Index, ci_lower, ci_upper,
                tier, tier_certain, current_count, epsilon_share)
write_metrics_cache("PSI", psi_cache, cohort_date)
```

## PSI Trend Visuals

```{r psi_visuals}
source(here::here("R/report_visuals.R"))
source(here::here("R/load_metrics_history.R"))
psi_hist <- load_metrics_history("PSI", 4)
psi_trend_table(psi_hist)
psi_trend_chart(psi_hist)
```

## CSI

CSI evaluates drift in the model's input features. Each feature is binned using
frozen development-population breaks (D18) and compared to the dev distribution.
The CSI population is derived from psi_df to guarantee identity with the PSI
population.

```{r}
# --- CSI: Feature Stability ---
source(here::here("R/feature_breaks.R"))
fs::dir_create(here::here("data/features"))

# Pull + cache (mirrors apps/scorecard pull pattern above)
feat_paths <- fs::dir_ls("data/features")[which(
  basename(fs::dir_ls("data/features")) %in% c(
    glue::glue("features_{format(as.Date(cohort_date), '%Y%m')}.txt.gz"),
    glue::glue("features_{format(as.Date(cohort_date) %m+% months(1), '%Y%m')}.txt.gz"),
    glue::glue("features_{format(as.Date(cohort_date) %m+% months(2), '%Y%m')}.txt.gz")
  )
)]

if (length(feat_paths) != 3) {
  purrr::walk(seq(cohort_date, cohort_date %m+% months(2), "month"),
              function(m) get_features_data(performance_window = m, write = TRUE))
}

# Read from cache
features <- purrr::map_dfr(seq_len(number_of_month_window), function(i) {
  data.table::fread(glue::glue(
    "data/features/features_{format(cohort_date %m+% months(i - 1), '%Y%m')}.txt.gz"
  ))
})
names(features) <- tolower(names(features))
features <- features |> dplyr::mutate(user_ref_num = as.numeric(user_ref_num))

# Join to PSI population (guarantees identical population — same filters applied)
csi_df <- dplyr::inner_join(
  psi_df |> dplyr::select(user_ref_num, segment),
  features,
  by = "user_ref_num"
)

# --- Per-feature CSI ---
csi_results <- list()
csi_summary_rows <- list()

for (fname in names(feature_breaks)) {
  fb <- feature_breaks[[fname]]
  vals <- csi_df[[fname]]

  # Bin: integer index (1:n_bins). Join key is structural, not label-based.
  if (fb$type == "continuous") {
    bin_idx <- as.integer(cut(vals, breaks = fb$breaks,
                              right = TRUE, include.lowest = TRUE))
    n_bins <- length(fb$dev_counts)
    bin_labels <- paste(head(fb$breaks, -1), tail(fb$breaks, -1), sep = " to ")
  } else {
    bin_idx <- as.integer(factor(vals, levels = fb$levels))
    n_bins <- length(fb$levels)
    bin_labels <- fb$levels
  }

  # Assert no NA bin index (value outside declared bins/levels)
  stopifnot("Feature value outside declared bins/levels" = !anyNA(bin_idx))

  # Aggregation: per segment + All Segments
  binned <- dplyr::tibble(
    user_ref_num = csi_df$user_ref_num,
    Scorecard    = as.character(as.numeric(csi_df$segment)),
    bin_index    = bin_idx
  )

  agg_by_seg <- binned |>
    dplyr::group_by(Scorecard, bin_index) |>
    dplyr::summarise(counts = dplyr::n(), .groups = "drop")

  agg_all <- binned |>
    dplyr::mutate(Scorecard = "All Segments") |>
    dplyr::group_by(Scorecard, bin_index) |>
    dplyr::summarise(counts = dplyr::n(), .groups = "drop")

  agg <- dplyr::bind_rows(agg_all, agg_by_seg)

  # Dev reference: 6 segments x n_bins rows (global breaks — same for all)
  dev_ref <- dplyr::bind_rows(lapply(
    c("All Segments", as.character(0:4)),
    function(seg) {
      dplyr::tibble(
        Scorecard  = seg,
        bin_index  = seq_len(n_bins),
        counts_dev = fb$dev_counts,
        bin_label  = bin_labels
      )
    }
  ))

  # Full join from dev side; coalesce empty current bins to 0
  csi_joined <- dplyr::full_join(dev_ref, agg,
                                  by = c("Scorecard", "bin_index")) |>
    dplyr::mutate(counts = dplyr::coalesce(counts, 0L))

  # Assert full grid
  expected_rows <- n_bins * 6L
  if (nrow(csi_joined) != expected_rows) {
    stop(fname, ": expected ", expected_rows, " rows, got ", nrow(csi_joined))
  }

  # Compute stability index (same helper as PSI)
  result <- compute_stability_index(csi_joined, epsilon = psi_epsilon)

  csi_results[[fname]] <- result
  csi_summary_rows[[fname]] <- result$summary |>
    dplyr::mutate(feature = fname)
}

# --- CSI summary table: 6 segments x 5 features ---
csi_summary_long <- dplyr::bind_rows(csi_summary_rows)
csi_summary <- csi_summary_long |>
  dplyr::select(Scorecard, feature, CSI = SI_value) |>
  tidyr::pivot_wider(names_from = feature, values_from = CSI)

csi_summary

# --- CSI Bootstrap CI ---
# Resample application rows ONCE per replicate; recompute all 5 features
# from the same draw to preserve correlation structure.
csi_boot_data <- csi_df |>
  dplyr::mutate(Scorecard = as.character(as.numeric(segment)))

csi_ci <- bootstrap_ci(
  data      = csi_boot_data,
  group_col = "Scorecard",
  stat_fn   = function(df) {
    all_results <- list()
    for (fname in names(feature_breaks)) {
      fb <- feature_breaks[[fname]]
      vals <- df[[fname]]
      if (fb$type == "continuous") {
        bin_idx <- as.integer(cut(vals, breaks = fb$breaks, right = TRUE, include.lowest = TRUE))
        n_bins <- length(fb$dev_counts)
      } else {
        bin_idx <- as.integer(factor(vals, levels = fb$levels))
        n_bins <- length(fb$levels)
      }
      binned <- dplyr::tibble(Scorecard = df$Scorecard, bin_index = bin_idx)
      agg <- dplyr::bind_rows(
        binned |> dplyr::group_by(Scorecard, bin_index) |>
          dplyr::summarise(counts = dplyr::n(), .groups = "drop"),
        binned |> dplyr::mutate(Scorecard = "All Segments") |>
          dplyr::group_by(Scorecard, bin_index) |>
          dplyr::summarise(counts = dplyr::n(), .groups = "drop")
      )
      dev_ref <- dplyr::bind_rows(lapply(c("All Segments", as.character(0:4)), function(seg) {
        dplyr::tibble(Scorecard = seg, bin_index = seq_len(n_bins), counts_dev = fb$dev_counts)
      }))
      joined <- dplyr::full_join(dev_ref, agg, by = c("Scorecard", "bin_index")) |>
        dplyr::mutate(counts = dplyr::coalesce(counts, 0L))
      result <- compute_stability_index(joined, epsilon = psi_epsilon)
      for (i in seq_len(nrow(result$summary))) {
        all_results[[length(all_results) + 1]] <- list(
          group = paste0(result$summary$Scorecard[i], "::", fname),
          value = result$summary$SI_value[i]
        )
      }
    }
    dplyr::bind_rows(all_results)
  },
  B = 500
)

# Parse compound group key back to Scorecard + feature
csi_ci <- csi_ci |>
  tidyr::separate(group, into = c("Scorecard", "feature"), sep = "::") |>
  dplyr::left_join(
    csi_summary_long |> dplyr::select(Scorecard, feature, estimate = SI_value),
    by = c("Scorecard", "feature")
  ) |>
  dplyr::select(Scorecard, feature, estimate, ci_lower, ci_upper, B)

csi_ci

# Epsilon share
csi_eps_share <- csi_summary_long |>
  dplyr::select(Scorecard, feature, epsilon_share) |>
  tidyr::pivot_wider(names_from = feature, values_from = epsilon_share)

csi_eps_share

# --- Assert full bin grid: 10+8+5+4+3 = 30 bins per segment, 180 total ---
total_data_rows <- sum(purrr::map_int(names(csi_results), function(fname) {
  fb <- feature_breaks[[fname]]
  n_bins <- if (fb$type == "continuous") length(fb$dev_counts) else length(fb$levels)
  data_rows <- sum(purrr::map_int(
    csi_results[[fname]]$detail,
    ~ sum(!is.na(.x$bin_index))
  ))
  if (data_rows != n_bins * 6) {
    stop(fname, ": expected ", n_bins * 6, " data rows, got ", data_rows)
  }
  data_rows
}))
stopifnot("Total data rows should be 180 (30 bins x 6 segments)" =
            total_data_rows == 180)

# --- Write xlsx: one tab per feature, segment as column ---
wb_csi <- openxlsx::createWorkbook()
purrr::walk(names(csi_results), function(fname) {
  tab_data <- dplyr::bind_rows(csi_results[[fname]]$detail)
  openxlsx::addWorksheet(wb_csi, fname)
  openxlsx::writeDataTable(wb_csi, fname, tab_data)
})
openxlsx::addWorksheet(wb_csi, "ci")
openxlsx::writeDataTable(wb_csi, "ci", csi_ci)
openxlsx::saveWorkbook(wb_csi,
  here::here("output_files/csi_quarterly.xlsx"),
  overwrite = TRUE)
csi_cache <- csi_ci |>
  dplyr::rename(CSI = estimate) |>
  dplyr::select(-B) |>
  dplyr::left_join(
    csi_summary_long |> dplyr::select(Scorecard, feature, current_count, epsilon_share),
    by = c("Scorecard", "feature")
  )
write_metrics_cache("CSI", csi_cache, cohort_date)
```

## Candidate Drivers of Score Distribution Shift

The score distribution shifted (PSI above), and among model inputs the features
below also shifted materially while others held. These are candidate drivers,
not a decomposition: CSI and PSI are independent calculations on different
variables. Attributing a specific share of the PSI shift to a given feature
would require the scorecard weights and a sensitivity analysis, which is outside
the scope of this quarterly review.

```{r csi_visuals}
csi_hist <- load_metrics_history("CSI", 4)
current_q <- max(psi_hist$report_quarter)
csi_heatmap(csi_hist, current_q)
drilldowns <- csi_drilldown_bars(csi_hist, psi_hist, current_q, max_segments = 3)
for (nm in names(drilldowns)) {
  cat("\n\n### Segment", nm, "— Feature Drill-Down\n\n")
  print(drilldowns[[nm]])
}
```

## KS and DQ90 Rank Ordering

Performance-based metrics use a DIFFERENT cohort than PSI/CSI. PSI/CSI
evaluate Q3 2026 through-the-door applications (current quarter input
distribution). KS and DQ90 rank ordering evaluate Q3 2025 BOOKED
applications whose 12-month outcome window has now closed. The lag is
inherent to outcome monitoring: performance evidence is always 12 months
behind the input distribution that PSI measures.

```{r}
# --- KS and DQ90 Rank Ordering ---
source(here::here("R/compute_ks.R"))
source(here::here("R/ks_baseline.R"))

# Performance cohort: 12 months prior to current quarter
perf_date <- cohort_date %m-% months(12)

# Pull + cache performance data (3 months, mirrors apps pull pattern above)
perf_paths <- fs::dir_ls("data/dq_12_mos")[which(
  basename(fs::dir_ls("data/dq_12_mos")) %in% c(
    glue::glue("dq_12_mos_{format(perf_date, '%Y%m')}.txt.gz"),
    glue::glue("dq_12_mos_{format(perf_date %m+% months(1), '%Y%m')}.txt.gz"),
    glue::glue("dq_12_mos_{format(perf_date %m+% months(2), '%Y%m')}.txt.gz")
  )
)]

if (length(perf_paths) != 3) {
  purrr::walk(seq(perf_date, perf_date %m+% months(2), "month"),
              function(m) get_performance_data(performance_window = m, write = TRUE))
}

perf <- purrr::map_dfr(seq_len(number_of_month_window), function(i) {
  data.table::fread(glue::glue(
    "data/dq_12_mos/dq_12_mos_{format(perf_date %m+% months(i - 1), '%Y%m')}.txt.gz"
  ))
})
names(perf) <- tolower(names(perf))

# Pull Q3 2025 apps + scorecard for score and segment
perf_apps_paths <- fs::dir_ls("data/apps")[which(
  basename(fs::dir_ls("data/apps")) %in% c(
    glue::glue("apps_{format(perf_date, '%Y%m')}.txt.gz"),
    glue::glue("apps_{format(perf_date %m+% months(1), '%Y%m')}.txt.gz"),
    glue::glue("apps_{format(perf_date %m+% months(2), '%Y%m')}.txt.gz")
  )
)]

if (length(perf_apps_paths) != 3) {
  purrr::walk(seq(perf_date, perf_date %m+% months(2), "month"),
              function(m) get_apps_data(performance_window = m, write = TRUE))
}

perf_apps <- purrr::map_dfr(seq_len(number_of_month_window), function(i) {
  data.table::fread(glue::glue(
    "data/apps/apps_{format(perf_date %m+% months(i - 1), '%Y%m')}.txt.gz"
  ))
})
names(perf_apps) <- tolower(names(perf_apps))

perf_sc_paths <- fs::dir_ls("data/scorecard")[which(
  basename(fs::dir_ls("data/scorecard")) %in% c(
    glue::glue("scorecard_{format(perf_date, '%Y%m')}.txt.gz"),
    glue::glue("scorecard_{format(perf_date %m+% months(1), '%Y%m')}.txt.gz"),
    glue::glue("scorecard_{format(perf_date %m+% months(2), '%Y%m')}.txt.gz")
  )
)]

if (length(perf_sc_paths) != 3) {
  purrr::walk(seq(perf_date, perf_date %m+% months(2), "month"),
              function(m) get_cc_scorecard_data(performance_window = m, write = TRUE))
}

perf_sc <- purrr::map_dfr(seq_len(number_of_month_window), function(i) {
  data.table::fread(glue::glue(
    "data/scorecard/scorecard_{format(perf_date %m+% months(i - 1), '%Y%m')}.txt.gz"
  ))
})
names(perf_sc) <- tolower(names(perf_sc))

# Join: performance -> apps -> scorecard
ks_df <- perf |>
  dplyr::mutate(user_ref_num = as.numeric(user_ref_num)) |>
  dplyr::inner_join(
    perf_apps |> dplyr::mutate(user_ref_num = as.numeric(user_ref_num)) |>
      dplyr::select(user_ref_num, prim_score, decision),
    by = "user_ref_num"
  ) |>
  dplyr::inner_join(
    perf_sc |> dplyr::mutate(user_ref_num = as.numeric(user_ref_num)) |>
      dplyr::select(user_ref_num, segment),
    by = "user_ref_num"
  )

# Assert: all performance rows are approved (table-level constraint)
stopifnot("Performance rows with non-Approve decision" =
            all(ks_df$decision == "Approve"))

# KS deciles are RE-DERIVED from the booked cohort, NOT frozen.
# This is the OPPOSITE of PSI/CSI and correctly so: PSI asks whether the
# population moved relative to development, KS asks whether the score
# still separates within THIS population.
ks_result <- compute_ks_stats(ks_df)

# --- Monitoring flags (observations, not hard stops) ---
# Monotonicity: segments 1-4 should have non-decreasing decile bad rates
for (seg in c("0", "1", "2", "3", "4")) {
  seg_rates <- ks_result$decile_rates |>
    dplyr::filter(segment == seg) |>
    dplyr::arrange(decile)
  diffs <- diff(seg_rates$bad_rate)
  if (!all(diffs >= 0)) {
    breaks <- which(diffs < 0)
    warning("Seg ", seg, ": monotonicity break at decile(s) ",
            paste(breaks, collapse = ", "))
  }
}

# --- Compare to development baseline ---
ks_comparison <- dplyr::inner_join(
  ks_result$ks_by_segment,
  ks_baseline$ks,
  by = "segment",
  suffix = c("", "_dev")
) |>
  dplyr::mutate(ks_delta = ks_value - dev_ks)

ks_comparison

# --- KS Bootstrap CI ---
ks_boot_t0 <- proc.time()
ks_boot <- bootstrap_ci(
  data      = ks_df |> dplyr::mutate(segment = as.character(segment)),
  group_col = "segment",
  stat_fn   = function(df) {
    all_df <- dplyr::bind_rows(df, df |> dplyr::mutate(segment = "All Segments"))
    ks <- all_df |>
      dplyr::group_by(segment) |>
      dplyr::group_modify(~ {
        .x <- .x |> dplyr::arrange(dplyr::desc(prim_score)) |>
          dplyr::mutate(decile = dplyr::ntile(dplyr::desc(prim_score), 10))
        dec <- .x |> dplyr::group_by(decile) |>
          dplyr::summarise(n = dplyr::n(), n_bads = sum(dq90), .groups = "drop") |>
          dplyr::arrange(decile)
        total_goods <- sum(dec$n - dec$n_bads)
        total_bads <- sum(dec$n_bads)
        if (total_bads == 0) return(tibble::tibble(ks_value = 0))
        dec <- dec |>
          dplyr::mutate(
            cum_pct_good = cumsum(n - n_bads) / total_goods,
            cum_pct_bad  = cumsum(n_bads) / total_bads,
            ks_at_decile = abs(cum_pct_bad - cum_pct_good) * 100
          )
        tibble::tibble(ks_value = max(dec$ks_at_decile))
      }) |>
      dplyr::ungroup()
    tibble::tibble(group = ks$segment, value = ks$ks_value)
  },
  B = 500
)
message("KS bootstrap: ", round((proc.time() - ks_boot_t0)[3], 1), "s")

ks_comparison <- ks_comparison |>
  dplyr::left_join(
    ks_boot |> dplyr::select(group, ci_lower, ci_upper, B),
    by = c("segment" = "group")
  )

ks_comparison

# --- Decile bad-rate Wilson CI ---
# Wilson intervals per decile INDEPENDENTLY. These describe each decile
# alone, not the ten jointly. Comparing all nine adjacent pairs is nine
# comparisons and will occasionally show a spurious gap. These are
# screening intervals for triage, not hypothesis tests.
decile_wilson <- wilson_ci(ks_result$decile_rates$n_bads, ks_result$decile_rates$n)
ks_result$decile_rates <- ks_result$decile_rates |>
  dplyr::mutate(ci_lower = decile_wilson$lower, ci_upper = decile_wilson$upper)

stopifnot("Wilson CI lower bound negative" = all(ks_result$decile_rates$ci_lower >= 0))
stopifnot("Wilson CI upper bound > 1" = all(ks_result$decile_rates$ci_upper <= 1))

# Test case: segment 0 decile 1 (0 bads in 1538)
seg0_d1 <- ks_result$decile_rates |> dplyr::filter(segment == "0", decile == 1)
stopifnot("Wilson CI for 0/1538: lower should be ~0" = seg0_d1$ci_lower < 0.001)
stopifnot("Wilson CI for 0/1538: upper should be ~0.0025" = abs(seg0_d1$ci_upper - 0.0024) < 0.001)

ks_result$decile_rates

# --- Cache ---
openxlsx::write.xlsx(
  list(ks_comparison = ks_comparison,
       decile_rates = ks_result$decile_rates),
  here::here("output_files/ks_quarterly.xlsx"),
  overwrite = TRUE
)
ks_cache <- ks_comparison |>
  dplyr::select(segment, ks_value, dev_ks, ks_delta, ci_lower, ci_upper, n_booked, n_bads)
write_metrics_cache("KS", ks_cache, cohort_date, perf_date = perf_date)
decile_cache <- ks_result$decile_rates |>
  dplyr::select(segment, decile, n, n_bads, bad_rate, ci_lower, ci_upper, min_score, max_score)
write_metrics_cache("KS_DECILES", decile_cache, cohort_date, perf_date = perf_date)
```

## KS and Rank-Ordering Visuals

```{r ks_visuals}
ks_hist <- load_metrics_history("KS")
ks_comparison_chart(ks_hist)
ks_change_table(ks_hist)
```

## Rank Ordering by Segment

Compare current and development decile bad rates by segment. Each panel
shows the rate curve and Wilson confidence band; monotonicity breaks are
visible as inversions.

```{r rank_order_visuals}
decile_hist <- load_metrics_history("KS_DECILES")
source(here::here("R/ks_baseline.R"))
rank_order_chart(decile_hist, ks_baseline$decile_rates)
```

## Threshold Provenance and Methods

### Thresholds and Actions

| Metric | Stable | Watch | Investigate |
|---|---|---|---|
| PSI / CSI | < 0.10 | 0.10 – 0.25 | > 0.25 |
| KS relative decline | < 10% | 10% – 15% | > 15% |
| Rank ordering | Monotonic | — | Any break in middle deciles |

**Actions:**

- **Stable**: No action; note in quarterly review.
- **Watch**: Flag in quarterly review; compare to prior quarters for trend.
- **Investigate**: Notify model owner; assess refit need; document in model risk log.

### Statistical Methods

Confidence intervals use two methods:

- **Bootstrap** (B = 500, stratified percentile): PSI, CSI, and KS. Resamples
  rows within each segment, holding group size fixed. Measures sampling
  variability of the metric given the observed cohort.
- **Wilson score**: Decile bad rates. Closed-form binomial CI; survives zero
  counts.

These intervals reflect sampling variability — "if a cohort with this shape had
been drawn differently, how much would the metric move?" They do NOT predict
regeneration variance from the data generator.

## Executive Summary

_Placement note: this summary requires values computed throughout the document.
During docx assembly it moves to the front of the report._

```{r executive_summary}
exec_tbl <- executive_summary_table(psi_hist, ks_hist, decile_hist,
                                     ks_baseline$decile_rates)
exec_tbl
```
